### 2015-03-17 tex-inputs/related_work.tex
paper

%!TEX root = ../paper.tex

\section{Related Work}
In this section, we outline previous research regarding how users understand and act on the Internet, communicating relevant risks to users, and usability of Tor Browser

\subsection{User Perceptions and Behaviors}
It is not surprising to note that the general public is very willing to trade their personal information for little rewards \cite{norberg2007privacy}. A part of this phenomenon is due to the fact that the Internet provides instant gratification for this exchange \cite{acquisti2004privacy}. Indeed, there is a discrepancy between users' reported privacy preferences and their browsing habits \cite{jensen2005privacy}.

The behavior profiles, as well as the demographics of Tor Browser, are kept anonymous for obvious reasons. No one knows exactly what the average Tor user is like. Some information can be inferred from the bug reports filed by users, but this is a self-selecting subset of the users who are arguably much more motivated and technically savvy than the average user. Anecdotes are another source to gain an understanding of the average user, although these may not be ground truth. A surprising resource is research investigating attacks on Tor users. Work by Blond trace back and profile a subset of users in the process, and talk about the results \cite{blond2011one}. However, this is also a small subset of the user space.

\subsection{Risk Communication}
Effectively communicating the current risks to a user can have a significant impact on user behavior. A field study of browser warnings show that browser warnings do have the potential to greatly affect user behavior, and work somewhat well in practice \cite{akhawe2013alice}. However, many browsers and their warnings have a history of failing to inform users, who become habituated to warnings; active warnings which interrupt the user process can be a more effective warning mechanism \cite{egelman2008you}. Warnings are critical in informing users for Tor Browser, since consequences of becoming deanonymized can mean drastic consequences, especially users who live in countries which have outlawed encryption or employ nation-state level censorship \cite{crypto_wikipedia_2015,china_wikipedia_2015}.

\subsection{Tor Browser and Usability}

Tor, the clear frontrunner today in anonymous browsing, was specifically designed with usability, or the ease of use, in mind \cite{tor_wikipedia_2015, dingledine2004tor}. Although usability is generally critical to the security of any system, this human factors field has traditionally played a limited role in research \cite{cranor2005security}. However, anonymous systems especially benefit from usability. Usability means more users--and more users mean more security and privacy in such systems \cite{dingledine2006anonymity}. Currently, a wide range of people use Tor Browser, including normal people, militaries, journalists, law enforcements, activists, businessmen, bloggers, and IT professionals \cite{torproject_2015}.

As a whole, Tor is very usable. This is evidenced by the popularity of the system. Clark's usability study of Tor Browser and related software find that in general, Tor Browser is very usable, and suggest that changes made should be in communicating to users, rather than altering the current system. However, the average novice user would most likely have problems installing, configuring, and using Tor Browser \cite{clark2007usability}. Other usability concerns include the increased latency in using Tor. Even though Tor is a low-latency anonymizing system, there is a noticeable difference in user experience \cite{fabian2010privately}. With usability as intricately linked to the anonymity of its users as it is, additional research to further improve usability is a worthwhile endeavor. Work by Norcie investigates ``stop points,'' or point where a user would give up in frustration, in installation and use of Tor Browser \cite{norcie2012eliminating}. We contribute in the same spirit, also identifying stop points in the system, but also gauging users' understanding of features, and investigating ways to improve the user experience.

### 2015-03-20 tex-inputs/experiment.tex
Rough out experiment and results sections.

%!TEX root = ../paper.tex

\section{Experiment}

Recruited through journalist contacts.

Ran five experiments.

One-on-one with researcher.
Researcher limited interaction.
Demo cognitive walkthrough.
Cognitive walkthrough understanding task (Zimbabwe).

List of tasks.
Removed "Configure" from list of tasks after p2 because of confusion.

Live viewing by Tor Project developers.

Transcribed audio and made captioned screen recording videos.

\section{Results}

Common errors and confusion.

Apple Gatekeeper problems,
difficulty of fixing (concerns with the App Store).

Selected interesting quotes.

Number of new tickets created and fixed.

### 2015-04-07 PETS2015-paper/paper.tex
make separate folders for cs261n and PETS papers

\documentclass{acm_proc_article-sp}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}

\def\etal{{\it et al.~}}
\newenvironment{packed_enum}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}}
\newenvironment{packed_item}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

\begin{document}
\input{tex-inputs/title.tex}
\input{tex-inputs/abstract.tex}
\input{tex-inputs/introduction.tex}
\input{tex-inputs/related_work.tex} 
\input{tex-inputs/experiment.tex}
\input{tex-inputs/conclusion.tex}

\bibliographystyle{abbrv}
\bibliography{bibliography.bib} 
\end{document}

### 2015-04-07 cs261n-paper/tex-inputs/title.tex
make separate folders for cs261n and PETS papers

%!TEX root = ../paper.tex

\title{Assessing Usability of Tor Browser}
\numberofauthors{1}
\author{
 \alignauthor David Fifield\textsuperscript{1} and Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,2}, David Wagner\textsuperscript{1}\\
   \vspace{0.5em}
   \affaddr{\textsuperscript{1}University of California, Berkeley, \{fifield,lnl,egelman,daw\}@cs.berkeley.edu}, \\
   \affaddr{\textsuperscript{2}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
}

%\numberofauthors{1}
%\author{
% \alignauthor Anonymous\\
%   \vspace{0.5em}
%   \affaddr{Some Place}
%}
\maketitle

### 2015-04-10 PETS2015-paper/paper.tex
consent form done
Copy tex-inputs/* contents into paper.tex.

@@
 \begin{document}
-\input{tex-inputs/title.tex}
-\input{tex-inputs/abstract.tex}
-\input{tex-inputs/introduction.tex}
-\input{tex-inputs/related_work.tex} 
-\input{tex-inputs/experiment.tex}
-\input{tex-inputs/conclusion.tex}
+
+\title{Assessing Usability of Tor Browser}
+\numberofauthors{1}
+\author{
+ \alignauthor David Fifield\textsuperscript{1} and Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,2}, David Wagner\textsuperscript{1}\\
+   \vspace{0.5em}
+   \affaddr{\textsuperscript{1}University of California, Berkeley, \{fifield,lnl,egelman,daw\}@cs.berkeley.edu}, \\
+   \affaddr{\textsuperscript{2}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
+}
+
+%\numberofauthors{1}
+%\author{
+% \alignauthor Anonymous\\
+%   \vspace{0.5em}
+%   \affaddr{Some Place}
+%}
+\maketitle
+{\color {red} TODO: write the paper for PETS currently, it is the same as the class paper..}
+
+\begin{abstract}
+Abstract here.
+\end{abstract}
+
+% A category with the (minimum) three required fields
+%\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
+
+%\terms{Human Factors}{Measurement}{Security}
+
+\keywords{Privacy, Security, User Studies, Anonymity, Tor} % NOT required for Proceedings
+
+\section{Introduction}
+
+Text here.
+
+\section{Related Work}
+In this section, we outline previous research regarding how users understand and act on the Internet, communicating relevant risks to users, and usability of Tor Browser
+
+\subsection{User Perceptions and Behaviors}
+It is not surprising to note that the general public is very willing to trade their personal information for little rewards \cite{norberg2007privacy}.
+A part of this phenomenon is due to the fact that the Internet provides instant gratification for this exchange \cite{acquisti2004privacy}.
+Indeed, there is a discrepancy between users' reported privacy preferences and their browsing habits \cite{jensen2005privacy}.
+
+The behavior profiles, as well as the demographics of Tor Browser, are kept anonymous for obvious reasons.
+No one knows exactly what the average Tor user is like.
+Some information can be inferred from the bug reports filed by users, but this is a self-selecting subset of the users who are arguably much more motivated and technically savvy than the average user.
+Anecdotes are another source to gain an understanding of the average user, although these may not be ground truth.
+A surprising resource is research investigating attacks on Tor users.
+Le~Blond \etal trace back and profile a subset of users in the process, and talk about the results \cite{blond2011one}.
+However, this is also a small subset of the user space.
+
+\subsection{Risk Communication}
+Effectively communicating the current risks to a user can have a significant impact on user behavior.
+A field study of browser warnings show that browser warnings do have the potential to greatly affect user behavior, and work somewhat well in practice \cite{akhawe2013alice}.
+However, many browsers and their warnings have a history of failing to inform users, who become habituated to warnings; active warnings which interrupt the user process can be a more effective warning mechanism \cite{egelman2008you}.
+Warnings are critical in informing users for Tor Browser, since consequences of becoming deanonymized can mean drastic consequences, especially users who live in countries which have outlawed encryption or employ nation-state level censorship \cite{crypto_wikipedia_2015,china_wikipedia_2015}.
+
+\subsection{Tor Browser and Usability}
+
+Tor, the clear frontrunner today in anonymous browsing, was specifically designed with usability, or the ease of use, in mind \cite{tor_wikipedia_2015, dingledine2004tor}.
+Although usability is generally critical to the security of any system, this human factors field has traditionally played a limited role in research \cite{cranor2005security}.
+However, anonymous systems especially benefit from usability.
+Usability means more users--and more users mean more security and privacy in such systems \cite{dingledine2006anonymity}.
+Currently, a wide range of people use Tor Browser, including normal people, militaries, journalists, law enforcements, activists, businessmen, bloggers, and IT professionals \cite{torproject_2015}.
+
+As a whole, Tor is very usable.
+This is evidenced by the popularity of the system.
+Clark's usability study of Tor Browser and related software find that in general, Tor Browser is very usable, and suggest that changes made should be in communicating to users, rather than altering the current system.
+However, the average novice user would most likely have problems installing, configuring, and using Tor Browser \cite{clark2007usability}.
+Other usability concerns include the increased latency in using Tor.
+Even though Tor is a low-latency anonymizing system, there is a noticeable difference in user experience \cite{fabian2010privately}.
+With usability as intricately linked to the anonymity of its users as it is, additional research to further improve usability is a worthwhile endeavor.
+Work by Norcie investigates ``stop points,'' or point where a user would give up in frustration, in installation and use of Tor Browser \cite{norcie2012eliminating}.
+We contribute in the same spirit, also identifying stop points in the system, but also gauging users' understanding of features, and investigating ways to improve the user experience.
+
+\section{Experiment}
+
+Recruited through journalist contacts.
+
+Ran five experiments.
+
+One-on-one with researcher.
+Researcher limited interaction.
+Demo cognitive walkthrough.
+Cognitive walkthrough understanding task (Zimbabwe).
+
+List of tasks.
+Removed "Configure" from list of tasks after p2 because of confusion.
+
+Live viewing by Tor Project developers.
+
+Transcribed audio and made captioned screen recording videos.
+
+\section{Results}
+
+Common errors and confusion.
+
+Apple Gatekeeper problems,
+difficulty of fixing (concerns with the App Store).
+
+Selected interesting quotes.
+
+As a result of our study,
+our partners at the Tor Project created 16 new tickets in their bug tracker~\cite{uxsprint2015-tickets}.
+Seven of those tickets were fixed as of this writing,
+with others in progress.
+
+\section{Conclusion}
+
+Text here.
 

### 2015-04-10 PETS2015-paper/paper.tex
new PETS template
new sections

--- 2015-04-07 PETS2015-paper/paper.tex
@@
-\documentclass{acm_proc_article-sp}
+\documentclass{sig-alternate-hotpets15}
 \usepackage{color}
@@
 \begin{document}
-\input{tex-inputs/title.tex}
-\input{tex-inputs/abstract.tex}
-\input{tex-inputs/introduction.tex}
-\input{tex-inputs/related_work.tex} 
-\input{tex-inputs/experiment.tex}
-\input{tex-inputs/conclusion.tex}
+
+\title{Assessing Usability of Tor Browser}
+\numberofauthors{1}
+\author{
+ \alignauthor David Fifield\textsuperscript{1} and Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,2}, David Wagner\textsuperscript{1}\\
+   \vspace{0.5em}
+   \affaddr{\textsuperscript{1}University of California, Berkeley, \{fifield,lnl,egelman,daw\}@cs.berkeley.edu}, \\
+   \affaddr{\textsuperscript{2}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
+}
+
+%\numberofauthors{1}
+%\author{
+% \alignauthor Anonymous\\
+%   \vspace{0.5em}
+%   \affaddr{Some Place}
+%}
+\maketitle
+{\color {red} TODO: write the paper for PETS currently, it is the same as the class paper..}
+
+\begin{abstract}
+Abstract here.
+\end{abstract}
+
+% A category with the (minimum) three required fields
+%\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
+
+%\terms{Human Factors}{Measurement}{Security}
+
+\keywords{Privacy, Security, User Studies, Anonymity, Tor} % NOT required for Proceedings
+
+\section{What we already did/background stuff}
+
+Text here.
+
+\section{Design}
+In this section, we outline previous research regarding how users understand and act on the Internet, communicating relevant risks to users, and usability of Tor Browser
+
+\section{What we want feedback on}
 

### 2015-04-10 PETS2015-paper/paper.tex
deleted useless stuff
Add a cite to make it compile.
Rough draft of abstract.

@@
 \maketitle
-{\color {red} TODO: write the paper for PETS currently, it is the same as the class paper..}
 
 \begin{abstract}
-Abstract here.
+Our talk will be about ongoing experiments aimed at
+assessing and improving the usability of Tor Browser.
+There have been been no major usability evaluations of
+Tor Browser since the introduction of the 4.0 series,
+which introduced radical UI changes.
+We will briefly describe the results of a completed study
+that examined downloading and installing the browser
+and using it for basic browsing tasks.
+This study uncovered a number of bugs and stopping points
+and has already effected concrete change in the browser.
+We will describe our plans for future studies aimed at
+isolating specific browser features in depth,
+with a detailed design of an experiment to evaluate
+Tor Browser as a tool for censorship circumvention.
+We solicit feedback on our experimental design
+and the specific features of the browser that we are testing.
 \end{abstract}
-
-% A category with the (minimum) three required fields
-%\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
-
-%\terms{Human Factors}{Measurement}{Security}
 
@@
 Text here.
+\cite{norcie2012eliminating}
 

### 2015-04-10 PETS2015-paper/paper.tex
rough parts..

--- 2015-04-10 PETS2015-paper/paper.tex
@@
 \maketitle
-{\color {red} TODO: write the paper for PETS currently, it is the same as the class paper..}
 
@@
 
-% A category with the (minimum) three required fields
-%\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
-
-%\terms{Human Factors}{Measurement}{Security}
-
 \keywords{Privacy, Security, User Studies, Anonymity, Tor} % NOT required for Proceedings
@@
 \section{What we already did/background stuff}
+Tor is an anonymity tool which is used by a lot of people.
+It is important (prove this/cite stuff/say something more meaningful about this) and works well.
+However, there are complaints that Tor is not usable.
+Norcie did an experiment \cite{norcie2012eliminating} which identified stopping points in Tor browser, finding out when people would get frustrated with Tor so much they would stop using it.
+But what about the people who are using Tor?
+what usability issues would thee be if people were not stopped?
 
-Text here.
+To our knowledge, that has been the only user study of Tor.
+Since then, Tor has a lot of updates.
+Additionally, there were a lot of features that were untested.
+We ran a small pilot study on 5 journalists which involved a cognitive walkthrough.(explain cognitive walkthrough if necessary).
+We did this to find new stopping points, but also to see how they would download Tor, if they could understand the address bar/menu, how well they were able to complete basic tasks (searching, setting new circuits, etc), and generally if they had any usability complaints about the browser.
+
+Recruitment here.
+Demographics here.
+Setup here.
+Explain that other Tor users could see this as well.
+How long each the experiment took on average here.
+(put any misc details or additional methodology things here).
+The result was that people did have difficulty with X, Y, Z.
 

### 2015-04-10 PETS2015-paper/paper.tex

@@
 \begin{abstract}
-Abstract here.
+Our talk will be about ongoing experiments aimed at
+assessing and improving the usability of Tor Browser.
+There have been been no major usability evaluations of
+Tor Browser since the introduction of the 4.0 series,
+which introduced radical UI changes.
+We will briefly describe the results of a completed study
+that examined downloading and installing the browser
+and using it for basic browsing tasks.
+This study uncovered a number of bugs and stopping points
+and has already effected concrete change in the browser.
+We will describe our plans for future studies aimed at
+isolating specific browser features in depth,
+with a detailed design of an experiment to evaluate
+Tor Browser as a tool for censorship circumvention.
+We solicit feedback on our experimental design
+and the specific features of the browser that we are testing.
 \end{abstract}

### 2015-04-10 PETS2015-paper/paper.tex
lol

@@
 \section{Design}
+\#STORYTIMEE
+
 In this section, we outline previous research regarding how users understand and act on the Internet, communicating relevant risks to users, and usability of Tor Browser
@@
 
+1) testing the pluggable transports
+2) censorship environments
+3) list of tasks
+4) general design feedback (size, recruitment pool --ie general or journalists)
+
 \bibliographystyle{abbrv}

### 2015-04-10 PETS2015-paper/paper.tex
filler stuff

--- 2015-04-10 PETS2015-paper/paper.tex
@@
 \section{Design}
-In this section, we outline previous research regarding how users understand and act on the Internet, communicating relevant risks to users, and usability of Tor Browser
+\#STORYTIMEE  about why we chose this experiment.
+
+Design of experiment.
+
+Methodology of experiment.
+
+What we hope to get from this experiment.
 
 \section{What we want feedback on}
+
+\noindent {\bfseries 1. testing the pluggable transports} blah explain ourselves.
+
+\noindent {\bfseries 2. censorship environments} blah explain ourselves.
+
+\noindent {\bfseries 3. list of tasks} blah explain ourselves.
+
+\noindent {\bfseries 4. general design feedback} (size, recruitment pool --ie general or journalists) blah explain ourselves.
 

### 2015-04-10 PETS2015-paper/paper.tex
Placeholder resources section.
abstract editing?
made a note in the abstract.

@@
 Tor Browser as a tool for censorship circumvention.
+{\color {red}LL: I don't know how to say this, but I want the fact that we are evaluating it from a different standpoint --ie as a censorship circumvention tool, to stand out more.
+Also, we spend more abstract real estate talking about the first experiment rather than our design, which I think should be flipped.
+But for right now, I can't think of what exactly to fix so I'll look at this later.}
 We solicit feedback on our experimental design
@@
 
-What we hope to get from this experiment.
+What we hope to get from this experiment
 
@@
 
+\section{Resources}
+
+\url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}
+
+\url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}
+
+\url{https://people.torproject.org/~dcf/uxsprint2015/}
+
 \bibliographystyle{abbrv}

### 2015-04-10 PETS2015-paper/paper.tex
Summary of censorship environments.

@@
 
+We plan to simulate three censorship environments.
+They are informed by our experience with pluggable transports
+and knowledge of commonly seen censorship techniques.
+They are not meant perfectly to replicate the network environment
+in any particular country; rather, they are abstract simulations
+that are nevertheless inspired by reality.
+
+\begin{itemize}
+\item{Corporate network.}
+A simulation of a corporate or educational firewall.
+Blocks all services but HTTP, HTTPS, and DNS.
+Certain non-work-related domains, like youtube.com and torproject.org,
+are blocked by DNS and HTTP inspection.
+Blocked requests are redirected to a block page.
+\item{DNS-only censor.}
+This censor injects false replies to DNS queries
+for forbidden domain names (DNS poisoning),
+but does not do deep packet inspection on TCP streams.
+Unlike the corporate censor, this censor allows protocols
+other than HTTP, HTTPS, and DNS.
+\item{Comprehensive censor.}
+Employs a variety of techniques, depending on the target.
+May do DNS poisoning, IP blocking, and inspection of TCP streams
+(examining the URL of HTTP requests, for example).
+Some domains may be blocked by DNS and deep packet inspection;
+others may additionally be blocked by IP address.
+Tor relays are blocked by IP address.
+Some domains, like wikipedia.org, may allow HTTP but not HTTPS.
+Blocked requests fail silently (no block page).
+\end{itemize}
+
 \section{What we want feedback on}

### 2015-04-10 PETS2015-paper/paper.tex
Summarize list of tasks.

@@
 
+We will divide our participants into treatments
+by censorship environment.
+All participants will be asked to complete the same
+list of tasks.
+We constructed the list by looking at some of the top
+Alexa sites and imagining what might be reasonable
+and relevant tasks for each
+(that do not require a participant to reveal private information
+like passwords).
+The tasks are not all intended to be challenging to complete.
+Some may not even require the use of Tor Browser,
+depending on the censorship environment in effect.
+
+\begin{itemize}
+\item Do a Google web search.
+\item Watch a YouTube video.
+\item Find the Amazon best-selling books.
+\item Find Yahoo's exchange rate between dollars and euros.
+\item Read the Wikipedia featured article.
+\item Find the Twitter trending topics.
+\item Find directions on Bing Maps.
+\end{itemize}
+
 \section{What we want feedback on}

### 2015-04-10 PETS2015-paper/paper.tex
horrible design storywriting.

@@
 \section{Design}
-\#STORYTIMEE  about why we chose this experiment.
+After our first experiment, it was clear to us that so many of the features had been left uninvestigated--such as advanced web browsing tasks, the configuration menu, (what else were we going to investigate?), etc.
+But rather than selecting the features to study in isolation, we decided to study the new context in which the Tor browser is being used, censorship circumvention.
+To our knowledge, this is the first user study investigating the usability of Tor as a censorship circumvention tool, rather than an anonymity tool.
 
-Design of experiment.
+For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both.
+There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use.
+The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.
 
-Methodology of experiment.
+We start off the experiment by telling them that they are in an adversarial setting, and that some websites are blocked and some websites are not.
+We will instruct them to visit notblocked.com and also blocked.com to illustrate the situation that they are in.
+We will also explain what Tor is, and how they can use it if necessary {\color {red} is this true?..
+or what happens?} We will them instruct them to complete the set of tasks.
+We designed the experiment so that the users are able to complete some easy tasks without having to use a censorship circumvention tool.
+To complete all the tasks, the participants will ultimately need to get the correct configuration settings for the country they are simulated to be in.
+We will end the experiment with a survey which asks them things like their security background, tech exposure, what was unexpected, what was hard, etc.
 
-What we hope to get from this experiment
+{\color {red} might be too much}We plan to recruit at least 120 (to 200?) users for the purpose of this study.
+This study will be performed at the Experimental Social Science Laboratory (Xlab) at the University of California, Berkeley.
+The laboratory space consists of 36 Toshiba Tecra R850 laptops in 6 rows of 6 laptops each, with cubicle walls separating each laptop.
+We used individual host firewalls to simulate the censorship environments.
+We plan to write a browser extension to measure when users visit what websites in order to log which websites they were successfully able to visit.
+The total length of the experiment should be less than an hour.
+Participants will be compensated \$30 for their time, which is more to cover minimum wage and transportation costs.
+
+We plan to analyze: which configuration tasks are hard (bridges vs proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.
 

### 2015-04-10 PETS2015-paper/paper.tex
tigher spacing for the tasks list
What we want feedback on.

@@
 
-\begin{itemize}
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
 \item Do a Google web search.
@@
 
-\noindent {\bfseries 1. testing the pluggable transports} blah explain ourselves.
+During the question-and-answer session,
+we will be especially interested in soliciting feedback
+on these topics:
 
-\noindent {\bfseries 2. censorship environments} blah explain ourselves.
+{\bfseries Targeting specific pluggable transports.}
+Some pluggable transports work in censorship environments
+where others don't.
+Also, some of them require additional information
+(like bridge addresses) before they can work.
+Is there a way to target testing of specific transports?
+Is there anything to infer from participants' selection of transports?
 
-\noindent {\bfseries 3. list of tasks} blah explain ourselves.
+{\bfseries Censorship environments.}
+Our proposed censorship environments are informed
+by real-world censors.
+What other representative environments
+should be tested?
 
-\noindent {\bfseries 4. general design feedback} (size, recruitment pool --ie general or journalists) blah explain ourselves.
+{\bfseries Browsing tasks.}
+Circumvention is broader than the stereotypical
+``dissident blogger'' use case.
+We have invented some tasks that use some of the
+most popular web sites.
+What other browsing tasks make sense to test?
+
+{\bfseries Experimental design.}
+Our initial study was aimed at journalists.
+We plan to remove this restriction in order
+to have a larger participant population.
+We aim to make our results reproducible by publishing
+our software and firewall configurations.
 

### 2015-04-10 PETS2015-paper/paper.tex
formatting for design section

@@
 To our knowledge, this is the first user study investigating the usability of Tor as a censorship circumvention tool, rather than an anonymity tool.
+\\
 
+\noindent {\bfseries Overview}
 For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both.
@@
 We will end the experiment with a survey which asks them things like their security background, tech exposure, what was unexpected, what was hard, etc.
+We plan to analyze: which configuration tasks are hard (bridges vs proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.
+\\
 
-{\color {red} might be too much}We plan to recruit at least 120 (to 200?) users for the purpose of this study.
+\noindent {\bfseries Experiment Execution Details} 
+{\color {red} this subsection might be too much}We plan to recruit at least 120 (to 200?) users for the purpose of this study.
 This study will be performed at the Experimental Social Science Laboratory (Xlab) at the University of California, Berkeley.
@@
 Participants will be compensated \$30 for their time, which is more to cover minimum wage and transportation costs.
+\\
 
-We plan to analyze: which configuration tasks are hard (bridges vs proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.
-
+\noindent {\bfseries Censorship Environment Simulation}
 We plan to simulate three censorship environments.
@@
 
-\begin{itemize}
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
 \item{Corporate network.}
@@
 
+\noindent {\bfseries List of Tasks} 
 We will divide our participants into treatments

### 2015-04-10 PETS2015-paper/paper.tex
formatting feedback section

@@
 on these topics:
+{\color {red} I feel like I am abusing bold text in this paper..}
 
-{\bfseries Targeting specific pluggable transports.}
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item {\bfseries Targeting specific pluggable transports.}
 Some pluggable transports work in censorship environments
@@
 
-{\bfseries Censorship environments.}
+\item {\bfseries Censorship environments.}
 Our proposed censorship environments are informed
@@
 
-{\bfseries Browsing tasks.}
+\item {\bfseries Browsing tasks.}
 Circumvention is broader than the stereotypical
@@
 
-{\bfseries Experimental design.}
+\item {\bfseries Experimental design.}
 Our initial study was aimed at journalists.
@@
 our software and firewall configurations.
+\end{itemize}
 

### 2015-04-10 PETS2015-paper/paper.tex
make previous experiment section less crappy

@@
 \section{What we already did/background stuff}
-Tor is an anonymity tool which is used by a lot of people.
-It is important (prove this/cite stuff/say something more meaningful about this) and works well.
+Tor is the most widely used anonymity browser today.
 However, there are complaints that Tor is not usable.
@@
 Additionally, there were a lot of features that were untested.
-We ran a small pilot study on 5 journalists which involved a cognitive walkthrough.(explain cognitive walkthrough if necessary).
+We ran a small pilot study on 5 journalists which involved a cognitive walk through.(explain cognitive walkthrough if necessary).
 We did this to find new stopping points, but also to see how they would download Tor, if they could understand the address bar/menu, how well they were able to complete basic tasks (searching, setting new circuits, etc), and generally if they had any usability complaints about the browser.
 
-Recruitment here.
+We recruited 5 journalists from Berkeley.
 Demographics here.
-Setup here.
-Explain that other Tor users could see this as well.
+We recorded their screen, what they were saying out loud in their cognitive walk through, and also cast their screen into a room with Tor developers.
+The participants also took an exit survey which estimated their familiarity with technology and security.
 How long each the experiment took on average here.
 (put any misc details or additional methodology things here).
-The result was that people did have difficulty with X, Y, Z.
+The result was that people did have difficulty with downloading the Tor browser because of the gatekeeper icon, did not understand what many of the many options meant, and were confused about why certain things were happening.
 

### 2015-04-10 PETS2015-paper/paper.tex
Add descriptions to resources.

@@
 
-\url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}
+These are online artifacts of our completed pilot study.
 
-\url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}
+\noindent \url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}\\
+\noindent \url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}\\
+\indent Summary and results of the study.
 
-\url{https://people.torproject.org/~dcf/uxsprint2015/}
+\noindent \url{https://people.torproject.org/~dcf/uxsprint2015/}\\
+\indent Subtitled screen recordings.
 

### 2015-04-10 PETS2015-paper/paper.tex
new section

@@
 
-\section{Design}
+\section{Wut new section} 
+perhaps a section on the state of censorship technologies today, and how to evaluate censorship circumvention tools sketching here.
+This gives our work scope and some purpose.
+Our work examines one of many facets which make a censorship circumvention tool a good one, and it's the usability of the system.
+
+%moved this up to this new section 
 After our first experiment, it was clear to us that so many of the features had been left uninvestigated--such as advanced web browsing tasks, the configuration menu, (what else were we going to investigate?), etc.
@@
 To our knowledge, this is the first user study investigating the usability of Tor as a censorship circumvention tool, rather than an anonymity tool.
-\\
 
+\section{Design}
 \noindent {\bfseries Overview}

### 2015-04-10 PETS2015-paper/paper.tex
Minor fixes.

@@
 However, there are complaints that Tor is not usable.
-Norcie did an experiment \cite{norcie2012eliminating} which identified stopping points in Tor browser, finding out when people would get frustrated with Tor so much they would stop using it.
+Norcie~\cite{norcie2012eliminating} did an experiment which identified stopping points in Tor browser, finding out when people would get frustrated with Tor so much they would stop using it.
 But what about the people who are using Tor?
@@
 This study will be performed at the Experimental Social Science Laboratory (Xlab) at the University of California, Berkeley.
-The laboratory space consists of 36 Toshiba Tecra R850 laptops in 6 rows of 6 laptops each, with cubicle walls separating each laptop.
+The laboratory space consists of 36 laptops with cubicle walls separating each laptop.
 We used individual host firewalls to simulate the censorship environments.
@@
 The tasks are not all intended to be challenging to complete.
-Some may not even require the use of Tor Browser,
-depending on the censorship environment in effect.
 

### 2015-04-10 PETS2015-paper/paper.tex
merging stuff
dash

@@
 which introduced radical UI changes.
-We will briefly describe the results of a completed study
-that examined downloading and installing the browser
-and using it for basic browsing tasks.
+We briefly describe the results of a completed study
+that examined the download, install, and 
+and basic browsing behaviors.
 This study uncovered a number of bugs and stopping points
 and has already effected concrete change in the browser.
-We will describe our plans for future studies aimed at
-isolating specific browser features in depth,
-with a detailed design of an experiment to evaluate
-Tor Browser as a tool for censorship circumvention.
+We will describe a future study aimed at
+evaluating Tor Browser as a tool for censorship circumvention, isolating specific browser features in depth in the process. 
 {\color {red}LL: I don't know how to say this, but I want the fact that we are evaluating it from a different standpoint --ie as a censorship circumvention tool, to stand out more.
@@
 %moved this up to this new section 
-After our first experiment, it was clear to us that so many of the features had been left uninvestigated--such as advanced web browsing tasks, the configuration menu, (what else were we going to investigate?), etc.
+After our first experiment, it was clear to us that so many of the features had been left uninvestigated---such as advanced web browsing tasks, the configuration menu, (what else were we going to investigate?), etc.
 But rather than selecting the features to study in isolation, we decided to study the new context in which the Tor browser is being used, censorship circumvention.
@@
 
-\noindent {\bfseries Experiment Execution Details} 
-{\color {red} this subsection might be too much}We plan to recruit at least 120 (to 200?) users for the purpose of this study.
-This study will be performed at the Experimental Social Science Laboratory (Xlab) at the University of California, Berkeley.
-The laboratory space consists of 36 laptops with cubicle walls separating each laptop.
-We used individual host firewalls to simulate the censorship environments.
-We plan to write a browser extension to measure when users visit what websites in order to log which websites they were successfully able to visit.
-The total length of the experiment should be less than an hour.
-Participants will be compensated \$30 for their time, which is more to cover minimum wage and transportation costs.
-\\
-
 \noindent {\bfseries Censorship Environment Simulation}
@@
 \item{Corporate network.}
-A simulation of a corporate or educational firewall.
+A simulation of a enterprise or educational firewall.
 Blocks all services but HTTP, HTTPS, and DNS.
@@
 \noindent {\bfseries List of Tasks} 
-We will divide our participants into treatments
-by censorship environment.
-All participants will be asked to complete the same
-list of tasks.
-We constructed the list by looking at some of the top
-Alexa sites and imagining what might be reasonable
-and relevant tasks for each
-(that do not require a participant to reveal private information
-like passwords).
+The lists of tasks were originally inspired by the top Alexa sites, which gave an idea of relevant and popular browsing behavior, then refined by ethical concerns, filtering out tasks which would require a participant to reveal private information.
+The resulting task list is one which we hope is both representative of how a user might browse the internet, but also give good coverage of sites which are censored today.
+
+All participants will be asked to complete the same list of tasks, regardless of the censorship environment.
+Although every participant will attempt the same set of tasks, the difficulty of completing these tasks will vary on their chosen censorship environment.
 The tasks are not all intended to be challenging to complete.
+Some may not even require the use or Tor Browser, depending on the environment.
 
@@
 \end{itemize}
+
+\noindent {\bfseries Experiment Execution Details} 
+{\color {red} this subsection might be too much}We plan to recruit at least 120 (to 200?) users for the purpose of this study.
+This study will be performed at the Experimental Social Science Laboratory (Xlab) at the University of California, Berkeley.
+The laboratory space consists of 36 laptops with cubicle walls separating each laptop.
+We used individual host firewalls to simulate the censorship environments.
+We plan to write a browser extension to measure when users visit what websites in order to log which websites they were successfully able to visit.
+The total length of the experiment should be less than an hour.
+Participants will be compensated \$30 for their time, which is more to cover minimum wage and transportation costs.
+\\
 

### 2015-04-10 PETS2015-paper/paper.tex
linda's rewording of not-linda sections

@@
 %moved this up to this new section 
-After our first experiment, it was clear to us that so many of the features had been left uninvestigated---such as advanced web browsing tasks, the configuration menu, (what else were we going to investigate?), etc.
+After our first experiment, it was clear to us that so many of the features had been left uninvestigated--such as advanced web browsing tasks, the configuration menu, (what else were we going to investigate?), etc.
 But rather than selecting the features to study in isolation, we decided to study the new context in which the Tor browser is being used, censorship circumvention.

### 2015-04-10 PETS2015-paper/paper.tex
Typo.
remove red comments

--- 2015-04-10 PETS2015-paper/paper.tex
@@
 }
-
-%\numberofauthors{1}
-%\author{
-% \alignauthor Anonymous\\
-%   \vspace{0.5em}
-%   \affaddr{Some Place}
-%}
 \maketitle
 
+% is the abstract missing some oomph? 
+% I don't know how much the storyline is showing through.. or what we are testing. 
 \begin{abstract}
@@
 evaluating Tor Browser as a tool for censorship circumvention, isolating specific browser features in depth in the process. 
-{\color {red}LL: I don't know how to say this, but I want the fact that we are evaluating it from a different standpoint --ie as a censorship circumvention tool, to stand out more.
-Also, we spend more abstract real estate talking about the first experiment rather than our design, which I think should be flipped.
-But for right now, I can't think of what exactly to fix so I'll look at this later.}
 We solicit feedback on our experimental design
@@
 
-\keywords{Privacy, Security, User Studies, Anonymity, Tor} % NOT required for Proceedings
+\keywords{Privacy, Security, User Studies, Anonymity, Tor}
 
@@
 \item{Corporate network.}
-A simulation of a enterprise or educational firewall.
+A simulation of an enterprise or educational firewall.
 Blocks all services but HTTP, HTTPS, and DNS.
@@
 
+%frame this in the sense that we are saying, ``we have this figued out. we want feedback on other things.''
 \noindent {\bfseries Experiment Execution Details} 
-{\color {red} this subsection might be too much}We plan to recruit at least 120 (to 200?) users for the purpose of this study.
+We plan to recruit at least 120 (to 200?) users for the purpose of this study.
 This study will be performed at the Experimental Social Science Laboratory (Xlab) at the University of California, Berkeley.
@@
 on these topics:
-{\color {red} I feel like I am abusing bold text in this paper..}
 

### 2015-04-11 PETS2015-paper/paper.tex
david and linda's passthrough

@@
 We briefly describe the results of a completed study
-that examined the download, install, and 
-and basic browsing behaviors.
+that examined the download and installation processes, 
+as well as basic browsing behaviors.
 This study uncovered a number of bugs and stopping points
-and has already effected concrete change in the browser.
+which has already effected concrete change in the browser.
 We will describe a future study aimed at
 evaluating Tor Browser as a tool for censorship circumvention, isolating specific browser features in depth in the process. 
-We solicit feedback on our experimental design
-and the specific features of the browser that we are testing.
+To this end, we will conduct a large-scale user study examining hundreds of users on how they navigate Tor's configuration wizard to complete seven browsing tasks in three different adversarial settings.
+We solicit feedback in order to improve the representation
+of our study and its design.
 \end{abstract}
 
-\keywords{Privacy, Security, User Studies, Anonymity, Tor}
+\keywords{Censorship, Security, User Studies, Anonymity, Tor}
 
-\section{What we already did/background stuff}
+\section{Inspiration}
 Tor is the most widely used anonymity browser today.
@@
 To our knowledge, that has been the only user study of Tor.
-Since then, Tor has a lot of updates.
+Since then, Tor has had a lot of updates.
 Additionally, there were a lot of features that were untested.
-We ran a small pilot study on 5 journalists which involved a cognitive walk through.(explain cognitive walkthrough if necessary).
-We did this to find new stopping points, but also to see how they would download Tor, if they could understand the address bar/menu, how well they were able to complete basic tasks (searching, setting new circuits, etc), and generally if they had any usability complaints about the browser.
+We ran a small pilot study of five journalists which involved a cognitive walk through in which participants explained the motivation for their actions and any confusion that they had during the process.
+We did this to find new stopping points, and sources of confusion.
+But in the process, we were also able to observer how users would download Tor, if they could understand the address bar/menu, how well they were able to complete basic tasks (searching, setting new circuits, etc), and generally if they had any usability complaints about the browser.
 
-We recruited 5 journalists from Berkeley.
-Demographics here.
-We recorded their screen, what they were saying out loud in their cognitive walk through, and also cast their screen into a room with Tor developers.
+We recruited five journalists from Berkeley by reaching out to journalist contacts. 
+%Demographics here. 
+During the study, we recorded their screen, what they were saying out loud in their cognitive walk through, and also cast their screen into a room with Tor developers.
 The participants also took an exit survey which estimated their familiarity with technology and security.
-How long each the experiment took on average here.
-(put any misc details or additional methodology things here).
+On average, participants took 26 minutes to complete the study ($\sigma$ = 7 min).
 The result was that people did have difficulty with downloading the Tor browser because of the gatekeeper icon, did not understand what many of the many options meant, and were confused about why certain things were happening.
 
-\section{Wut new section} 
-perhaps a section on the state of censorship technologies today, and how to evaluate censorship circumvention tools sketching here.
-This gives our work scope and some purpose.
-Our work examines one of many facets which make a censorship circumvention tool a good one, and it's the usability of the system.
+\section{Contextual Evaluation} 
+After our first experiment, it was clear to us that so many of the features had been left uninvestigated---such as advanced web browsing tasks, the configuration menu, automatic updates, and identity and cookie management.
+But rather than selecting the features to study in isolation, we decided to focus on an important use case of Tor browser, censorship circumvention.
+To our knowledge, this is the first user study investigating the usability of Tor as a censorship circumvention tool, rather than an anonymity tool.
 
-%moved this up to this new section 
-After our first experiment, it was clear to us that so many of the features had been left uninvestigated---such as advanced web browsing tasks, the configuration menu, (what else were we going to investigate?), etc.
-But rather than selecting the features to study in isolation, we decided to study the new context in which the Tor browser is being used, censorship circumvention.
-To our knowledge, this is the first user study investigating the usability of Tor as a censorship circumvention tool, rather than an anonymity tool.
+Tor has grown beyond its original purpose and has become an important Internet circumvention tool.
+Our work is the first to analyze Tor as a censorship circumvention tool, rather than an anonymous browsing tool.
+We specifically examine one  essential facet for a good censorship circumvention tool: its usability.
+Our analysis the configuration dialog of the browser has new significance because of the new ways Tor is used.
 
@@
 We will instruct them to visit notblocked.com and also blocked.com to illustrate the situation that they are in.
-We will also explain what Tor is, and how they can use it if necessary {\color {red} is this true?..
-or what happens?} We will them instruct them to complete the set of tasks.
-We designed the experiment so that the users are able to complete some easy tasks without having to use a censorship circumvention tool.
+We will also explain what Tor is, and how they can use it if necessary, and ask them to complete the set of tasks.
 To complete all the tasks, the participants will ultimately need to get the correct configuration settings for the country they are simulated to be in.
@@
 
+%%%%%%%%%%%%%PROOF READ THE REST
+
 %frame this in the sense that we are saying, ``we have this figued out. we want feedback on other things.''
@@
 We plan to recruit at least 120 (to 200?) users for the purpose of this study.
-This study will be performed at the Experimental Social Science Laboratory (Xlab) at the University of California, Berkeley.
+This makes it largest user study to date on Tor (check this) This study will be performed at the Experimental Social Science Laboratory (Xlab) at the University of California, Berkeley.
 The laboratory space consists of 36 laptops with cubicle walls separating each laptop.

### 2015-04-13 PETS2015-paper/paper.tex
Getting rid of awkward second section and reformatting the abstract and introduction section.

@@
 
-\title{Assessing Usability of Tor Browser}
+\title{Tor's Usability for Censorship Circumvention}
 \numberofauthors{1}
@@
 \begin{abstract}
-Our talk will be about ongoing experiments aimed at
-assessing and improving the usability of Tor Browser.
+
+Tor has grown beyond its original purpose and has become an important Internet circumvention tool.
+Our work is the first to analyze Tor as a censorship circumvention tool, rather than an anonymous browsing tool. 
+We specifically examine one  essential facet for a good censorship circumvention tool: its usability. 
+Our analysis the configuration dialog of the browser has new significance because of the new ways Tor is used.
+Our talk will describe a future study aimed at evaluating Tor Browser as a tool for censorship circumvention,
+ isolating specific browser features in depth in the process. 
+To this end, we will conduct a large-scale user study examining hundreds of users 
+on how they navigate Tor's configuration wizard to complete seven browsing tasks in three different adversarial settings. 
+We solicit feedback in order to improve the representation of our study and its design.
+\end{abstract}
+
+\keywords{Censorship, Security, User Studies, Anonymity, Tor}
+
+\section{Tor's Usability}
+%Idea is to cover background on Tor's usability as an anonymity tool, and then highlight the shift in focus to evaluating Tor's usability as a censorship circumvention tool.
+
+Tor is the most widely used anonymity tool today.
+However, there are complaints that Tor is not usable.
+Norcie~\cite{norcie2012eliminating} did an experiment which identified stopping points in Tor browser,
+finding out when people would get frustrated with Tor so much they would stop using it. 
+%redo this next couple sentences into something better
+But what about the people who are using Tor? what usability issues would thee be if people were not stopped? 
+To our knowledge, that has been the only user study of Tor. 
+Since then, Tor has had a lot of updates. 
+Additionally, there were a lot of features that were untested. 
 There have been been no major usability evaluations of
@@
 which introduced radical UI changes.
+
 We briefly describe the results of a completed study
@@
 which has already effected concrete change in the browser.
-We will describe a future study aimed at
-evaluating Tor Browser as a tool for censorship circumvention, isolating specific browser features in depth in the process. 
-To this end, we will conduct a large-scale user study examining hundreds of users on how they navigate Tor's configuration wizard to complete seven browsing tasks in three different adversarial settings.
-We solicit feedback in order to improve the representation
-of our study and its design.
-\end{abstract}
 
-\keywords{Censorship, Security, User Studies, Anonymity, Tor}
-
-\section{Inspiration}
-Tor is the most widely used anonymity browser today.
-However, there are complaints that Tor is not usable.
-Norcie~\cite{norcie2012eliminating} did an experiment which identified stopping points in Tor browser, finding out when people would get frustrated with Tor so much they would stop using it.
-But what about the people who are using Tor?
-what usability issues would thee be if people were not stopped?
-
-To our knowledge, that has been the only user study of Tor.
-Since then, Tor has had a lot of updates.
-Additionally, there were a lot of features that were untested.
-We ran a small pilot study of five journalists which involved a cognitive walk through in which participants explained the motivation for their actions and any confusion that they had during the process.
+We ran a small pilot study of five journalists which involved a cognitive walk through in which 
+participants explained the motivation for their actions and any confusion that they had during the process. 
 We did this to find new stopping points, and sources of confusion. 
-But in the process, we were also able to observer how users would download Tor, if they could understand the address bar/menu, how well they were able to complete basic tasks (searching, setting new circuits, etc), and generally if they had any usability complaints about the browser.
+But in the process, we were also able to observe how users would download Tor, 
+if they could understand the address bar/menu, how well they were able to complete basic tasks
+(searching, setting new circuits, etc), and generally if they had any usability complaints about the browser.
 
@@
 
-\section{Contextual Evaluation} 
-After our first experiment, it was clear to us that so many of the features had been left uninvestigated---such as advanced web browsing tasks, the configuration menu, automatic updates, and identity and cookie management.
-But rather than selecting the features to study in isolation, we decided to focus on an important use case of Tor browser, censorship circumvention.
-To our knowledge, this is the first user study investigating the usability of Tor as a censorship circumvention tool, rather than an anonymity tool.
-
-Tor has grown beyond its original purpose and has become an important Internet circumvention tool.
-Our work is the first to analyze Tor as a censorship circumvention tool, rather than an anonymous browsing tool.
-We specifically examine one  essential facet for a good censorship circumvention tool: its usability.
-Our analysis the configuration dialog of the browser has new significance because of the new ways Tor is used.
+After our first  usability evaluation of Tor, it was clear to us that so many of the features had been left unevaluated---such as advanced web browsing tasks, the configuration menu, automatic updates, and identity and cookie management.
+%say something about how we resolved this somehow, and how it doesn't necessarily need our attention now
+We found that the most effective way to resolve the problems encountered was more user guidance and interface remodeling rather than continued user observations.
+%emphasize how we are aiming for new research, not new test cases for debugging an interface
+Rather than selecting the features to study in isolation, 
+we decided to focus on an important use case of Tor browser, censorship circumvention. 
+%say something along the lines of ``x people are using it for this, and there's no work on it,'' 
+%if there are stats on this type of thing.
+To our knowledge, this is the first user study investigating the usability of Tor as a 
+censorship circumvention tool, rather than an anonymity tool.
 
@@
 \noindent {\bfseries Experiment Execution Details} 
-We plan to recruit at least 120 (to 200?) users for the purpose of this study.
+We plan to recruit around 150 users for the purpose of this study.
 This makes it largest user study to date on Tor (check this) This study will be performed at the Experimental Social Science Laboratory (Xlab) at the University of California, Berkeley.

### 2015-04-16 PETS2015-paper/paper.tex
Put equals sign inside $$.
Slightly better formatting for resources.

@@
 The participants also took an exit survey which estimated their familiarity with technology and security.
-On average, participants took 26 minutes to complete the study ($\sigma$ = 7 min).
+On average, participants took 26 minutes to complete the study ($\sigma = 7$~min).
 The result was that people did have difficulty with downloading the Tor browser because of the gatekeeper icon, did not understand what many of the many options meant, and were confused about why certain things were happening.
@@
 These are online artifacts of our completed pilot study.
+Summary and results, including resulting browser changes:
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item \url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}
+\item \url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}
+\end{itemize}
 
-\noindent \url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}\\
-\noindent \url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}\\
-\indent Summary and results of the study.
-
-\noindent \url{https://people.torproject.org/~dcf/uxsprint2015/}\\
-\indent Subtitled screen recordings.
+Subtitled screen videos:
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item \url{https://people.torproject.org/~dcf/uxsprint2015/}
+\end{itemize}
 

### 2015-04-16 PETS2015-paper/paper.tex
Phrasing.

@@
 The lists of tasks were originally inspired by the top Alexa sites, which gave an idea of relevant and popular browsing behavior, then refined by ethical concerns, filtering out tasks which would require a participant to reveal private information.
-The resulting task list is one which we hope is both representative of how a user might browse the internet, but also give good coverage of sites which are censored today.
+The resulting task list is one which we hope is both representative of how a user might browse the internet, and also gives good coverage of sites which are censored today.
 

### 2015-04-16 PETS2015-paper/paper.tex
Spell out "versus".

@@
 We will end the experiment with a survey which asks them things like their security background, tech exposure, what was unexpected, what was hard, etc.
-We plan to analyze: which configuration tasks are hard (bridges vs proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.
+We plan to analyze: which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.
 \\

### 2015-04-16 PETS2015-paper/paper.tex
rewording experiment execution details

@@
 \noindent {\bfseries Experiment Execution Details} 
-We plan to recruit around 150 users for the purpose of this study.
-This makes it largest user study to date on Tor (check this) This study will be performed at the Experimental Social Science Laboratory (Xlab) at the University of California, Berkeley.
-The laboratory space consists of 36 laptops with cubicle walls separating each laptop.
-We used individual host firewalls to simulate the censorship environments.
-We plan to write a browser extension to measure when users visit what websites in order to log which websites they were successfully able to visit.
-The total length of the experiment should be less than an hour.
-Participants will be compensated \$30 for their time, which is more to cover minimum wage and transportation costs.
-\\
+We plan to recruit up to 200 users for the purpose of this study, 
+making it largest user study to date examining Tor (check this). 
+This study will be conducted at the Experimental Social Science Laboratory (Xlab)
+at the University of California, Berkeley, which consists of 36 laptops with 
+cubicle walls separating each laptop. We will use individual host firewalls to simulate
+the censorship environments and will write a browser extension to 
+log when user activity, such as what websites they were successfully able to visit. 
+The total length of the experiment, including briefing, completing the censorship 
+circumvention tasks, exit survey, and debriefing, will take less than an hour. 
+Participants will be compensated \$30 for their time, 
+which is more to cover minimum wage and transportation costs.  \\
 

### 2015-04-16 PETS2015-paper/paper.tex
I guess some people don't like contractions.
Period after "etc".

@@
 if they could understand the address bar/menu, how well they were able to complete basic tasks
-(searching, setting new circuits, etc), and generally if they had any usability complaints about the browser.
+(searching, setting new circuits, etc.), and generally if they had any usability complaints about the browser.
 
@@
 Some pluggable transports work in censorship environments
-where others don't.
+where others do not.
 Also, some of them require additional information

### 2015-04-16 PETS2015-paper/paper.tex
changes to targeting specific pluggable transports bullet

--- 2015-04-16 PETS2015-paper/paper.tex
@@
 Some pluggable transports work in censorship environments
-where others don't.
-Also, some of them require additional information
-(like bridge addresses) before they can work.
+where others do not.
+Additionally, some of them require additional information
+(like bridge addresses) before they work.
 Is there a way to target testing of specific transports?
-Is there anything to infer from participants' selection of transports?
+Is there anything to infer from participants' selection of transports, 
+or do we assume they are trying transports at random?
 

### 2015-04-16 PETS2015-paper/paper.tex

--- 2015-04-16 PETS2015-paper/paper.tex
@@
 where others do not.
-Also, some of them require additional information
-(like bridge addresses) before they can work.
+Additionally, some of them require additional information
+(like bridge addresses) before they work.
 Is there a way to target testing of specific transports?
-Is there anything to infer from participants' selection of transports?
+Is there anything to infer from participants' selection of transports, 
+or do we assume they are trying transports at random?
 

### 2015-04-16 PETS2015-paper/paper.tex
Flesh out Gatekeeper sentence.

@@
 On average, participants took 26 minutes to complete the study ($\sigma = 7$~min).
-The result was that people did have difficulty with downloading the Tor browser because of the gatekeeper icon, did not understand what many of the many options meant, and were confused about why certain things were happening.
+The result was that people did have difficulty with installing Tor Browser (principally because of the Gatekeeper code-signing feature on OS~X), did not understand what many of the many options meant, and were confused about why certain things were happening.
 
@@
 \noindent {\bfseries List of Tasks} 
-The lists of tasks were originally inspired by the top Alexa sites, which gave an idea of relevant and popular browsing behavior, then refined by ethical concerns, filtering out tasks which would require a participant to reveal private information.
-The resulting task list is one which we hope is both representative of how a user might browse the internet, and also gives good coverage of sites which are censored today.
+The tasks below were originally inspired by the top Alexa sites, 
+an indication of representative and relevant browsing behavior. 
+We then selected sites which were commonly censored and 
+refined the tasks to remove ethical concerns, such as tasks 
+which would require a participant to reveal private information 
+(such as login information). We hope the resulting tasks convey an idea 
+of sites which are censored today, while remaining representative 
+of how a user might browse the Internet.
 
-All participants will be asked to complete the same list of tasks, regardless of the censorship environment.
-Although every participant will attempt the same set of tasks, the difficulty of completing these tasks will vary on their chosen censorship environment.
+All participants will be asked to complete the same list of tasks, 
+regardless of the censorship environment. 
+Although every participant will attempt the same set of tasks, 
+the difficulty of completing these tasks will vary based on 
+their chosen censorship environment. 
 The tasks are not all intended to be challenging to complete. 
-Some may not even require the use or Tor Browser, depending on the environment.
+Some may not even require the use or Tor Browser, 
+depending on the environment.
 
@@
 
-%%%%%%%%%%%%%PROOF READ THE REST
-
-%frame this in the sense that we are saying, ``we have this figued out. we want feedback on other things.''
 \noindent {\bfseries Experiment Execution Details} 
@@
 \item {\bfseries Experimental design.}
-Our initial study was aimed at journalists.
+Our initial study was aimed at a specific subset of users (journalists).
 We plan to remove this restriction in order
@@
 
-These are online artifacts of our completed pilot study.
-Summary and results, including resulting browser changes:
+Our online artifacts of our completed pilot study, such as 
+the summary, results, and resulting browser changes are below:
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt

### 2015-04-16 PETS2015-paper/paper.tex
wordtweaking to lists of tasks

--- 2015-04-16 PETS2015-paper/paper.tex
@@
 On average, participants took 26 minutes to complete the study ($\sigma = 7$~min).
-The result was that people did have difficulty with installing Tor Browser (principally because of the Gatekeeper code-signing feature on OS~X), did not understand what many of the many options meant, and were confused about why certain things were happening.
+The result was that people did have difficulty with downloading the Tor browser because of the gatekeeper icon, did not understand what many of the many options meant, and were confused about why certain things were happening.
 

### 2015-04-16 PETS2015-paper/paper.tex
More about screen videos.

--- 2015-04-16 PETS2015-paper/paper.tex
@@
 %Demographics here. 
-During the study, we recorded their screen, what they were saying out loud in their cognitive walk through, and also cast their screen into a room with Tor developers.
+During the study, we made a video recording of each participant's computer screen
+and simultaneously projected it
+into another room with Tor developers.
+We recorded what they were saying out loud in their cognitive walk through,
+and later added these words to the screen videos as subtitles.
 The participants also took an exit survey which estimated their familiarity with technology and security.
@@
 The result was that people did have difficulty with installing Tor Browser (principally because of the Gatekeeper code-signing feature on OS~X), did not understand what many of the many options meant, and were confused about why certain things were happening.
+Our talk will feature brief highlights of the screen videos.
 

### 2015-04-16 PETS2015-paper/paper.tex
Fewer dots.

@@
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Targeting specific pluggable transports.}
+\item {\bfseries Targeting specific pluggable transports}
 Some pluggable transports work in censorship environments
@@
 
-\item {\bfseries Censorship environments.}
+\item {\bfseries Censorship environments}
 Our proposed censorship environments are informed
@@
 
-\item {\bfseries Browsing tasks.}
+\item {\bfseries Browsing tasks}
 Circumvention is broader than the stereotypical
@@
 
-\item {\bfseries Experimental design.}
+\item {\bfseries Experimental design}
 Our initial study was aimed at a specific subset of users (journalists).

### 2015-04-16 PETS2015-paper/paper.tex
Change wording for better margins.

@@
 \item {\bfseries Targeting specific pluggable transports}
-Some pluggable transports work in censorship environments
+Some of Tor's pluggable transports work in censorship environments
 where others do not.
@@
 \item {\bfseries Censorship environments}
-Our proposed censorship environments are informed
+Our proposed censorship simulation is informed
 by real-world censors.

### 2015-04-16 PETS2015-paper/paper.tex
abstract redo

--- 2015-04-16 PETS2015-paper/paper.tex
@@
 
-Tor has grown beyond its original purpose and has become an important Internet circumvention tool.
-Our work is the first to analyze Tor as a censorship circumvention tool, rather than an anonymous browsing tool. 
-We specifically examine one  essential facet for a good censorship circumvention tool: its usability. 
-Our analysis the configuration dialog of the browser has new significance because of the new ways Tor is used.
-Our talk will describe a future study aimed at evaluating Tor Browser as a tool for censorship circumvention,
- isolating specific browser features in depth in the process. 
+Tor has grown beyond its original purpose as and has 
+since become an important Internet circumvention tool.
+We specifically examine it usability as a censorship circumvention tool,
+an essential facet for adoption and use.  
+We focus our analysis on the connection configuration dialog of Tor browser,
+as censorship circumvention requires correct transport configurations. %%
+Our talk will describe a future study aimed at evaluating 
+if and how easily users can circumvent censorship using Tor Browser,
+isolating specific browser features to study in the process. 
 To this end, we will conduct a large-scale user study examining hundreds of users 
 on how they navigate Tor's configuration wizard to complete seven browsing tasks in three different adversarial settings. 
-We solicit feedback in order to improve the representation of our study and its design.
+We solicit feedback to improve our study's design.
 \end{abstract}
@@
 %Demographics here. 
-During the study, we made a video recording of each participant's computer screen
-and simultaneously projected it
-into another room with Tor developers.
-We recorded what they were saying out loud in their cognitive walk through,
-and later added these words to the screen videos as subtitles.
+During the study, we recorded their screen, what they were saying out loud in their cognitive walk through, and also cast their screen into a room with Tor developers.
 The participants also took an exit survey which estimated their familiarity with technology and security.
 On average, participants took 26 minutes to complete the study ($\sigma = 7$~min).
-The result was that people did have difficulty with installing Tor Browser (principally because of the Gatekeeper code-signing feature on OS~X), did not understand what many of the many options meant, and were confused about why certain things were happening.
-Our talk will feature brief highlights of the screen videos.
+The result was that people did have difficulty with downloading the Tor browser because of the gatekeeper icon, did not understand what many of the many options meant, and were confused about why certain things were happening.
 

### 2015-04-16 PETS2015-paper/paper.tex
Shorter.
MUHAHAH ORPHANS DEAD

@@
 Unlike the corporate censor, this censor allows protocols
-other than HTTP, HTTPS, and DNS.
+outside a small whitelisted set.
 \item{Comprehensive censor.}
@@
 
-All participants will be asked to complete the same list of tasks, 
+All participants will be given the same set of tasks, 
 regardless of the censorship environment. 

### 2015-05-02 cs261n-paper/paper.tex
talk notes and paper update'

\documentclass{sig-alternate-hotpets15}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}

\def\etal{{\it et al.~}}
\newenvironment{packed_enum}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}}
\newenvironment{packed_item}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

\begin{document}

\title{better title eventually}
\numberofauthors{1}
\author{
 \alignauthor Linda N. Lee, David Fifield\\
   \affaddr{University of California, Berkeley, \{lnl, fifield\}@cs.berkeley.edu} \\
   \vspace{0.5em}
   CS261N Final Report, \today
}
\maketitle

% is the abstract missing some oomph? 
% I don't know how much the storyline is showing through.. or what we are testing. 
\begin{abstract}
It is easy to drastically overestimate user comprehension 
and therefore be misguided for user behavior. 
Even though people download and install things all the time, 
they do not know how to do it securely, and worse, 
they are habituated into doing it a certain way. 
What users had trouble with were the most basic tasks, 
such as downloading and installing Tor, rather than 
nagivating a robust menu or understanding subtleties of security guarentees. 
This is really troubling, and matters for things like Tor. 
We use this insight to fix a bunch of stuff and also 
present a new experiment with a basic enough focus, 
making us the first to focus on censorship too. 
\end{abstract}

\keywords{User Studies, Tor, Anonymity, Censorship, Security}

\section{Introduction} %this should CLEARLY state the results. 
Talk about the results and contributions concretely.
As short as possible summary of UX sprint here. %only what is necessary to understand results. 
Talk about the changes resulted in the Tor browser here.
As short as possible summary of lessons learned, 
and also a short as possible motivation for censorship work here. %yep, same.
Talk about the experiment design quickly here.

\section{Background}  %ramp people up!

\subsection{Tor} 
Talk about anything relevant to Tor. Just enough background so
that people who have never heard of it will know what I am talking
about, but no more than that.

\subsection{User behavior}
Then also talk about any of the behaviors we are trying to mitigate,
or talk about the average user and what they know, how they are motivated,
just sketching out the environment in general.

\subsection{Usable security impact} 
cite work which has made a huge impact on how people use it, and 
other things which still remain broken because of usability issues.

We don't want Tor to be like this, and want people to use it!

\subsection{Censorship} 
Motivational paragraph time about how this is so everywhere.

Talk about the basic methods of censoring, and how it differs 
around the world, which sites are targeted, etc.

Scope the paper here. Talk about how we are not up Cuba-like adversaries.

\section{UX sprint} 
Details. Gory gory details of how it all went down. 
Include the recruitment process, the setup, what the exact 
tasks were for participants, demographics, everything. 
It all should have a home here.

\section{Results}
Present situations which really were unexpected. 
Also extract the golden quotes and state them here 
to prove points I want to make.

\subsection{Impact}
whoo talk about the cool stuff that happened next here. 
This means talking about the tickets and changes made 
to the Tor browser, the start of a user manual, and 
increased Tor UX efforts as a whole.

\subsection{Takeaways} 
highlight what we learned and use this to transition into 
the design of the next experiment.

Wanted reproducibility of experiment.
Wanted more people for a representative population. 
Also make practical considerations such as avoiding transcription.

\section{Experiment Design} 
an informed, user-conscientious, user-focused experiment design to target 
narrow sets of basic features which are used for censorship.

\subsection{Methodology}  
Talk about the justification of the setup and the general 
work flow of an experiment session. Address any details up front
about computers, money, people, etc.

\subsection{Censorship Environments} 
Basically a section like the HOTPETS paper section.
I should add details of exact configurations if available.

\subsection{Tasks}
A section like the HOTPETS paper section. 
I  should add details of exact tasks if available.

\subsection{Feedback} 
Talk about the exit survey and what that covers. 
Explain why we want to know what we are asking about. 
And why this matters.

\section{Discussion} 
Discuss the hypotheses we have here for the experiment.

And any work that needs to be done for the experiment.

Next stps to take after the experiment, can also be here. %is this too far away?

\section{Related Work} %this is distracting to have earlier. %don't overdo the citations. 
The stopping points paper on Tor's usability ~\cite{norcie2012eliminating}. 
And that is pretty much it for Tor usability stuff. %find more if it exists

I guess that other literature on general usability applies here too. %so search for it.

\section{Conclusion} 
Do not repeat the abstract, introduction, or the results section. 
Focus this time to discuss the limitations of the work and broader impacts.

Reach out to the community to make a call for more a focus on usability for security products.

\bibliographystyle{abbrv}
\bibliography{bibliography.bib} 
\end{document}

### 2015-05-11 cs261n-paper/paper.tex
Link to wrapup blog post.
Default style.
started writing a little bit.

@@
-\documentclass{sig-alternate-hotpets15}
+%\documentclass{article}
+\documentclass[letterpaper,twocolumn,10pt]{article}
+\usepackage[margin=0.75in]{geometry}
 \usepackage{color}
@@
 \title{better title eventually}
-\numberofauthors{1}
-\author{
- \alignauthor Linda N. Lee, David Fifield\\
-   \affaddr{University of California, Berkeley, \{lnl, fifield\}@cs.berkeley.edu} \\
-   \vspace{0.5em}
-   CS261N Final Report, \today
+\author{Linda N. Lee, David Fifield\\
+University of California, Berkeley, \{lnl, fifield\}@cs.berkeley.edu
 }
@@
 \end{abstract}
-
-\keywords{User Studies, Tor, Anonymity, Censorship, Security}
 
@@
 \section{UX sprint} 
-Details. Gory gory details of how it all went down. 
-Include the recruitment process, the setup, what the exact 
-tasks were for participants, demographics, everything. 
-It all should have a home here.
-
-\section{Results}
-Present situations which really were unexpected. 
-Also extract the golden quotes and state them here 
-to prove points I want to make.
+Talk about it just enough that it makes a good storyline for the experiment that we 
+are proposing a design of. Motivate it a little bit, and tell a story. Then refer to the 
+Appendix for additional information.
 
@@
 \section{Experiment Design}
-an informed, user-conscientious, user-focused experiment design to target 
-narrow sets of basic features which are used for censorship.
+
+\subsection{WHAT IS THIS}
+
+\noindent {\bfseries Motivation and Background Story} talk about the generalizability of the work, what we aim to find, and what future work this will lead to.
+Be sure to sketch the storyline of honing in on specific features.
+
+Tor has grown beyond its original purpose as and has 
+since become an important Internet circumvention tool.
+We specifically examine it usability as a censorship circumvention tool,
+an essential facet for adoption and use.  
+We focus our analysis on the connection configuration dialog of Tor browser,
+as censorship circumvention requires correct transport configurations. %%
+This study is aimed at evaluating 
+if and how easily users can circumvent censorship using Tor Browser,
+isolating specific browser features to study in the process. 
+To this end, we will conduct a large-scale user study examining hundreds of users 
+on how they navigate Tor's configuration wizard to complete seven browsing tasks 
+in three different adversarial settings.
+
+\subsection{Overview}
+For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both.
+There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use.
+The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.
+
+We start off the experiment by telling them that they are in an adversarial setting, and that some websites are blocked and some websites are not.
+We will instruct them to visit notblocked.com and also blocked.com to illustrate the situation that they are in.
+We will also explain what Tor is, and how they can use it if necessary, and ask them to complete the set of tasks.
+To complete all the tasks, the participants will ultimately need to get the correct configuration settings for the country they are simulated to be in.
+We will end the experiment with a survey which asks them things like their security background, tech exposure, what was unexpected, what was hard, etc.
+We plan to analyze: which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.
+
+\subsection{Censorship Environment Simulation}
+For our experiment, we plan to simulate and test three distinct censorship environments
+which vary in their methods of censorship and thusly require distinct responses from our 
+participants to circumvent successfully. These environments are designed with respect to 
+common censorship techniques employed 
+today along with knowledge of how pluggable transports will need to be used.
+For instance, some of Tor's pluggable transports work in censorship environments
+where others do not. Additionally, some of them require additional information (like bridge 
+addresses) before they enable the user to successfully circumvent censorship. 
+Details of the three censorship environments are below, increasing in 
+order of censorship comprehensiveness and, therefore, difficulty to circumvent.
+
+These environments are not meant perfectly to replicate the network environment
+in any particular country.  Censorship environments in are complex and volatile, making
+the task of replicating a network environment infeasible. More importantly, replicating these
+environments is not critical to this experiment. What is required for this experiment are 
+environments which would require users to complete similar Tor configuration 
+tasks before they are able to circumvent the censorship environment. We set up the following 
+abstract simulations which are inspired by reality and require users to complete various tasks
+to circumvent censorship.
+
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item{Corporate network.}
+A simulation of an enterprise or educational firewall.
+Blocks all services but HTTP, HTTPS, and DNS.
+Certain non-work-related domains, like youtube.com and torproject.org,
+are blocked by DNS and HTTP inspection.
+Blocked requests are redirected to a block page.
+\item{DNS-only censor.}
+This censor injects false replies to DNS queries
+for forbidden domain names (DNS poisoning),
+but does not do deep packet inspection on TCP streams.
+Unlike the corporate censor, this censor allows protocols
+outside a small whitelisted set.
+\item{Comprehensive censor.}
+Employs a variety of techniques, depending on the target.
+May do DNS poisoning, IP blocking, and inspection of TCP streams
+(examining the URL of HTTP requests, for example).
+Some domains may be blocked by DNS and deep packet inspection;
+others may additionally be blocked by IP address.
+Tor relays are blocked by IP address.
+Some domains, like wikipedia.org, may allow HTTP but not HTTPS.
+Blocked requests fail silently (no block page).
+\end{itemize}
+
+Is there a way to target testing of specific transports?
+Is there anything to infer from participants' selection of transports, 
+or do we assume they are trying transports at random?
+
+\subsection{Web Browsing Tasks}
+The tasks below are designed to be easy and quick to complete for an average
+computer user. This design is critical since the objective of the experiment is to observe
+how comfortable users are with circumventing censorship, which we indirectly measure
+by taking data regarding how participants complete the task. Giving participants tasks 
+they are not comfortable with performing or sending them to websites which they are 
+unfamiliar with will introduce more variables into the experiment to account for. 
+Specifically, we would need to separate any confusion caused by the task itself versus
+the task of circumventing censorship.
+
+To create a set of tasks that an average user will be able to complete reliably, 
+we turned to the top Alexa sites, the most popular websites on the Internet. This 
+is an indication of representative and relevant browsing behavior. To reach the final
+set of website destinations, we selected sites which were popular, but also commonly
+censored around the world to make our study more representative. The tasks 
+associated with each website were crafted with user familiarity in mind but narrowed 
+down the possibilities by removing tasks which caused ethical concerns (such as 
+requiring a user to log in to a websites, which would reveal login information).  
+We believe that these tasks we will use for our study will be simple tasks for an average 
+user to complete, on familiar websites.
+
+All participants will be given the same set of tasks, regardless of their simulated
+censorship environment.  Although every participant will attempt to complete the same 
+set of tasks, the difficulty of completing these tasks will vary based on their chosen environment. 
+Depending on the censorship environment, some tasks may not even require the use or Tor Browser.
+
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item Do a Google web search.
+\item Watch a YouTube video.
+\item Find the Amazon best-selling books.
+\item Find Yahoo's exchange rate between dollars and euros.
+\item Read the Wikipedia featured article.
+\item Find the Twitter trending topics.
+\item Find directions on Bing Maps.
+\end{itemize}
+
+We plan to present our work at HotPETS2015 and solicit feedback on the design
+of this experiment. Circumvention is broader than the stereotypical ``dissident blogger'' 
+use case. We will solicit feedback on which additional tasks will provide additional insight,
+or if there are different tasks which are representative of other censorship evasion use cases.
 
 \subsection{Methodology}  
-Talk about the justification of the setup and the general 
-work flow of an experiment session. Address any details up front
-about computers, money, people, etc.
+We plan to recruit up to 200 users for the purpose of this study, 
+making it largest user study to date examining Tor (check this). 
+This study will be conducted at the Experimental Social Science Laboratory (Xlab)
+at the University of California, Berkeley, which consists of 36 laptops with 
+cubicle walls separating each laptop. We will use individual host firewalls to simulate
+the censorship environments and will write a browser extension to 
+log when user activity, such as what websites they were successfully able to visit. 
+The total length of the experiment, including briefing, completing the censorship 
+circumvention tasks, exit survey, and debriefing, will take less than an hour. 
+Participants will be compensated \$30 for their time, 
+which is more to cover minimum wage and transportation costs
 
-\subsection{Censorship Environments} 
-Basically a section like the HOTPETS paper section.
-I should add details of exact configurations if available.
+\subsection{Data}
 
-\subsection{Tasks}
-A section like the HOTPETS paper section. 
-I  should add details of exact tasks if available.
+\subsubsection{Measurements}
+Screen capture, timing, completion, clicks, etc. Things to measure
+about the activity.
 
-\subsection{Feedback} 
+\subsubsection{Feedback} 
 Talk about the exit survey and what that covers. 
@@
 I guess that other literature on general usability applies here too. %so search for it. 
+Especially look into browser configuration work. %do it to it.
 
@@
 
+\appendix
+
+\section{UX sprint} 
+Details. Gory gory details of how it all went down. 
+Include the recruitment process, the setup, what the exact 
+tasks were for participants, demographics, everything. 
+It all should have a home here.
+
+\subsection{Motivation}
+Talk about why we did what we did, and what the end goal 
+of the experiment was. Also talk about how we expected users
+to be much better at installing and downloading than they were.
+
+\subsection{Experiment Overview}
+Talk about how the experiment was for an average user. We start
+with the cognitive walkthrough, then have them do one on a dummy
+and calibration task, we give feedback on the walkthrough, and then 
+give them the freedom to complete the web tasks.
+
+GET THE LIST OF TASKS WE MADE THEM DO.
+
+\subsection{Methodology}
+How we recruited, what the setup was like, how we got the tasks, details of 
+how the experiment was run, and things like that.
+
+\subsection{Results}
+Present situations which really were unexpected. 
+Also extract the golden quotes and state them here 
+to prove points I want to make.
+
+\url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}
+
+\subsection{Impact}
+whoo talk about the cool stuff that happened next here. 
+This means talking about the tickets and changes made 
+to the Tor browser, the start of a user manual, and 
+increased Tor UX efforts as a whole.
+
+\subsection{Resources}
+
+Our online artifacts of our completed pilot study, such as 
+the summary, results, and resulting browser changes are below:
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item \url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}
+\item \url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}
+\end{itemize}
+
+\noindent Subtitled screen videos:
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item \url{https://people.torproject.org/~dcf/uxsprint2015/}
+\end{itemize}
+
 \bibliographystyle{abbrv}

### 2015-05-11 cs261n-paper/paper.tex
more writing

@@
 \begin{abstract}
-It is easy to drastically overestimate user comprehension 
+\indent \indent It is easy to drastically overestimate user comprehension 
 and therefore be misguided for user behavior. 
@@
 \section{Introduction} %this should CLEARLY state the results. 
-Talk about the results and contributions concretely.
+\indent \indent Talk about the results and contributions concretely.
 As short as possible summary of UX sprint here. %only what is necessary to understand results. 
@@
 \subsection{Tor} 
-Talk about anything relevant to Tor. Just enough background so
+\indent \indent Talk about anything relevant to Tor. Just enough background so
 that people who have never heard of it will know what I am talking
@@
 \subsection{User behavior}
-Then also talk about any of the behaviors we are trying to mitigate,
+\indent \indent Then also talk about any of the behaviors we are trying to mitigate,
 or talk about the average user and what they know, how they are motivated,
@@
 \subsection{Usable security impact} 
-cite work which has made a huge impact on how people use it, and 
+\indent \indent cite work which has made a huge impact on how people use it, and 
 other things which still remain broken because of usability issues.
@@
 \subsection{Censorship} 
-Motivational paragraph time about how this is so everywhere.
+\indent \indent Motivational paragraph time about how this is so everywhere.
 
@@
 \section{UX sprint} 
-Talk about it just enough that it makes a good storyline for the experiment that we 
+\indent \indent Talk about it just enough that it makes a good storyline for the experiment that we 
 are proposing a design of. Motivate it a little bit, and tell a story. Then refer to the 
@@
 \subsection{Impact}
-whoo talk about the cool stuff that happened next here. 
+\indent \indent whoo talk about the cool stuff that happened next here. 
 This means talking about the tickets and changes made 
@@
 \subsection{Takeaways} 
-highlight what we learned and use this to transition into 
+\indent \indent highlight what we learned and use this to transition into 
 the design of the next experiment.
@@
 \subsection{Overview}
-For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both.
+\indent \indent For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both.
 There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use.
@@
 \subsection{Censorship Environment Simulation}
-For our experiment, we plan to simulate and test three distinct censorship environments
+\indent \indent For our experiment, we plan to simulate and test three distinct censorship environments
 which vary in their methods of censorship and thusly require distinct responses from our 
@@
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item{Corporate network.}
+\item{\bfseries Corporate network.}
 A simulation of an enterprise or educational firewall.
@@
 Blocked requests are redirected to a block page.
-\item{DNS-only censor.}
+%what do users need to do to circumvent this? 
+\item{\bfseries DNS-only censor.}
 This censor injects false replies to DNS queries
@@
 outside a small whitelisted set.
-\item{Comprehensive censor.}
+%what do users need to do to circumvent this? 
+\item{\bfseries Comprehensive censor.}
 Employs a variety of techniques, depending on the target.
@@
 Blocked requests fail silently (no block page).
+%what do users need to do to circumvent this? 
 \end{itemize}
 
-Is there a way to target testing of specific transports?
-Is there anything to infer from participants' selection of transports, 
+We plant to present our work at HotPETS2015 and solicit feedback on the design 
+of this experiment. Specifically, we would want a reliable way to target the testing of 
+specific transports. But given that the average user would not have domain knowledge of 
+what transports are for Tor, is there anything to infer from participants' selection of transports, 
 or do we assume they are trying transports at random?
@@
 \subsection{Web Browsing Tasks}
-The tasks below are designed to be easy and quick to complete for an average
+\indent \indent The tasks below are designed to be easy and quick to complete for an average
 computer user. This design is critical since the objective of the experiment is to observe
@@
 
-\subsection{Methodology}  
-We plan to recruit up to 200 users for the purpose of this study, 
-making it largest user study to date examining Tor (check this). 
+\section{Methodology}
+
+\indent \indent Talk about the two-pronged qualitative and empirical data measurement stuff here.
+
+\subsection{Qualitative Data} 
+Write about the exit survey here. Write down number of questions, surveygizmo, etc.
+
+\subsection{Empirical Data} 
+Screen capture, timing, completion, clicks, etc. Things to measure about the activity.
+
+\subsection{Experimental Setup}
+
+\indent \indent We plan to recruit up to 200 users for the purpose of this study, making this the largest user 
+study to date examining Tor. We do this in order to increase our chances at recruiting a diverse
+user population, ranging in age, gender, technical fluency, and other characteristics. Since Tor 
+does not keep information regarding its user base, we will try to obtain a user base representative of
+the average Internet using-population. Additionally, recruiting a large number of participants has the 
+benefit of ensuring enough samples in order to have significant effect sizes in 
+each simulated censorship environment.
+
 This study will be conducted at the Experimental Social Science Laboratory (Xlab)
-at the University of California, Berkeley, which consists of 36 laptops with 
-cubicle walls separating each laptop. We will use individual host firewalls to simulate
-the censorship environments and will write a browser extension to 
-log when user activity, such as what websites they were successfully able to visit. 
-The total length of the experiment, including briefing, completing the censorship 
-circumvention tasks, exit survey, and debriefing, will take less than an hour. 
-Participants will be compensated \$30 for their time, 
-which is more to cover minimum wage and transportation costs
+at the University of California, Berkeley. Recruitment will be conducted through Craigslist. 
+Although Xlab provides a portal in which researchers can recruit a pre-registered user base,
+we choose to not recruit through this portal, as their participants mostly consist of mostly Berkeley 
+students. The laboratory setting consists of 36 Toshiba Tecra R850 laptops with cubicle walls 
+separating each laptop. Since we do not have the ability to employ network-level firewalls in this
+laboratory setting, we will use individual host firewalls to simulate the censorship environments.  
+We will write and employ a browser extension will record user activity, such as how many times they 
+clicked, what websites they were successfully able to visit, and how long they took to complete 
+each task. This is because WHY? %ask david exactly why--technically. isn't the first hop in the clear?
 
-\subsection{Data}
-
-\subsubsection{Measurements}
-Screen capture, timing, completion, clicks, etc. Things to measure
-about the activity.
-
-\subsubsection{Feedback} 
-Talk about the exit survey and what that covers. 
-Explain why we want to know what we are asking about. 
-And why this matters.
+The total length of the experiment, including briefing, completing the censorship circumvention tasks, 
+exit survey, and debriefing, will take less than an hour. Participants will be compensated \$30 in the form
+of a check or Visa debit card for their time, which is enough to cover minimum wage during their participation 
+and their transportation costs to and from the laboratory.
 
 \section{Discussion}
-Discuss the hypotheses we have here for the experiment.
 
-And any work that needs to be done for the experiment.
+\subsection{Limitations}
+\indent \indent One limitation of our experiment is that participants' behaviors in a laboratory setting may
+be different to participants' behaviors in the wild. Studies have shown that participants will act in a way which 
+will aim to please researchers, trying to simulate what they believe are the results that we desire. Our participants
+may be motivated to complete the task in order to succeed at the experiment. One possible effect is that a user
+may have more patience to try to succeed at configuring the Tor Browser correctly during the experiment 
+compared to if they were attempting the same task at home.
+
+Another limitation of our experiment is that our participants might not have true interest or motivation in
+circumventing censorship. We could instead choose to recruit only users who have actively circumvented
+censorship or have an interest in Tor, but that study would also come with its own biases and limitations.
+We believed that both are worthwhile endeavors; however, we chose to aim for the general population. 
+This is because we would eventually want Tor's configuration dialog to be usable for a wide array of users, 
+including non-power users, and other types users who might not yet use Tor.
+
+\section{Future Work}
+And any work that needs to be done for the experiment. Give a brief timeline.
 

### 2015-05-11 cs261n-paper/paper.tex
wrapped up design section

@@
 \usepackage[hyphens]{url}
-\usepackage{longtable}
 \usepackage{graphicx}
@@
 \indent \indent Talk about it just enough that it makes a good storyline for the experiment that we 
-are proposing a design of. Motivate it a little bit, and tell a story. Then refer to the 
-Appendix for additional information.
+are proposing a design of. Motivate it a little bit, and tell a story.
+
+Appendix ~\ref{sec:pilot}.
 
@@
 
-\subsection{WHAT IS THIS}
-
-\noindent {\bfseries Motivation and Background Story} talk about the generalizability of the work, what we aim to find, and what future work this will lead to.
-Be sure to sketch the storyline of honing in on specific features.
+\subsection{Motivation}
+ talk about the generalizability of the work, what we aim to find, and what future work this will lead to. Be sure to sketch the storyline of honing in on specific features.
 
@@
 
-\subsection{Overview}
+\subsection{What is Required of Users}
 \indent \indent For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both.
@@
 The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.
-
-We start off the experiment by telling them that they are in an adversarial setting, and that some websites are blocked and some websites are not.
-We will instruct them to visit notblocked.com and also blocked.com to illustrate the situation that they are in.
-We will also explain what Tor is, and how they can use it if necessary, and ask them to complete the set of tasks.
-To complete all the tasks, the participants will ultimately need to get the correct configuration settings for the country they are simulated to be in.
-We will end the experiment with a survey which asks them things like their security background, tech exposure, what was unexpected, what was hard, etc.
-We plan to analyze: which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.
 
@@
 
-We plant to present our work at HotPETS2015 and solicit feedback on the design 
-of this experiment. Specifically, we would want a reliable way to target the testing of 
+We plant to solicit feedback on the design of this experiment at HotPETS2015.
+Specifically, we would want a reliable way to target the testing of 
 specific transports. But given that the average user would not have domain knowledge of 
@@
 
-We plan to present our work at HotPETS2015 and solicit feedback on the design
-of this experiment. Circumvention is broader than the stereotypical ``dissident blogger'' 
+We plant to solicit feedback on the design of this experiment at HotPETS2015. 
+Circumvention is broader than the stereotypical ``dissident blogger'' 
 use case. We will solicit feedback on which additional tasks will provide additional insight,
@@
 
-\indent \indent Talk about the two-pronged qualitative and empirical data measurement stuff here.
+\indent \indent Our experiment consists of three parts: informing and motivating the participants in order 
+to roleplay in the experiment, asking our participants to complete a set of web browsing tasks which will 
+require them to circumvent censorship using the Tor Browser, and soliciting feedback from our participants
+about their experience. With participants' consent, we will also record their computer screen to monitor 
+their activity and employ a browser extension to take empirical measurements (such as idle waiting time, 
+how fast a particular task was completed, etc.) throughout the duration of this experiment.
 
-\subsection{Qualitative Data} 
-Write about the exit survey here. Write down number of questions, surveygizmo, etc.
+Each session of 30 participants will be placed in the same simulated censorship environment. 
+We start off the experiment by informing our participants that they are in an adversarial setting, 
+where some websites are blocked while other websites are not. We will instruct them to visit a censored
+website and a non-censored website to illustrate that their devices and the network is fully functional and
+operating as expected, but that they are in a censorship environment where some websites will fail to load. 
+We will take a moment to explain what Tor is, how it is generally used in this case, and ask them to complete 
+the aforementioned set of tasks. To complete all the tasks, the participants will ultimately need to get the correct
+configuration settings for the country they are simulated to be in.
+
+Then, each participant will be given about 30 minutes to complete their given Internet browsing tasks. 
+Note that these Internet tasks themselves do not take very much time, but that the time is alloted in order
+for participants to complete the configuration process. We believe that this is more than enough time to 
+test the usability of the configuration process. Even if some participants may have succeeded with more 
+time, we consider these cases to be a failure from a usability perspective as this would require too much
+time from a user in the wild. Minimal interaction will be allowed with participants and the researchers. 
+Researchers may inform participants of specific information (such as a bridge address) in a manner 
+which does not disturb other participants (such as instructing users to visit a specific non-blocked website 
+containing this information).
+
+We will end the experiment with a survey of 17 questions in order to collect basic participation information, 
+demographics of our participants, open-ended responses of their experience with censorship circumvention,
+and general security questions to gauge their awareness in this area. Along with the empirical measurements 
+we have taken during the experiment, we will use this survey information to determine which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.
+
+\subsection{Quantitative and Qualitative Data}   
+\indent \indent We will collect quantitative and qualitative data from our participants after they have completed 
+their Internet tasks. This will allow us to align user activity with which simulated censorship setting, 
+correlate performance with any demographics, get an idea of participants' motivations.
+
+The survey consists of 17 questions total, with a basic breakdown as follows. 
+The complete list of survey questions can be found in Appendix ~\ref{sec:survey}.
+
+%question breakdown
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item 2 session and participant information questions
+\item 4 basic demographics questions
+\item 5 questions regarding their experience
+\item 2 technical calibration questions
+\item 4 Internet attitude questions
+\end{itemize}
+
+We also take this time to and collect feedback on the experience as a whole and the usability of 
+the Tor Browser. Out of the five questions, there are two multiple choice questions and three 
+open-ended feedback questions in which our participants can write us any length of response. 
+We opted for both concrete quantitative measurements of their experience along with free-text
+qualitative data to gather a broad range of information from our 200 participants in a scalable manner.
 
 \subsection{Empirical Data} 
-Screen capture, timing, completion, clicks, etc. Things to measure about the activity.
+Although quantitative and qualitative data provides valuable feedback into what users perceive of 
+their censorship circumvention experience, it will be imperative that we check for the validity of their 
+statements by analyzing empirical data collected by our browser extension during the process of the
+experiment. Specifically, we will capture:
+
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item A participant's computer screen. 
+\item Configuration dialog navigation. 
+\item Keyboard and mouse activity.
+\item Successfully visited websites. 
+\item Unsuccessfully visited websites. 
+\item Time to complete various tasks.
+\end{itemize}
+
+We hope that exploring correlations between a statement such as  ``I was frustrated it took so long'' 
+with task completion time, how many times a user had to repeat a dialog, or other behaviors 
+will be an illuminating process. These correlations may hint at what makes this configuration dialog 
+usable or not usable for users.
+
+Additionally, users are not always reliable not complete sources of feedback. We will use the 
+empirical data to verify the validity of their statements (for instance, if a user was reportedly frustrated 
+but completed the task in under a minute, we may enforce our own threshold for usability) as well as 
+performing additional analyses independent from the collected qualitative data (such as separating time
+idle from time spent typing during the completion of a task).
 
@@
 \section{Future Work}
-And any work that needs to be done for the experiment. Give a brief timeline.
+\indent \indent With the high-level design of the experiment complete and IRB approval  to conduct this
+experiment,  the next steps are to implement the simulated censorship environments which participants 
+will be placed in and to write the browser extension which will collect the empirical data. 
+We wait on these tasks in order to incorporate the feedback on the design of this experiment 
+we will receive at HotPETS2015, which will take place during July. We plan to conduct this study starting 
+August 2015.
 
-Next stps to take after the experiment, can also be here. %is this too far away?
+The goal of this experiment is to measure how usable Tor Browser is as a censorship circumvention
+tool. We hope that this experiment will provide insight into what usability improvements can be made 
+in order to better to make Tor Browser's advanced features more accessible to the average user. The results
+of this experiment can be used to inform user interaction designs which will result in shorter configuration
+completion time and more reliable communication of the technical task to be completed, all while the 
+this experience does not frustrate users from future use. We believe that experiments which perform
+iterative A/B testing on various designs in order to increase usability to a wide, anonymous, international 
+use base will be an interesting area of user interface design research while also making impacting changes
+to a widely used censorship circumvention technology.
 
@@
 \section{UX sprint} 
+\label{sec:pilot}
 Details. Gory gory details of how it all went down. 
@@
 
+\section{Exit Survey Questions}
+\label{sec:survey} 
+\indent \indent Our participants will be taking the following survey, hosted online at 
+\url{http://www.surveygizmo.com/s3/2085559/Tor-Usability-Survey/SG_TEST_RUN}.\\
+
+\noindent Recall that the survey consists of the following 17 questions, in this order: 
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item 2 session and participant information questions
+\item 4 basic demographics questions
+\item 6 questions regarding their experience with Tor
+\item 2 technical calibration questions
+\item 4 Internet attitude questions
+\end{itemize}
+
+\noindent Specifically, the questions are as follows: 
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+\item foo
+\item bar
+\item baz
+\item foo
+\item bar
+\item baz
+\item foo
+\item bar
+\item baz
+\item foo
+\item bar
+\item baz
+\item foo
+\item bar
+\item baz
+\item foo
+\item bar
+\end{enumerate}
+
 \bibliographystyle{abbrv}

### 2015-05-11 cs261n-paper/paper.tex
shuffled around sections

@@
 \begin{abstract}
-\indent \indent It is easy to drastically overestimate user comprehension 
-and therefore be misguided for user behavior. 
-Even though people download and install things all the time, 
-they do not know how to do it securely, and worse, 
-they are habituated into doing it a certain way. 
-What users had trouble with were the most basic tasks, 
-such as downloading and installing Tor, rather than 
-nagivating a robust menu or understanding subtleties of security guarentees. 
-This is really troubling, and matters for things like Tor. 
-We use this insight to fix a bunch of stuff and also 
-present a new experiment with a basic enough focus, 
-making us the first to focus on censorship too. 
+\indent \indent Tor has grown beyond its original purpose and has  since become an important 
+Internet circumvention tool. We specifically examine it usability as a censorship circumvention tool, 
+an essential facet for adoption and use.  We focus our analysis on the connection configuration dialog of 
+Tor browser, as censorship circumvention requires correct transport configurations. 
+This study is aimed at evaluating if and how easily users can circumvent censorship using Tor Browser,
+isolating specific browser features to study in the process.  To this end, we present the design of
+ a large-scale user study examining hundreds of users  on how they navigate Tor's configuration wizard to complete seven browsing tasks in three different adversarial settings.
+The experiment is scheduled for August 2015.
 \end{abstract}
 
-\section{Introduction} %this should CLEARLY state the results. 
+\section{Introduction} %%% 
 \indent \indent Talk about the results and contributions concretely.
@@
 
-\section{Background}  %ramp people up!
+what we want to contribute to the research community.
 
-\subsection{Tor} 
+\subsection{Tor} %%% 
 \indent \indent Talk about anything relevant to Tor. Just enough background so
@@
 
-\subsection{User behavior}
-\indent \indent Then also talk about any of the behaviors we are trying to mitigate,
-or talk about the average user and what they know, how they are motivated,
-just sketching out the environment in general.
-
-\subsection{Usable security impact} 
-\indent \indent cite work which has made a huge impact on how people use it, and 
-other things which still remain broken because of usability issues.
-
 We don't want Tor to be like this, and want people to use it!
 
-\subsection{Censorship} 
+\subsection{Censorship} %%%
 \indent \indent Motivational paragraph time about how this is so everywhere.
+
+\subsection{What is Required of Users} %%%
+\indent \indent For users to circumvent censorship in their resident countries, they will need to 
+configure Tor to set up a proxy, bridge, or both. The requirement of the user will vary on their censorship
+environment, specifically, if they need to conceal the fact that they are using Tor or if Tor entry nodes 
+have been blocked by the government.
+
+There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use.
+The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.
 
@@
 
-\section{UX sprint} 
+\section{UX sprint}  %%%%
 \indent \indent Talk about it just enough that it makes a good storyline for the experiment that we 
@@
 
+It is easy to overestimate user comprehension and therefore be 
+misguided for user behavior. Even though people download and install things all the time, 
+they do not know how to do it securely, and worse, they are habituated into doing it in the 
+insecure manner. Of course, this is because the average user's objective is not security. 
+For instance, most of our participants thought the download source was a legitimate site because
+of the look and feel of the site and none our our participants thought to verify the download, 
+even though there were clear instructions to do so on the download page.
+
+During this pilot, the users were struggling with confusing bugs, such as flash errors which
+say ``Firefox'' rather than ``Tor,'' disappearing buttons on the configuration window, and errors when
+launching Tor from the download dialog rather than from their applications folder. This resulted in our 
+participants spending most of their time on the download and install tasks, rather than 
+navigating a robust menu or questioning the clarity of provided security guarantees.
+
 \subsection{Impact}
-\indent \indent whoo talk about the cool stuff that happened next here. 
-This means talking about the tickets and changes made 
-to the Tor browser, the start of a user manual, and 
-increased Tor UX efforts as a whole.
+\indent \indent Along with the Tor developers who came to observe the UX pilot, we filed 
+a total of sixteen bug tickets to Tor. At the time of  this writing, eight of the sixteen tickets 
+have already been resolved, and more will be resolved in the future.  The list of bug
+tickets filed can be found at \url{https://trac.torproject.org/projects/tor/query?keywords=~uxsprint2015}.
+
+As of April, the changes resulting from our pilot study has been incorporated into the latest 
+version of Tor Browser, making Tor more usable for people to use. 
+The summary of the usability changes can be found at \url{https://blog.torproject.org/blog/tor-browser-45a4-released}.
+
+Through the publicity of this usability pilot study on the Tor weekly blogs, we were connected
+with a source from the Library Freedom Project, which provides training on various technologies 
+to libraries across the country. We now collaborate with her work on creating a user manual
+for the Tor Browser.
 
 \subsection{Takeaways} 
-\indent \indent highlight what we learned and use this to transition into 
-the design of the next experiment.
+\indent \indent During the pilot study, we were attempting to test out a comprehensive set of 
+features for the Tor Browser. Our users had difficulties completing all the given tasks in the 
+time alloted for the experiment. Additionally, user fatigue was very evident, with users not 
+engaging in the later set of tasks after being tired from the download and install process. 
+To ensure that the experiment does not cause user fatigue, we select a smaller set of features 
+as the target for the full-scale study.  After deliberating with Tor developers, and testing out
+various features on our own, we chose to focus on the Tor Browser connection configuration 
+dialog because of its crucial role in censorship circumvention.
 
-Wanted reproducibility of experiment.
-Wanted more people for a representative population. 
-Also make practical considerations such as avoiding transcription.
+Although the data from the pilot study provided a lot of insight into what users thought processes
+are when completing various asks, transcribing audio recordings and syncing them to videos was
+required a lot of manual labor. Not only did this form of data collection and processing not scale 
+to larger numbers, we found that most users encountered similar thought processes and struggled
+with the same issues. Because of this, we aim to collect our future qualitative data in the form of 
+an open-ended survey question rather than using audio recordings.
+
+While our pilot was insightful, the experiment itself is not very reproducible, as it requires
+a specific target audience (journalists who have recently reported in other countries) along 
+with specific guidance and feedback on how to perform a cognitive walkthrough. This makes it hard
+for the research community to prove or build on any findings. Therefore, we take precautions
+to ensure that our full-scale study will be reproducible.
 
@@
 
-\subsection{Motivation}
- talk about the generalizability of the work, what we aim to find, and what future work this will lead to. Be sure to sketch the storyline of honing in on specific features.
+\subsection{Overview} %%%
+Our experiment consists of three parts: informing and motivating the participants in order 
+to roleplay in the experiment, asking our participants to complete a set of web browsing tasks which will 
+require them to circumvent censorship using the Tor Browser, and soliciting feedback from our participants
+about their experience. With participants' consent, we will also record their computer screen to monitor 
+their activity and employ a browser extension to take empirical measurements (such as idle waiting time, 
+how fast a particular task was completed, etc.) throughout the duration of this experiment.
 
-Tor has grown beyond its original purpose as and has 
-since become an important Internet circumvention tool.
-We specifically examine it usability as a censorship circumvention tool,
-an essential facet for adoption and use.  
-We focus our analysis on the connection configuration dialog of Tor browser,
-as censorship circumvention requires correct transport configurations. %%
-This study is aimed at evaluating 
-if and how easily users can circumvent censorship using Tor Browser,
-isolating specific browser features to study in the process. 
-To this end, we will conduct a large-scale user study examining hundreds of users 
-on how they navigate Tor's configuration wizard to complete seven browsing tasks 
-in three different adversarial settings.
+Each session of 30 participants will be placed in the same simulated censorship environment. 
+We start off the experiment by informing our participants that they are in an adversarial setting, 
+where some websites are blocked while other websites are not. We will instruct them to visit a censored
+website and a non-censored website to illustrate that their devices and the network is fully functional and
+operating as expected, but that they are in a censorship environment where some websites will fail to load. 
+We will take a moment to explain what Tor is, how it is generally used in this case, and ask them to complete 
+the aforementioned set of tasks. To complete all the tasks, the participants will ultimately need to get the correct
+configuration settings for the country they are simulated to be in.
 
-\subsection{What is Required of Users}
-\indent \indent For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both.
-There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use.
-The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.
+Then, each participant will be given about 30 minutes to complete their given Internet browsing tasks. 
+Note that these Internet tasks themselves do not take very much time, but that the time is alloted in order
+for participants to complete the configuration process. We believe that this is more than enough time to 
+test the usability of the configuration process. Even if some participants may have succeeded with more 
+time, we consider these cases to be a failure from a usability perspective as this would require too much
+time from a user in the wild. Minimal interaction will be allowed with participants and the researchers. 
+Researchers may inform participants of specific information (such as a bridge address) in a manner 
+which does not disturb other participants (such as instructing users to visit a specific non-blocked website 
+containing this information).
+
+We will end the experiment with a survey of 17 questions in order to collect basic participation information, 
+demographics of our participants, open-ended responses of their experience with censorship circumvention,
+and general security questions to gauge their awareness in this area. Along with the empirical measurements 
+we have taken during the experiment, we will use this survey information to determine which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.
 
@@
 
-\indent \indent Our experiment consists of three parts: informing and motivating the participants in order 
-to roleplay in the experiment, asking our participants to complete a set of web browsing tasks which will 
-require them to circumvent censorship using the Tor Browser, and soliciting feedback from our participants
-about their experience. With participants' consent, we will also record their computer screen to monitor 
-their activity and employ a browser extension to take empirical measurements (such as idle waiting time, 
-how fast a particular task was completed, etc.) throughout the duration of this experiment.
+\subsection{Recruitment}  
+\indent \indent We plan to recruit up to 200 users for the purpose of this study, making this the largest user 
+study to date examining Tor. We do this in order to increase our chances at recruiting a diverse
+user population, ranging in age, gender, technical fluency, and other characteristics. Since Tor 
+does not keep information regarding its user base, we will try to obtain a user base representative of
+the average Internet using-population. Additionally, recruiting a large number of participants has the 
+benefit of ensuring enough samples in order to have significant effect sizes in 
+each simulated censorship environment.
 
-Each session of 30 participants will be placed in the same simulated censorship environment. 
-We start off the experiment by informing our participants that they are in an adversarial setting, 
-where some websites are blocked while other websites are not. We will instruct them to visit a censored
-website and a non-censored website to illustrate that their devices and the network is fully functional and
-operating as expected, but that they are in a censorship environment where some websites will fail to load. 
-We will take a moment to explain what Tor is, how it is generally used in this case, and ask them to complete 
-the aforementioned set of tasks. To complete all the tasks, the participants will ultimately need to get the correct
-configuration settings for the country they are simulated to be in.
-
-Then, each participant will be given about 30 minutes to complete their given Internet browsing tasks. 
-Note that these Internet tasks themselves do not take very much time, but that the time is alloted in order
-for participants to complete the configuration process. We believe that this is more than enough time to 
-test the usability of the configuration process. Even if some participants may have succeeded with more 
-time, we consider these cases to be a failure from a usability perspective as this would require too much
-time from a user in the wild. Minimal interaction will be allowed with participants and the researchers. 
-Researchers may inform participants of specific information (such as a bridge address) in a manner 
-which does not disturb other participants (such as instructing users to visit a specific non-blocked website 
-containing this information).
-
-We will end the experiment with a survey of 17 questions in order to collect basic participation information, 
-demographics of our participants, open-ended responses of their experience with censorship circumvention,
-and general security questions to gauge their awareness in this area. Along with the empirical measurements 
-we have taken during the experiment, we will use this survey information to determine which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.
+ %% what we will recruit for, how we inform, and interactions.
 
@@
 
-\indent \indent We plan to recruit up to 200 users for the purpose of this study, making this the largest user 
-study to date examining Tor. We do this in order to increase our chances at recruiting a diverse
-user population, ranging in age, gender, technical fluency, and other characteristics. Since Tor 
-does not keep information regarding its user base, we will try to obtain a user base representative of
-the average Internet using-population. Additionally, recruiting a large number of participants has the 
-benefit of ensuring enough samples in order to have significant effect sizes in 
-each simulated censorship environment.
-
-This study will be conducted at the Experimental Social Science Laboratory (Xlab)
+\indent\indent This study will be conducted at the Experimental Social Science Laboratory (Xlab)
 at the University of California, Berkeley. Recruitment will be conducted through Craigslist. 
@@
 
-\section{Related Work} %this is distracting to have earlier. %don't overdo the citations. 
+\section{Related Work} %%%
+%%%Tor
 The stopping points paper on Tor's usability ~\cite{norcie2012eliminating}. 
@@
 
-\section{Conclusion} 
-Do not repeat the abstract, introduction, or the results section. 
-Focus this time to discuss the limitations of the work and broader impacts.
+%%%User behavior
+\indent \indent Then also talk about any of the behaviors we are trying to mitigate,
+or talk about the average user and what they know, how they are motivated,
+just sketching out the environment in general.
 
-Reach out to the community to make a call for more a focus on usability for security products.
+%%% Other Usability stuff 
+\indent \indent cite work which has made a huge impact on how people use it, and 
+other things which still remain broken because of usability issues.
 

### 2015-05-11 cs261n-paper/paper.tex
Section on Tor.

@@
 
-\subsection{Tor} %%% 
-\indent \indent Talk about anything relevant to Tor. Just enough background so
-that people who have never heard of it will know what I am talking
-about, but no more than that.
+\subsection{Tor} 
+% \indent \indent Talk about anything relevant to Tor. Just enough background so
+% that people who have never heard of it will know what I am talking
+% about, but no more than that.
 
-We don't want Tor to be like this, and want people to use it!
+The Tor Project, known for its anonymity network~\cite{tor-design},
+has in recent years become an important player in the world of
+censorship circumvention.
+In its early days, people used Tor to evade censorship,
+and in response censors began to block Tor itself.
+In response, work began on various anti-censorship technologies
+now known as ``pluggable transports''~\cite{pluggable-transports}.
+Currently there are over 15,000 users accessing the Tor network
+at any given time using one of these
+anti-censorship technologies~\cite{userstats-bridge-country}.
+
+Tor Browser~\cite{tor-browser},
+a specially modified version of Firefox that comes
+with a built-in Tor proxy and pluggable transports,
+is the primary means through which users access the Tor network.
+It aims to make powerful anonymity and circumvention technology
+accessible even to nontechnical users.
+Its user interface was greatly overhauled in its version~3.5 release,
+and since then it has not had a comprehensive usability evaluation.
 

### 2015-05-11 cs261n-paper/paper.tex
11-point font.
Per http://www.icir.org/vern/cs261n/writing.html.
Typo.
started using colors

@@
 %\documentclass{article}
-\documentclass[letterpaper,twocolumn,10pt]{article}
+\documentclass[letterpaper,twocolumn,11pt]{article}
 \usepackage[margin=0.75in]{geometry}
@@
 
-what we want to contribute to the research community.
+{\color {red} what we want to contribute to the research community.}
 
@@
 
-We plant to solicit feedback on the design of this experiment at HotPETS2015.
+We plan to solicit feedback on the design of this experiment at HotPETS2015.
 Specifically, we would want a reliable way to target the testing of 
@@
 clicked, what websites they were successfully able to visit, and how long they took to complete 
-each task. This is because WHY? %ask david exactly why--technically. isn't the first hop in the clear?
+each task. {\color {red} This is because WHY?} %ask david exactly why--technically. isn't the first hop in the clear?
 
@@
 %%%Tor
-The stopping points paper on Tor's usability ~\cite{norcie2012eliminating}. 
-And that is pretty much it for Tor usability stuff. %find more if it exists
+ {\color {red} The stopping points paper on Tor's usability ~\cite{norcie2012eliminating}. 
+And that is pretty much it for Tor usability stuff.} %find more if it exists
 
-I guess that other literature on general usability applies here too. %so search for it. 
-Especially look into browser configuration work. %do it to it.
+{\color {red}  I guess that other literature on general usability applies here too. %so search for it. 
+Especially look into browser configuration work. }
 
 %%%User behavior
-\indent \indent Then also talk about any of the behaviors we are trying to mitigate,
+\indent \indent {\color {red}  Then also talk about any of the behaviors we are trying to mitigate,
 or talk about the average user and what they know, how they are motivated,
-just sketching out the environment in general.
+just sketching out the environment in general.}
 
 %%% Other Usability stuff 
-\indent \indent cite work which has made a huge impact on how people use it, and 
-other things which still remain broken because of usability issues.
+\indent \indent {\color {red}  cite work which has made a huge impact on how people use it, and 
+other things which still remain broken because of usability issues.}
 
@@
 
-GET THE LIST OF TASKS WE MADE THEM DO.
+{\color {red}  GET THE LIST OF TASKS WE MADE THEM DO.}
 

### 2015-05-11 cs261n-paper/paper.tex
added in survey questions

@@
 
-Talk about the basic methods of censoring, and how it differs 
+{\color {red} Talk about the basic methods of censoring, and how it differs 
 around the world, which sites are targeted, etc.
 
-Scope the paper here. Talk about how we are not up Cuba-like adversaries.
+Scope the paper here. Talk about how we are not up Cuba-like adversaries. }
 
 \section{UX sprint}  %%%%
-\indent \indent Talk about it just enough that it makes a good storyline for the experiment that we 
+\indent \indent {\color {red} Talk about it just enough that it makes a good storyline for the experiment that we 
 are proposing a design of. Motivate it a little bit, and tell a story.
 
-Appendix ~\ref{sec:pilot}.
+Appendix ~\ref{sec:pilot}. }
 
@@
 
-\subsection{Overview} %%%
+\subsection{Overview} 
 Our experiment consists of three parts: informing and motivating the participants in order 
@@
 
- %% what we will recruit for, how we inform, and interactions.
+{\color {red} what we will recruit for, how we inform, and interactions.}
 
@@
 \item 4 basic demographics questions
-\item 5 questions regarding their experience
+\item 5 questions regarding their experience with Tor
+\item 4 Internet attitude questions
 \item 2 technical calibration questions
-\item 4 Internet attitude questions
 \end{itemize}
@@
 \item 4 basic demographics questions
-\item 6 questions regarding their experience with Tor
+\item 5 questions regarding their experience with Tor
+\item 4 Internet attitude questions
 \item 2 technical calibration questions
-\item 4 Internet attitude questions
 \end{itemize}
@@
 \begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-\item foo
-\item bar
-\item baz
-\item foo
-\item bar
-\item baz
-\item foo
-\item bar
-\item baz
-\item foo
-\item bar
-\item baz
-\item foo
-\item bar
-\item baz
-\item foo
-\item bar
+\item What session did you attend?  
+\item What is your participant ID? (This can be found on the sticker on the left hand corder of desk you are currently sitting at.) \\
+\item What is your gender? 
+\item What is your age? 
+\item Please select your highest level of education. 
+\item What is your current occupation? \\
+\item How familiar were you with Tor prior to this study? 
+\item Were you confident that Tor was able to provide you with security and anonymity while completing your tasks?
+\item Did anything unexpected happen while using Tor? 
+\item What, if any, of the following could use improvement? 
+\item Based on your experience, would you use Tor again? \\
+\item How many hours a week would you say you spend on the internet? 
+\item How concerned are you about your privacy on the Internet?
+\item How concerned are you about staying anonymous on the internet?
+\item How concerned are you about being censored while you browse the Internet? \\
+\item How familiar are you with computer security? 
+\item What kinds of computer security software do you use? 
 \end{enumerate}

### 2015-05-11 cs261n-paper/paper.tex
added a survey questions blurb.

@@
 \item What session did you attend?  
-\item What is your participant ID? (This can be found on the sticker on the left hand corder of desk you are currently sitting at.) \\
+\item What is your participant ID? (This can be found on the sticker on the left hand corder of desk you are currently sitting at.) 
 \item What is your gender? 
@@
 \item Please select your highest level of education. 
-\item What is your current occupation? \\
+\item What is your current occupation?*
 \item How familiar were you with Tor prior to this study? 
 \item Were you confident that Tor was able to provide you with security and anonymity while completing your tasks?
-\item Did anything unexpected happen while using Tor? 
-\item What, if any, of the following could use improvement? 
-\item Based on your experience, would you use Tor again? \\
+\item Did anything unexpected happen while using Tor?*
+\item What, if any, of the following could use improvement?*
+\item Based on your experience, would you use Tor again?*
 \item How many hours a week would you say you spend on the internet? 
@@
 \item How concerned are you about staying anonymous on the internet?
-\item How concerned are you about being censored while you browse the Internet? \\
+\item How concerned are you about being censored while you browse the Internet? 
 \item How familiar are you with computer security? 
@@
 
+Questions marked with asterisks are open-ended questions.
+All other questions are multiple choice, whether they be radio buttons, check boxes, or a drop down menu.
+For additional details regarding answer inputs, we refer you to our online survey linked above.
+
 \bibliographystyle{abbrv}

### 2015-05-11 cs261n-paper/paper.tex
finished reddening all unfinished sections and inline comments.

@@
 \label{sec:pilot}
-Details. Gory gory details of how it all went down. 
+ {\color {red}Details. Gory gory details of how it all went down. 
 Include the recruitment process, the setup, what the exact 
 tasks were for participants, demographics, everything. 
-It all should have a home here.
+It all should have a home here.}
 
 \subsection{Motivation}
-Talk about why we did what we did, and what the end goal 
+{\color {red} Talk about why we did what we did, and what the end goal 
 of the experiment was. Also talk about how we expected users
-to be much better at installing and downloading than they were.
+to be much better at installing and downloading than they were. }
 
 \subsection{Experiment Overview}
-Talk about how the experiment was for an average user. We start
+{\color {red} Talk about how the experiment was for an average user. We start
 with the cognitive walkthrough, then have them do one on a dummy
@@
 
-{\color {red}  GET THE LIST OF TASKS WE MADE THEM DO.}
+GET THE LIST OF TASKS WE MADE THEM DO.}
 
 \subsection{Methodology}
-How we recruited, what the setup was like, how we got the tasks, details of 
-how the experiment was run, and things like that.
+{\color {red} How we recruited, what the setup was like, how we got the tasks, details of 
+how the experiment was run, and things like that.}
 
 \subsection{Results}
-Present situations which really were unexpected. 
+{\color {red} Present situations which really were unexpected. 
 Also extract the golden quotes and state them here 
-to prove points I want to make.
+to prove points I want to make. }
 
 \url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}
-
-\subsection{Impact}
-whoo talk about the cool stuff that happened next here. 
-This means talking about the tickets and changes made 
-to the Tor browser, the start of a user manual, and 
-increased Tor UX efforts as a whole.
 

### 2015-05-11 cs261n-paper/paper.tex
Start of introduction.

@@
 \section{Introduction} %%% 
-\indent \indent Talk about the results and contributions concretely.
-As short as possible summary of UX sprint here. %only what is necessary to understand results. 
-Talk about the changes resulted in the Tor browser here.
-As short as possible summary of lessons learned, 
-and also a short as possible motivation for censorship work here. %yep, same.
-Talk about the experiment design quickly here.
+% \indent \indent Talk about the results and contributions concretely.
+% As short as possible summary of UX sprint here. %only what is necessary to understand results. 
+% Talk about the changes resulted in the Tor browser here.
+% As short as possible summary of lessons learned, 
+% and also a short as possible motivation for censorship work here. %yep, same.
+% Talk about the experiment design quickly here.
+
+We aim to improve user security by evaluating
+and improving the usability of security software.
+Both ``usability'' and ``security'' encompass many topics;
+therefore we limit our scope and focus on
+an important and timely use case:
+user configuration of software to evade Internet censorship.
+In this report, we detail the design of a usability-focused user experiment,
+which we hope will be a benchmark for such studies
+and guide their development in the future.
+
+We hold that usability must be regarded as a security property.
+It should be part of the design of security software.
+Usable software not only decreases the risk of making mistakes
+with dangerous security consequences,
+but also provides a bridge over which users can
+transition from substitutes that are less safe.
 

### 2015-05-11 cs261n-paper/paper.tex
Move up censorship subsection.
wrote some intro

--- 2015-05-11 cs261n-paper/paper.tex
@@
 
-\title{better title eventually}
+\title{{\color {red}better title eventually}}
 \author{Linda N. Lee, David Fifield\\
@@
 
-% is the abstract missing some oomph? 
-% I don't know how much the storyline is showing through.. or what we are testing. 
 \begin{abstract}
@@
 
-\subsection{What is Required of Users} %%%
+\subsection{What is Required of Users}
 \indent \indent For users to circumvent censorship in their resident countries, they will need to 
@@
 have been blocked by the government.
+There is a configuration wizard to help guide users through setting up their connection, but they require the user to provide IP addresses of proxies or bridges to use.
 
-There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use.
-The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.
+The end user generally does not care about the details of the 
+censorship environment, and how the censorship is implemented; rather, they care about how to get
+to the website of their choice. In the wild, users may choose to get the required information in a variety 
+of ways, including reading online manuals on how to configure Tor, finding out information through word of mouth, 
+or figuring out correct configurations themselves by trial and error.  We cannot accurately simulate the effects
+of these localized effects during our experiment.
 
-{\color {red} Talk about the basic methods of censoring, and how it differs 
-around the world, which sites are targeted, etc.
-
-Scope the paper here. Talk about how we are not up Cuba-like adversaries. }
+However, we are testing the usability, and therefore comprehension and user-friendliness, of the Tor configuration 
+dialog, which will require users in the most strict censorship environments to navigate through three configuration windows and provide correct answers all along the process in order to configure the connection correctly.
+Knowledge
+required includes if their connection would require a proxy to access the Internet, the IP address of a bridge if required, 
+and which pluggable transports are functional in their country.
 

### 2015-05-12 cs261n-paper/paper.tex

@@
 \section{Introduction} %%% 
-\indent \indent Talk about the results and contributions concretely.
-As short as possible summary of UX sprint here. %only what is necessary to understand results. 
-Talk about the changes resulted in the Tor browser here.
-As short as possible summary of lessons learned, 
-and also a short as possible motivation for censorship work here. %yep, same.
-Talk about the experiment design quickly here.
+% \indent \indent Talk about the results and contributions concretely.
+% As short as possible summary of UX sprint here. %only what is necessary to understand results. 
+% Talk about the changes resulted in the Tor browser here.
+% As short as possible summary of lessons learned, 
+% and also a short as possible motivation for censorship work here. %yep, same.
+% Talk about the experiment design quickly here.
+
+We aim to improve user security by evaluating
+and improving the usability of security software.
+Both ``usability'' and ``security'' encompass many topics;
+therefore we limit our scope and focus on
+an important and timely use case:
+user configuration of software to evade Internet censorship.
+In this report, we detail the design of a usability-focused user experiment,
+which we hope will be a benchmark for such studies
+and guide their development in the future.
+
+We hold that usability must be regarded as a security property.
+It should be part of the design of security software.
+Usable software not only decreases the risk of making mistakes
+with dangerous security consequences,
+but also provides a bridge over which users can
+transition from substitutes that are less safe.
+
+\subsection{Censorship} %%%
+% \indent \indent Motivational paragraph time about how this is so everywhere.
 
@@
 
-\subsection{Censorship} %%%
-\indent \indent Motivational paragraph time about how this is so everywhere.
-
-\subsection{What is Required of Users}
+\subsection{What is Required of Users} %%%
 \indent \indent For users to circumvent censorship in their resident countries, they will need to 

### 2015-05-12 cs261n-paper/paper.tex
little fixes

@@
 \section{Introduction} %%%
-% \indent \indent Talk about the results and contributions concretely.
-% As short as possible summary of UX sprint here. %only what is necessary to understand results. 
-% Talk about the changes resulted in the Tor browser here.
-% As short as possible summary of lessons learned, 
-% and also a short as possible motivation for censorship work here. %yep, same.
-% Talk about the experiment design quickly here.
 
-We aim to improve user security by evaluating
+\indent \indent We aim to improve user security by evaluating
 and improving the usability of security software.
@@
 \subsection{Tor}
-% \indent \indent Talk about anything relevant to Tor. Just enough background so
-% that people who have never heard of it will know what I am talking
-% about, but no more than that.
 
-The Tor Project, known for its anonymity network~\cite{tor-design},
+\indent \indent The Tor Project, known for its anonymity network~\cite{tor-design},
 has in recent years become an important player in the world of
@@
 
-{\color {red} what we will recruit for, how we inform, and interactions.}
-
 \subsection{Quantitative and Qualitative Data}   
@@
 clicked, what websites they were successfully able to visit, and how long they took to complete 
-each task. {\color {red} This is because WHY?} %ask david exactly why--technically. isn't the first hop in the clear?
+each task.
 

### 2015-05-12 cs261n-paper/paper.tex
More introduction.

@@
 
+The heart of our investigation will be a large-scale user study
+that measures how effectively users are able to complete
+basic web browsing tasks in the presence of a censor.
+We will place users in a controlled network environment
+that simulates the kind of censorship conditions that many
+users around the world face daily.
+We will be testing specific circumvention software---namely,
+Tor Browser---though our larger contribution is to establish
+a usability testing methodology for the evaluation
+of this kind of software.
+
 \subsection{Censorship} %%%
@@
 
-\section{UX sprint}  %%%%
-\indent \indent {\color {red} Talk about it just enough that it makes a good storyline for the experiment that we 
-are proposing a design of. Motivate it a little bit, and tell a story.
-
-Appendix ~\ref{sec:pilot}. }
-
-It is easy to overestimate user comprehension and therefore be 
-misguided for user behavior. Even though people download and install things all the time, 
-they do not know how to do it securely, and worse, they are habituated into doing it in the 
-insecure manner. Of course, this is because the average user's objective is not security. 
-For instance, most of our participants thought the download source was a legitimate site because
-of the look and feel of the site and none our our participants thought to verify the download, 
-even though there were clear instructions to do so on the download page.
+\section{A Pilot Tor Usability Study} 
+\indent \indent We ran a pilot Tor usability study to test the usability of Tor as an anonymity tool,
+targeting a specific demographic of users known to use Tor (journalists who have reported in other
+countries) and aiming to identify how well they could understand Tor's non-typical behaviors and 
+navigate advanced settings. For the full details of this pilot experiment, we refer you to Appendix ~\ref{sec:pilot}.
 
@@
 participants spending most of their time on the download and install tasks, rather than 
-navigating a robust menu or questioning the clarity of provided security guarantees.
+our original task for navigating a robust menu or questioning the clarity of provided security 
+guarantees. We took the opportunity to collaborate with Tor developers to make changes for the Tor 
+Browser and use the lessons learned to design our large-scale user study on testing Tor as a 
+censorship circumvention tool.
 
@@
 
-\subsection{Takeaways} 
+\subsection{Lessons Learned} 
 \indent \indent During the pilot study, we were attempting to test out a comprehensive set of 
@@
 \section{Related Work} %%%
-%%%Tor
- {\color {red} The stopping points paper on Tor's usability ~\cite{norcie2012eliminating}. 
-And that is pretty much it for Tor usability stuff.} %find more if it exists
 
-{\color {red}  I guess that other literature on general usability applies here too. %so search for it. 
-Especially look into browser configuration work. }
+\subsection{Usability work on Tor}
+\indent \indent  Work by Clark \etal to explore ways to simplify the Tor user interface
+has led to great usability improvements ~\cite{clark2007usability}.  Clark analyzed the challenges 
+of using multiple Tor-related tools including TorPark, Vidalia, FoxyProxy, and TorButton to find that
+none are fully satisfactory from a usability perspective. Researchers provide guidelines on 
+how to incorporate the best aspects of each tool, while providing a set of guidelines drawn from
+usable security and computer human interaction. Key takeaways from this work includes 
+finding out that exposure to how Tor works may be difficult for users to understand, and that 
+familiar, non-technical language is critical for communication. We plan to draw from Clark's
+guidelines as well as other works in usable security and computer human interaction to suggest
+any improvements to the Tor Browser.
 
-%%%User behavior
+This will be the first experiment to evaluate Tor's usability as a censorship circumvention tool.
+Previous work on evaluating the usability of Tor as an anonymity system have been fruitful. 
+Norcie \etal identified ``stop points,'' or barriers to installing and using Tor to help streamline
+the interface. Key stop points included the ability to discriminate between anonymized and non-
+anonymized browser windows while using tor, unclear download and install processes, and 
+confusion as to why the Tor behaves in peculiar ways ~\cite{norcie2012eliminating}. A follow up
+study by Norcie \etal verifies that the changes recommended to the Tor Project were indeed 
+effective at reducing stopping points mentioned in the previous work. The authors also present
+design heuristics for designing usable anonymous systems, such as easy installation, communicating
+tradeoffs made to users, and informing why, not how, precautions are taken for security guarantees ~\cite{norcie2014johnny}.
+
+\subsection{Usable Security and User Behavior}
 \indent \indent {\color {red}  Then also talk about any of the behaviors we are trying to mitigate,
@@
 
-%%% Other Usability stuff 
-\indent \indent {\color {red}  cite work which has made a huge impact on how people use it, and 
-other things which still remain broken because of usability issues.}
+{\color {red}  I guess that other literature on general usability applies here too. %so search for it. 
+Especially look into browser configuration work. }
 
@@
 It all should have a home here.}
+
+%It is easy to overestimate user comprehension and therefore be 
+%misguided for user behavior. During this process, we discovered why 
+%previous studies had not concentrated on a specific user 
+%demographic or focus on advanced features. 
+%Even though people download and install on a frequent basis, 
+%they do not know how to do it securely and are habituated into doing it in the 
+%insecure manner. Of course, this is because the average user's objective is not security. 
+%For instance, most of our participants thought the download source was a legitimate site because
+%of the look and feel of the site and none our our participants thought to verify the download, 
+%even though there were clear instructions to do so on the download page.
 
@@
 
-Our online artifacts of our completed pilot study, such as 
+\indent \indent  Our online artifacts of our completed pilot study, such as 
 the summary, results, and resulting browser changes are below:

### 2015-05-12 cs261n-paper/paper.tex
ux section written.

--- 2015-05-12 cs261n-paper/paper.tex
@@
 transition from substitutes that are less safe.
-
-The heart of our investigation will be a large-scale user study
-that measures how effectively users are able to complete
-basic web browsing tasks in the presence of a censor.
-We will place users in a controlled network environment
-that simulates the kind of censorship conditions that many
-users around the world face daily.
-We will be testing specific circumvention software---namely,
-Tor Browser---though our larger contribution is to establish
-a usability testing methodology for the evaluation
-of this kind of software.
 

### 2015-05-12 cs261n-paper/paper.tex
List of UX Sprint tasks.
I got it from tasks.html from
https://repo.eecs.berkeley.edu/git-anon/users/fifield/tor-ux.git.

--- 2015-05-12 cs261n-paper/paper.tex
@@
 and calibration task, we give feedback on the walkthrough, and then 
-give them the freedom to complete the web tasks.
+give them the freedom to complete the web tasks.}
 
-GET THE LIST OF TASKS WE MADE THEM DO.}
+After the calibration task, we asked participants to complete
+the following Tor Browser--related tasks:
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+\item Download Tor (the web browser)
+\item Install Tor
+\item Check that Tor is working
+\item Do a web search for ``onions''
+\item Find a YouTube video for ``Ode to Joy''
+\item Use ``New Identity'' under the onion menu
+\item Explain your best understanding of all the items in the toolbar
+\end{enumerate}
+We originally had another step after Step~1, ``Configure Tor.''
+We removed it after the first two participants
+when it became clear that the wording was confusing.
+The two main buttons in the configuration wizard are labeled
+``Connect'' and ``Configure''; we did not intend for users
+to have to go through the longer ``Configure'' path,
+but they assumed they had to because of the presence
+of the word ``Configure'' in the list of tasks.
 

### 2015-05-12 cs261n-paper/paper.tex
Subsection on censorship.

@@
 
-{\color {red} what we want to contribute to the research community.}
+\indent \indent Censorship and other information controls
+are widespread on the Internet and increasing in prevalence.
+Since 2011, Freedom House has published a yearly report
+on the state of Internet freedom in dozens of countries.
+The 2014 report~\cite{freedom-on-the-net-2014} observes
+an overall decrease in freedom worldwide,
+with 36 of 65 surveyed countries decreasing in their freedom rating
+since 2013 (only 12 countries had an increase).
+
+To escape restrictive networks and communicate more freely,
+users turn to a variety of censorship circumvention technologies.
+What tools are necessary depends greatly on the specifics of
+a particular censor;
+they range from simple one-hop proxies and VPNs
+to complicated steganographic systems.
+Our goal is the development of an experiment
+to test the usability of such tools.
+We focus on one particular system,
+Tor Browser, which bundles a variety of circumvention
+tools designed for different use cases.
 

### 2015-05-12 cs261n-paper/paper.tex
Abstract editing.

@@
 \begin{abstract}
-\indent \indent Tor has grown beyond its original purpose and has  since become an important 
-Internet circumvention tool. We specifically examine it usability as a censorship circumvention tool, 
-an essential facet for adoption and use.  We focus our analysis on the connection configuration dialog of 
-Tor browser, as censorship circumvention requires correct transport configurations. 
-This study is aimed at evaluating if and how easily users can circumvent censorship using Tor Browser,
-isolating specific browser features to study in the process.  To this end, we present the design of
- a large-scale user study examining hundreds of users  on how they navigate Tor's configuration wizard to complete seven browsing tasks in three different adversarial settings.
-The experiment is scheduled for August 2015.
+\indent \indent Tor has grown beyond its original purpose of anonymity
+to become an important tool for
+Internet censorship circumvention.
+We describe an experiment to assess the usability of Tor Browser,
+a web browser with a bundled Tor proxy,
+for the purpose of circumvention.
+We focus our analysis on the browser's connection configuration dialog,
+which enables circumvention even under stringent censors,
+when used correctly.
+The experiment is aimed at evaluating whether, and how easily users can circumvent censorship using Tor Browser,
+under several censorship environments.
+We present the design of the experiment,
+which will involve hundreds of users completing seven browsing tasks in three different adversarial settings.
+We describe the results of a smaller-scale pilot study,
+the lessons we learned from it,
+and how it guided our future experimental ambitions.
+The experiment we describe is scheduled to run in August 2015.
 \end{abstract}

### 2015-05-12 cs261n-paper/paper.tex
Spell check.

@@
 features for the Tor Browser. Our users had difficulties completing all the given tasks in the 
-time alloted for the experiment. Additionally, user fatigue was very evident, with users not 
+time allotted for the experiment. Additionally, user fatigue was very evident, with users not 
 engaging in the later set of tasks after being tired from the download and install process. 
@@
 Then, each participant will be given about 30 minutes to complete their given Internet browsing tasks. 
-Note that these Internet tasks themselves do not take very much time, but that the time is alloted in order
+Note that these Internet tasks themselves do not take very much time, but that the time is allotted in order
 for participants to complete the configuration process. We believe that this is more than enough time to 
@@
 \indent \indent For our experiment, we plan to simulate and test three distinct censorship environments
-which vary in their methods of censorship and thusly require distinct responses from our 
+which vary in their methods of censorship and thus require distinct responses from our 
 participants to circumvent successfully. These environments are designed with respect to 
@@
 
-We plan to solicit feedback on the design of this experiment at HotPETS2015.
+We plan to solicit feedback on the design of this experiment at HotPETs 2015.
 Specifically, we would want a reliable way to target the testing of 
@@
 
-We plant to solicit feedback on the design of this experiment at HotPETS2015. 
+We plant to solicit feedback on the design of this experiment at HotPETs 2015. 
 Circumvention is broader than the stereotypical ``dissident blogger'' 
@@
 We wait on these tasks in order to incorporate the feedback on the design of this experiment 
-we will receive at HotPETS2015, which will take place during July. We plan to conduct this study starting 
+we will receive at HotPETs 2015, which will take place during July. We plan to conduct this study starting 
 August 2015.
@@
 \item What session did you attend?  
-\item What is your participant ID? (This can be found on the sticker on the left hand corder of desk you are currently sitting at.) 
+\item What is your participant ID? (This can be found on the sticker on the left hand corner of desk you are currently sitting at.) 
 \item What is your gender? 

### 2015-05-12 cs261n-paper/paper.tex
ux sprint overview section

--- 2015-05-12 cs261n-paper/paper.tex
@@
 
-\section{Introduction} %%%
+\section{Introduction}
 
@@
 
-The heart of our investigation will be a large-scale user study
-that measures how effectively users are able to complete
-basic web browsing tasks in the presence of a censor.
-We will place users in a controlled network environment
-that simulates the kind of censorship conditions that many
-users around the world face daily.
-We will be testing specific circumvention software---namely,
-Tor Browser---though our larger contribution is to establish
-a usability testing methodology for the evaluation
-of this kind of software.
-
 \subsection{Censorship} %%%
@@
 
-\indent \indent Censorship and other information controls
-are widespread on the Internet and increasing in prevalence.
-Since 2011, Freedom House has published a yearly report
-on the state of Internet freedom in dozens of countries.
-The 2014 report~\cite{freedom-on-the-net-2014} observes
-an overall decrease in freedom worldwide,
-with 36 of 65 surveyed countries decreasing in their freedom rating
-since 2013 (only 12 countries had an increase).
-
-To escape restrictive networks and communicate more freely,
-users turn to a variety of censorship circumvention technologies.
-What tools are necessary depends greatly on the specifics of
-a particular censor;
-they range from simple one-hop proxies and VPNs
-to complicated steganographic systems.
-Our goal is the development of an experiment
-to test the usability of such tools.
-We focus on one particular system,
-Tor Browser, which bundles a variety of circumvention
-tools designed for different use cases.
+{\color {red} what we want to contribute to the research community.}
 
@@
 their activity and employ a browser extension to take empirical measurements (such as idle waiting time, 
-how fast a particular task was completed, etc.) throughout the duration of this experiment.
+or how fast a particular task was completed) throughout the duration of this experiment.
 
@@
 the aforementioned set of tasks. To complete all the tasks, the participants will ultimately need to get the correct
-configuration settings for the country they are simulated to be in.
+configuration settings for the country they are simulated to be in.  Figure ~\ref{dialog} shows one of the 
+Tor configuration dialog screens that a user will need to navigate.
 
@@
 \subsection{Censorship Environment Simulation}
+
+\begin{figure}[t]
+\includegraphics[width=0.5\textwidth]{configuration-dialog.png}
+\caption{The fourth and final window of the Tor configuration dialog is what users will use to 
+configure their network settings to circumvent censorship. The instructions asks users to 
+choose a pluggable transport or enter custom bridges.}
+\label{dialog}
+\end{figure}
+
 \indent \indent For our experiment, we plan to simulate and test three distinct censorship environments
@@
 
-\section{Related Work} %%%
+\section{Related Work}
 
@@
 
-\subsection{Usable Security and User Behavior}
+\subsection{Usable Security and User Behavior} %%%
 \indent \indent {\color {red}  Then also talk about any of the behaviors we are trying to mitigate,
@@
 \subsection{Experiment Overview}
-{\color {red} Talk about how the experiment was for an average user. We start
-with the cognitive walkthrough, then have them do one on a dummy
-and calibration task, we give feedback on the walkthrough, and then 
-give them the freedom to complete the web tasks.}
+\indent \indent Our experiment consisted of three parts. We first prepare our participants to perform a 
+cognitive walkthrough, ask our participants to perform a list of Internet browsing 
+tasks while performing a cognitive walkthrough, and finish with an exit survey to collect 
+additional information.
 
-After the calibration task, we asked participants to complete
-the following Tor Browser--related tasks:
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-\item Download Tor (the web browser)
-\item Install Tor
-\item Check that Tor is working
+To first ensure that our users knew what a cognitive walkthrough is, we explain what a cognitive
+walkthrough and give a demonstration of a cognitive walkthrough on a non-related dummy task 
+(drawing a red hexagon in the computer graphics program Paint). We then ask our users to perform
+an unrelated Internet-based task (finding the population of Zimbabwe) using any browser of their choice
+while performing a cognitive walkthrough along the process of completing the task. We give our 
+participants feedback on how to properly conduct a cognitive walkthrough ~\cite{wharton1994cognitive}.
+This process was also used to get users comfortable with talking our loud with the researcher and gauge 
+how comfortable users were with a computer.
+
+Then our participants were instructed to complete the following tasks while performing a cognitive
+walkthrough:
+
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item Search for, download, and install Tor Browser
 \item Do a web search for ``onions'' 
-\item Find a YouTube video for ``Ode to Joy''
-\item Use ``New Identity'' under the onion menu
-\item Explain your best understanding of all the items in the toolbar
-\end{enumerate}
-We originally had another step after Step~1, ``Configure Tor.''
-We removed it after the first two participants
-when it became clear that the wording was confusing.
-The two main buttons in the configuration wizard are labeled
-``Connect'' and ``Configure''; we did not intend for users
-to have to go through the longer ``Configure'' path,
-but they assumed they had to because of the presence
-of the word ``Configure'' in the list of tasks.
+\item Watch an ``Ode to Joy'' video on youtube 
+\item Use ``New Identity"
+\item Interact with and describe what you think the browser toolbar buttons do
+\end{itemize}
+
+The first task was to  test how easy it was for a user to search for, download, and install Tor Browser correctly for use.
+Since no software is useful if the user is not able to access it, we included this in the list of tasks.
+Additionally, we provided three tasks which highlights Tor's ``irregular'' behavior comparatively to other
+web browsers, to gauge if users were confused at the non-Google search engine, slow loading
+times for videos, and disappearing tabs upon starting a new identity. Lastly, we asked our users to 
+interact with and describe buttons on the toolbar to gauge user comprehension of how Tor functioned.
+
+We finished the experiment with a short exit survey which asked their basic demographics information 
+such as their age, gender, and education. Upon finishing the survey, participants had the opportunity to 
+ask any questions about the Tor Browser that they encountered during their walkthrough.
 
@@
 
-\url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}
-
 \subsection{Resources}
@@
 
-\noindent Subtitled screen videos:
+\noindent We transcribed the audio files from our participants' cognitive walkthroughs
+and synced them to the screen capture we took during the duration of the experiment:
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
@@
 \label{sec:survey} 
-\indent \indent Our participants will be taking the following survey, hosted online at 
-\url{http://www.surveygizmo.com/s3/2085559/Tor-Usability-Survey/SG_TEST_RUN}.\\
+\indent \indent Our participants will be taking the following exit survey, hosted through
+SurveyGizmo at: 
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item \url{http://www.surveygizmo.com/s3/2085559/Tor-Usability-Survey/SG_TEST_RUN}.
+\end{itemize}
 

### 2015-05-12 cs261n-paper/paper.tex

--- 2015-05-12 cs261n-paper/paper.tex
@@
 \subsection{Experiment Overview}
-{\color {red} Talk about how the experiment was for an average user. We start
-with the cognitive walkthrough, then have them do one on a dummy
-and calibration task, we give feedback on the walkthrough, and then 
-give them the freedom to complete the web tasks.}
+\indent \indent Our experiment consisted of three parts. We first prepare our participants to perform a 
+cognitive walkthrough, ask our participants to perform a list of Internet browsing 
+tasks while performing a cognitive walkthrough, and finish with an exit survey to collect 
+additional information.
+
+To first ensure that our users knew what a cognitive walkthrough is, we explain what a cognitive
+walkthrough and give a demonstration of a cognitive walkthrough on a non-related dummy task 
+(drawing a red hexagon in the computer graphics program Paint). We then ask our users to perform
+an unrelated Internet-based task (finding the population of Zimbabwe) using any browser of their choice
+while performing a cognitive walkthrough along the process of completing the task. We give our 
+participants feedback on how to properly conduct a cognitive walkthrough ~\cite{wharton1994cognitive}.
+This process was also used to get users comfortable with talking our loud with the researcher and gauge 
+how comfortable users were with a computer.
 
@@
 the following Tor Browser--related tasks:
+
 \begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
@@
 \end{enumerate}
+
 We originally had another step after Step~1, ``Configure Tor.''
@@
 of the word ``Configure'' in the list of tasks.
+
+The first task was to test how easy it was for a user to search for, download, and install Tor Browser correctly for use.
+Since no software is useful if the user is not able to access it, we included this in the list of tasks.
+Additionally, we provided three tasks which highlights Tor's ``irregular'' behavior comparatively to other
+web browsers, to gauge if users were confused at the non-Google search engine, slow loading
+times for videos, and disappearing tabs upon starting a new identity. Lastly, we asked our users to 
+interact with and describe buttons on the toolbar to gauge user comprehension of how Tor functioned.
+
+We finished the experiment with a short exit survey which asked their basic demographics information 
+such as their age, gender, and education. Upon finishing the survey, participants had the opportunity to 
+ask any questions about the Tor Browser that they encountered during their walkthrough.
 

### 2015-05-12 cs261n-paper/paper.tex
I guess I am done rewording this overview section.

@@
 
-The first task was to test how easy it was for a user to search for, download, and install Tor Browser correctly for use.
-Since no software is useful if the user is not able to access it, we included this in the list of tasks.
-Additionally, we provided three tasks which highlights Tor's ``irregular'' behavior comparatively to other
-web browsers, to gauge if users were confused at the non-Google search engine, slow loading
-times for videos, and disappearing tabs upon starting a new identity. Lastly, we asked our users to 
+Tasks 1-3 test how easy it was for a user to search for, download, and install Tor Browser 
+correctly for use and if they understood that they had done the tasks correctly. 
+Since no software is useful if the user is not able to access it, we found it valuable
+to test the usability of this process.  Additionally, tasks 4-6 highlights Tor's ``irregular'' behavior 
+comparatively to other web browsers. Specifically, gauge user reactions to Tor's default
+privacy-preserving search engine Startpage,  longer loading times and performance for videos, 
+and disappearing tabs upon starting a new identity. Lastly, we asked our users to 
 interact with and describe buttons on the toolbar to gauge user comprehension of how Tor functioned.

### 2015-05-12 cs261n-paper/paper.tex
wrote more of the ux sprint appendix

@@
 
-\subsection{Usable Security and User Behavior} %%%
+\subsection{Usable Security and User Behavior} %%%%%%
 \indent \indent {\color {red}  Then also talk about any of the behaviors we are trying to mitigate,
@@
 
-{\color {red}  I guess that other literature on general usability applies here too. %so search for it. 
+{\color {red}  I guess that other literature on general usability applies here too.
 Especially look into browser configuration work. }
@@
 
-\section{UX sprint} 
+\section{UX sprint} %%%%%%
 \label{sec:pilot}
- {\color {red}Details. Gory gory details of how it all went down. 
-Include the recruitment process, the setup, what the exact 
-tasks were for participants, demographics, everything. 
-It all should have a home here.}
-
-%It is easy to overestimate user comprehension and therefore be 
-%misguided for user behavior. During this process, we discovered why 
-%previous studies had not concentrated on a specific user 
-%demographic or focus on advanced features. 
-%Even though people download and install on a frequent basis, 
-%they do not know how to do it securely and are habituated into doing it in the 
-%insecure manner. Of course, this is because the average user's objective is not security. 
-%For instance, most of our participants thought the download source was a legitimate site because
-%of the look and feel of the site and none our our participants thought to verify the download, 
-%even though there were clear instructions to do so on the download page.
-
-\subsection{Motivation}
  {\color {red}  Talk about why we did what we did, and what the end goal 
@@
 
-\subsection{Methodology}
+\subsection{Methodology} %%%%%%%%%
+We 
 {\color {red} How we recruited, what the setup was like, how we got the tasks, details of 
@@
 \subsection{Results}
-{\color {red} Present situations which really were unexpected. 
-Also extract the golden quotes and state them here 
-to prove points I want to make. }
+\indent \indent Because of the limited size of the study, it's not possible to state with confidence what 
+fraction of users will encounter major usability obstacles. However, it was effective at discovering 
+and demonstrating issues that are likely to cause problems for many users. For specific problems 
+encountered by an individual user, we refer you to our resources below.
 
@@
 
-\indent \indent  Our online artifacts of our completed pilot study, such as 
+\indent \indent  Online artifacts of our completed pilot study, such as 
 the summary, results, and resulting browser changes are below:
@@
 
-\noindent We transcribed the audio files from our participants' cognitive walkthroughs
+\noindent If you would like to observe individual participants' cognitive walkthroughs, 
+we transcribed the audio files from our experiment
 and synced them to the screen capture we took during the duration of the experiment:
@@
 \end{itemize}
+
+\subsection{Acknowledgements}
+\indent \indent We thank the Tor Project for supporting the sprint, the participants, those who helped us recruit on short notice, and those who helped us plan and set goals and everyone who attended as a developer or observer: Arlo, Arthur, Ashkan, Griffin, Isis, Krishna, Mike, and Nima.
+We also thank the Tor help desk, whose \#tbb-helpdesk-frequent tag helped us prioritize tickets.
+Special thanks go to Nima for setting up the collaboration.
 

### 2015-05-12 cs261n-paper/paper.tex
Small edits.

@@
 
-Tasks 1-3 test how easy it was for a user to search for, download, and install Tor Browser 
+Tasks 1--3 test how easy it was for a user to search for, download, and install Tor Browser 
 correctly for use and if they understood that they had done the tasks correctly. 
 Since no software is useful if the user is not able to access it, we found it valuable
-to test the usability of this process.  Additionally, tasks 4-6 highlights Tor's ``irregular'' behavior 
+to test the usability of this process.  Additionally, tasks 4--6 highlight Tor's ``irregular'' behavior 
 comparatively to other web browsers. Specifically, gauge user reactions to Tor's default

### 2015-05-12 cs261n-paper/paper.tex
Use \linewidth over 0.5\textwidth.

@@
 
-\title{{\color {red}better title eventually}}
+\title{Assessing Tor's Usability as a Censorship Circumvention Tool}
 \author{Linda N. Lee, David Fifield\\
@@
 
-While our pilot was insightful, the experiment itself is not very reproducible, as it requires
-a specific target audience (journalists who have recently reported in other countries) along 
-with specific guidance and feedback on how to perform a cognitive walkthrough. This makes it hard
-for the research community to prove or build on any findings. Therefore, we take precautions
-to ensure that our full-scale study will be reproducible.
+\section{Experiment Design}
 
-\section{Experiment Design}
+\subsection{Assumptions} 
+{\color{red} do I need this here?}
 
@@
 \begin{figure}[t]
-\includegraphics[width=0.5\textwidth]{configuration-dialog.png}
+\includegraphics[width=\linewidth]{configuration-dialog.png}
 \caption{The fourth and final window of the Tor configuration dialog is what users will use to 
@@
 
-\subsection{Usability work on Tor}
+\subsection{Usability Work on Tor}
 \indent \indent  Work by Clark \etal to explore ways to simplify the Tor user interface
@@
 \subsection{Usable Security and User Behavior} %%%%%%
-\indent \indent {\color {red}  Then also talk about any of the behaviors we are trying to mitigate,
-or talk about the average user and what they know, how they are motivated,
-just sketching out the environment in general.}
+% Okay, this is a mess. Last brain dump before sleep. 
+\indent \indent {\color {red} 
+The work that started usable security, using a cognitive walkthough to expose usability issues
+in PGP ~\cite{whitten1999johnny}. The authors give suggestions for better usability, such as 
+aligning words to pictures, etc.
 
-{\color {red}  I guess that other literature on general usability applies here too.
-Especially look into browser configuration work. }
+ Work which shows that people are willing to give up privacy for instant gratification with respect to 
+ e-commerce, showing that participants' motivations are not aligned for preserving privacy, but to 
+ complete the task at hand. ~\cite{acquisti2004privacy}. Talk about how censorship might be different
+ because people need to actually configure to succeed.
+
+ People care about how easy something is to use when picking software ~\cite{}.
+
+ infrastructure is highly distributed, with the bundle of
+tools in one single installer (below is the screenshot of
+the Vidalia control panel, which runs on many different
+platforms), making the technology accessible to average
+users BUt people don't care.
+
+ users should not only look at the technical angle of their
+approach, but should also be aware of frequent attempts
+to infiltrate or otherwise identify social networks of
+people with dissenting opinions, even when they are
+only partially operating online.
+
+you might want to choose a system based on the usability of others 
+~\cite{dingledine2006anonymity}.
+
+  }
 
@@
 \label{sec:pilot}
- {\color {red}  Talk about why we did what we did, and what the end goal 
-of the experiment was. Also talk about how we expected users
-to be much better at installing and downloading than they were. }
+\indent \indent This pilot was to test-drive an experiment which examines the usability of Tor as an anonymity tool
+with respect to a target demographic of users known to use Tor (journalists who have reported in other
+countries). We emphasized the targeting of a high-risk user group of Tor and to 
+target usability changes aimed at helping those who could not afford to make mistakes. To see 
+if those users had any potentially damaging misunderstandings or incomprehensions of Tor, 
+we created tasks to licit Tor's non-typical behaviors and ask our participants to
+navigate through more advanced settings.
 
@@
 
-\subsection{Methodology} %%%%%%%%%
-We 
-{\color {red} How we recruited, what the setup was like, how we got the tasks, details of 
-how the experiment was run, and things like that.}
+\subsection{Methodology} 
+\indent \indent We recruited five journalists from Berkeley by reaching out to journalist contacts.
+ We recruited five users with an average age of 28 ($\sigma = 13 $~years). Out of 
+our five participants, 3 were female.
+
+We conducted the experiment on January 30-31st in Soda 
+Hall at the University of Berkeley, California. We used a 2013 Macbook Air and a 
+2012 Acer Aspire AS5750Z-4835 Windows laptop to give users a choice in using whatever they were comfortable with. 
+All of our participants were Mac users. During the experiment, 
+we recorded video data of their computer screen and audio data to capture their cognitive walkthrough. 
+The average time to complete the given tasks, not including the cognitive
+walkthrough nor the exit survey, was 26 minutes ($\sigma = 7$~min).
+
+This pilot was held in conjunction with the first Tor UX sprint. With IRB approval, Tor developers
+observed the screens of our participants, which was set to broadcast to a separate  
+room during the experiment. Audio of the cognitive walkthrough was not broadcast for privacy
+considerations as voice is considered an identifying characteristic.
 
@@
 fraction of users will encounter major usability obstacles. However, it was effective at discovering 
-and demonstrating issues that are likely to cause problems for many users. For specific problems 
+and demonstrating issues that are likely to cause problems for many users. 
+People did have difficulty with installing Tor Browser (principally because of the Gatekeeper 
+code-signing feature on OS X), did not understand what many of the toolbar options meant, 
+and were confused by most Tor-specific behaviors. For specific problems 
 encountered by an individual user, we refer you to our resources below.

### 2015-05-12 cs261n-paper/paper.tex
ux methodology

@@
 
+While our pilot was insightful, the experiment itself is not very reproducible, as it requires
+a specific target audience (journalists who have recently reported in other countries) along 
+with specific guidance and feedback on how to perform a cognitive walkthrough. This makes it hard
+for the research community to prove or build on any findings. Therefore, we take precautions
+to ensure that our full-scale study will be reproducible.
+
 \section{Experiment Design}
-
-\subsection{Assumptions} 
-{\color{red} do I need this here?}
 
@@
 \begin{figure}[t]
-\includegraphics[width=\linewidth]{configuration-dialog.png}
+\includegraphics[width=0.5\textwidth]{configuration-dialog.png}
 \caption{The fourth and final window of the Tor configuration dialog is what users will use to 
@@
 
-Tasks 1--3 test how easy it was for a user to search for, download, and install Tor Browser 
+Tasks 1-3 test how easy it was for a user to search for, download, and install Tor Browser 
 correctly for use and if they understood that they had done the tasks correctly. 
 Since no software is useful if the user is not able to access it, we found it valuable
-to test the usability of this process.  Additionally, tasks 4--6 highlight Tor's ``irregular'' behavior 
+to test the usability of this process.  Additionally, tasks 4-6 highlights Tor's ``irregular'' behavior 
 comparatively to other web browsers. Specifically, gauge user reactions to Tor's default

### 2015-05-12 cs261n-paper/paper.tex
delete a paragraph inline paper for ux sprint
Add a walkthrough graphic.
I went in to VLC, turned on subtitles, "Take Snapshot", opened in Gimp,
resized to 3.4 inches wide at 150 dpi.

--- 2015-05-12 cs261n-paper/paper.tex
@@
 
+\begin{figure}
+\includegraphics[width=\linewidth]{walkthrough.png}
+\caption{
+A participant narrates their thinking
+while downloading Tor Browser.
+% https://people.torproject.org/~dcf/uxsprint2015/p3.srt
+{
+\it
+``There's this big purple icon on the left side of the screen that says `Download Tor Browser',
+so I'm going to click on that because it seems like the most obvious thing.
+There are a couple of other small words on the screen that I'm not going to look at, because this seems like the most obvious thing to do.''
+}
+}
+\label{walkthrough}
+\end{figure}
+
 \subsection{Resources}

### 2015-05-12 cs261n-paper/paper.tex
Move screenshot to Resources, refer to it in the text.

@@
 
+\subsection{Resources}
+
 \begin{figure}
@@
 
-\subsection{Resources}
-
 \indent \indent  Online artifacts of our completed pilot study, such as 
@@
 we transcribed the audio files from our experiment
-and synced them to the screen capture we took during the duration of the experiment:
+and synced them to the screen capture we took during the duration of the experiment.
+Figure~\ref{walkthrough} shows a screenshot of one of the videos.
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt

### 2015-05-12 cs261n-paper/paper.tex
related work

--- 2015-05-12 cs261n-paper/paper.tex
@@
 
-\subsection{Usability Work on Tor}
+\subsection{Usability for Security Software}
+\indent \indent 
+We evaluate the usability of the configuration window's interface. Generally, usability 
+refers to the learnability, efficiency, memorability, error rate/recoverability, and satisfaction
+during use. To achieve these goals, the HCI community has established heuristics for user
+interface design: visibility of the system status, using familiar
+language, preventing errors, having consistent visuals, flexibility and efficiency of use, 
+error recovery, and leveraging recognition over memorization ~\cite{nielsen199510}. Note
+that these are not specific usability guidelines, but heuristics.
+
+Usability has sligtly different meanings depending on the context. Some emphasize
+learnability, flexibility, and ease of user. In a security context, the priorities are whatever is 
+required for the security to be used effectively. As stated by Whitten \etal, a security software is 
+usable if people who are expected to use it are reliably made aware of the security tasks to perform, 
+are able to figure out how to successfully perform those tasks, do not make dangerous errors, and
+are sufficiently comfortable with the software interface ~\cite{whitten1999johnny}. Since usable security 
+has user interface design goals than general consumer software, it likewise requires usability evaluation
+methods which are suitable to test these properties. Our goals are to test that the Tor Browser, 
+communicates an accurate conceptual model of the task to the users as quickly as possible, provide guidance to 
+users at the right time, and use warnings and other interactive tools to prevent any mistakes.
+
+\subsection{Usability and Tor}
 \indent \indent  Work by Clark \etal to explore ways to simplify the Tor user interface
@@
 
-\subsection{Usable Security and User Behavior} %%%%%%
-% Okay, this is a mess. Last brain dump before sleep. 
-\indent \indent {\color {red} 
-The work that started usable security, using a cognitive walkthough to expose usability issues
-in PGP ~\cite{whitten1999johnny}. The authors give suggestions for better usability, such as 
-aligning words to pictures, etc.
-
- Work which shows that people are willing to give up privacy for instant gratification with respect to 
- e-commerce, showing that participants' motivations are not aligned for preserving privacy, but to 
- complete the task at hand. ~\cite{acquisti2004privacy}. Talk about how censorship might be different
- because people need to actually configure to succeed.
-
- People care about how easy something is to use when picking software ~\cite{}.
-
- infrastructure is highly distributed, with the bundle of
-tools in one single installer (below is the screenshot of
-the Vidalia control panel, which runs on many different
-platforms), making the technology accessible to average
-users BUt people don't care.
-
- users should not only look at the technical angle of their
-approach, but should also be aware of frequent attempts
-to infiltrate or otherwise identify social networks of
-people with dissenting opinions, even when they are
-only partially operating online.
-
-you might want to choose a system based on the usability of others 
-~\cite{dingledine2006anonymity}.
-
-  }
-
 \appendix
 
-\section{UX sprint} %%%%%%
+\section{UX sprint}
 \label{sec:pilot}

### 2015-05-12 cs261n-paper/paper.tex

@@
 
+\begin{figure}
+\includegraphics[width=\linewidth]{walkthrough.png}
+\caption{
+A participant narrates their thinking
+while downloading Tor Browser.
+% https://people.torproject.org/~dcf/uxsprint2015/p3.srt
+{
+\it
+``There's this big purple icon on the left side of the screen that says `Download Tor Browser',
+so I'm going to click on that because it seems like the most obvious thing.
+There are a couple of other small words on the screen that I'm not going to look at, because this seems like the most obvious thing to do.''
+}
+}
+\label{walkthrough}
+\end{figure}
+
 \indent \indent  Online artifacts of our completed pilot study, such as 

### 2015-05-12 cs261n-paper/paper.tex
results todo note to self
scratch superfluous section
put in quotes

@@
 \section{Experiment Design}
-
-\subsection{Assumptions} 
-{\color{red} do I need this here?}
 
@@
 
+{\color {red}
+I should do this if I have time and finish polishing.
+
+Unexpected observations:
+
+Something unexpected which interfered with Tor's usability is that Mac's usable 
+security feature which prevents opening unsigned code made Tor much less usable.
+
+Lessons learned: 
+Leverage visuals and interface design to prioritize communication to users. Most of the 
+important information was communicated with paragraphs of text that users actively 
+communicated that they did not read or did not want to read and only read because of 
+issues they were experiencing.
+
+Most participants did not have any interest or comprehension for advanced features.
+In usability literature, it is good to just configure these for users, but Tor does not track
+information on users. Maybe it's good to have failsafe defaults and less options.
+
+Quotes:
+
+SEO poisoning opportunity:
+
+`` I'm going to use Chrome, because that's what I use at home...
+I'm just going to open it up, and I'm going to type in "download tor" because 
+that's what I'm supposed to do. And I'm going to click on the first one, because,
+at the top, which is `Download Tor'.'' -P1
+
+``Okay. So I just would type in `tor' in the uh search engine and `Tor Project'...
+`Anonymity Online'... I guess this is it. And I click. And the there is a "Download Tor", 
+so I am going to click this.'' -P2
+
+``There's, like, the first thing on the page is called the Tor Project, and I wouldn't figure out what that is,
+but then it says `Tor Browser' just a little bit underneath, so I get, I put two and two together and I figure this is probably what I have to download.'' -P3
+
+``so I am going to type in `tor mac download.'
+And that gives me some suggestions. I pick the first one.'' -P4
+
+``I am seeing the second result is `Download Tor.'
+That might save a few steps, I will click on that.'' -P5
+
+On using visuals and emphasis:
+
+``...it looks like I should click there, because it is purple. No, not because it's purple, but... 
+[laughter] because it has that little cloud with the arrow... and you can't click anywhere else to download.'' -P1
+
+``There's this big purple icon on the left side of the screen that says `Download Tor Browser',
+so I'm going to click on that because it seems like the most obvious thing.
+There are a couple of other small words on the screen that I'm not going to look at, because this seems like the most obvious thing to do.'' -P3
+
+"Don't open documents downloaded through Tor... That doesn't make sense to me.
+But I'll just pay attention because it's in capitals and it's like they're yelling at me.'' -P1
+
+Gatekeeper stuff:
+
+`` `The app has been modified...', blah blah blah... Oh, this is annoying. I would maybe normally stop now.'' -P1
+
+`` `TorBrowser' can't be opened because it's from an unidentified developer.'
+Grr! I express some frustration at this fact.'' - P4
+
+Advanced Settings:
+
+``Yeah, and like the settings of your Tor Browser, I guess.'' -P1
+
+``But then I have toyed around before with like preferences and looking around and 
+usually it's out of my understanding.'' -P5
+
+``Oh, hey! There's the onion menu. That was not obviously defined at all!'' -P4
+
+Someone who understands:
+
+``So yeah, there was an onion. Small green onion. And yeah, I guess, it's new identity.
+So I'm guessing it's the same thing as with Google, when you open a page and you don't 
+want the history to show up or something. And then you can, it's like you're disconnected 
+from your Gmail account and everything, you can type that as a different user.'' -P3
+
+}
+
 \subsection{Resources}

### 2015-05-12 cs261n-paper/paper.tex
added and formatted quotes for ux results

--- 2015-05-12 cs261n-paper/paper.tex
@@
 
+{\color {red}
+
+We saw an SEO poisoning opportunity.
+
+\begin{quote}{\it
+`` I'm going to use Chrome, because that's what I use at home...
+I'm just going to open it up, and I'm going to type in "download tor" because 
+that's what I'm supposed to do. And I'm going to click on the first one, because,
+at the top, which is `Download Tor'.''} -P
+\end{quote}
+
+\begin{quote}{\it
+``Okay. So I just would type in `tor' in the uh search engine and `Tor Project'...
+`Anonymity Online'... I guess this is it. And I click. And the there is a "Download Tor", 
+so I am going to click this.''} -P2
+\end{quote}
+
+\begin{quote}{\it
+``There's, like, the first thing on the page is called the Tor Project, and I wouldn't figure out what that is,
+but then it says `Tor Browser' just a little bit underneath, so I get, I put two and two together and I figure 
+this is probably what I have to download.'}' -P3
+\end{quote}
+
+\begin{quote}{\it
+``so I am going to type in `tor mac download.'
+And that gives me some suggestions. I pick the first one.'''} -P4
+\end{quote}
+
+\begin{quote}{\it
+``I am going to go to torproject.org... I am seeing the second result is `Download Tor.'
+That might save a few steps, I will click on that.''} -P5
+\end{quote}
+
+Something unexpected which interfered with Tor's usability is that Mac's usable 
+security feature which prevents opening unsigned code made Tor much less usable.
+
+\begin{quote}{\it
+`` `The app has been modified...', blah blah blah... Oh, this is annoying. I would maybe normally stop now.''} -P1
+\end{quote}
+
+\begin{quote}{\it
+`` `TorBrowser' can't be opened because it's from an unidentified developer.'
+Grr! I express some frustration at this fact.''} - P4
+\end{quote}
+
+Lessons learned: 
+Leverage visuals and interface design to prioritize communication to users. Most of the 
+important information was communicated with paragraphs of text that users actively 
+communicated that they did not read or did not want to read and only read because of 
+issues they were experiencing.
+
+\begin{quote}{\it
+``...it looks like I should click there, because it is purple. No, not because it's purple, but... 
+[laughter] because it has that little cloud with the arrow... and you can't click anywhere else to download.''} -P1 
+\end{quote}
+
+\begin{quote}{\it
+``There's this big purple icon on the left side of the screen that says `Download Tor Browser',
+so I'm going to click on that because it seems like the most obvious thing.
+There are a couple of other small words on the screen that I'm not going to look at, because this seems like the most obvious thing to do.''} -P3
+\end{quote}
+
+\begin{quote}{\it
+"Don't open documents downloaded through Tor... That doesn't make sense to me.
+But I'll just pay attention because it's in capitals and it's like they're yelling at me.''} -P1
+\end{quote}
+
+Most participants did not have any interest or comprehension for advanced features.
+In usability literature, it is good to just configure these for users, but Tor does not track
+information on users. Maybe it's good to have failsafe defaults and less options.
+
+\begin{quote}{\it
+``Yeah, and like the settings of your Tor Browser, I guess.''} -P1
+\end{quote}
+
+\begin{quote}{\it
+``But then I have toyed around before with like preferences and looking around and 
+usually it's out of my understanding.''} -P5
+\end{quote}
+
+\begin{quote}{\it
+``So yeah, there was an onion. Small green onion. And yeah, I guess, it's new identity.
+So I'm guessing it's the same thing as with Google, when you open a page and you don't 
+want the history to show up or something. And then you can, it's like you're disconnected 
+from your Gmail account and everything, you can type that as a different user.''} -P3 
+\end{quote}
+}
+
 \subsection{Resources}

### 2015-05-12 cs261n-paper/paper.tex
Remove extra space before refs.

@@
 countries) and aiming to identify how well they could understand Tor's non-typical behaviors and 
-navigate advanced settings. For the full details of this pilot experiment, we refer you to Appendix ~\ref{sec:pilot}.
+navigate advanced settings. For the full details of this pilot experiment, we refer you to Appendix~\ref{sec:pilot}.
 
@@
 the aforementioned set of tasks. To complete all the tasks, the participants will ultimately need to get the correct
-configuration settings for the country they are simulated to be in.  Figure ~\ref{dialog} shows one of the 
+configuration settings for the country they are simulated to be in.  Figure~\ref{dialog} shows one of the 
 Tor configuration dialog screens that a user will need to navigate.
@@
 The survey consists of 17 questions total, with a basic breakdown as follows. 
-The complete list of survey questions can be found in Appendix ~\ref{sec:survey}.
+The complete list of survey questions can be found in Appendix~\ref{sec:survey}.
 
@@
 language, preventing errors, having consistent visuals, flexibility and efficiency of use, 
-error recovery, and leveraging recognition over memorization ~\cite{nielsen199510}. Note
+error recovery, and leveraging recognition over memorization~\cite{nielsen199510}. Note
 that these are not specific usability guidelines, but heuristics.
@@
 are able to figure out how to successfully perform those tasks, do not make dangerous errors, and
-are sufficiently comfortable with the software interface ~\cite{whitten1999johnny}. Since usable security 
+are sufficiently comfortable with the software interface~\cite{whitten1999johnny}. Since usable security 
 has user interface design goals than general consumer software, it likewise requires usability evaluation
@@
 \indent \indent  Work by Clark \etal to explore ways to simplify the Tor user interface
-has led to great usability improvements ~\cite{clark2007usability}.  Clark analyzed the challenges 
+has led to great usability improvements~\cite{clark2007usability}.  Clark analyzed the challenges 
 of using multiple Tor-related tools including TorPark, Vidalia, FoxyProxy, and TorButton to find that
@@
 anonymized browser windows while using tor, unclear download and install processes, and 
-confusion as to why the Tor behaves in peculiar ways ~\cite{norcie2012eliminating}. A follow up
+confusion as to why the Tor behaves in peculiar ways~\cite{norcie2012eliminating}. A follow up
 study by Norcie \etal verifies that the changes recommended to the Tor Project were indeed 
@@
 design heuristics for designing usable anonymous systems, such as easy installation, communicating
-tradeoffs made to users, and informing why, not how, precautions are taken for security guarantees ~\cite{norcie2014johnny}.
+tradeoffs made to users, and informing why, not how, precautions are taken for security guarantees~\cite{norcie2014johnny}.
 
@@
 while performing a cognitive walkthrough along the process of completing the task. We give our 
-participants feedback on how to properly conduct a cognitive walkthrough ~\cite{wharton1994cognitive}.
+participants feedback on how to properly conduct a cognitive walkthrough~\cite{wharton1994cognitive}.
 This process was also used to get users comfortable with talking our loud with the researcher and gauge 

### 2015-05-12 cs261n-paper/paper.tex
Typo.

@@
 if those users had any potentially damaging misunderstandings or incomprehensions of Tor, 
-we created tasks to licit Tor's non-typical behaviors and ask our participants to
+we created tasks to elicit Tor's non-typical behaviors and ask our participants to
 navigate through more advanced settings.

### 2015-05-12 cs261n-paper/paper.tex
Quote formatting.

@@
 \begin{quote}{\it
-`` I'm going to use Chrome, because that's what I use at home...
-I'm just going to open it up, and I'm going to type in "download tor" because 
+``I'm going to use Chrome, because that's what I use at home\ldots\ 
+I'm just going to open it up, and I'm going to type in `download tor' because 
 that's what I'm supposed to do. And I'm going to click on the first one, because,
-at the top, which is `Download Tor'.''} -P
+at the top, which is `Download Tor'.''} \mbox{---P}
 \end{quote}
@@
 \begin{quote}{\it
-``Okay. So I just would type in `tor' in the uh search engine and `Tor Project'...
-`Anonymity Online'... I guess this is it. And I click. And the there is a "Download Tor", 
-so I am going to click this.''} -P2
+``Okay. So I just would type in `tor' in the uh search engine and `Tor Project'\ldots\ 
+`Anonymity Online'\ldots\ I guess this is it. And I click. And the there is a `Download Tor', 
+so I am going to click this.''} \mbox{---P2}
 \end{quote}
@@
 but then it says `Tor Browser' just a little bit underneath, so I get, I put two and two together and I figure 
-this is probably what I have to download.'}' -P3
+this is probably what I have to download.'}' \mbox{---P3}
 \end{quote}
@@
 \begin{quote}{\it
-``so I am going to type in `tor mac download.'
-And that gives me some suggestions. I pick the first one.'''} -P4
+``\ldots so I am going to type in `tor mac download'.
+And that gives me some suggestions. I pick the first one.''} \mbox{---P4}
 \end{quote}
@@
 \begin{quote}{\it
-``I am going to go to torproject.org... I am seeing the second result is `Download Tor.'
-That might save a few steps, I will click on that.''} -P5
+``I am going to go to torproject.org\ldots\ I am seeing the second result is `Download Tor.'
+That might save a few steps, I will click on that.''} \mbox{---P5}
 \end{quote}
@@
 \begin{quote}{\it
-`` `The app has been modified...', blah blah blah... Oh, this is annoying. I would maybe normally stop now.''} -P1
+``\/`The app has been modified\ldots', blah blah blah\ldots\  Oh, this is annoying. I would maybe normally stop now.''} \mbox{---P1}
 \end{quote}
@@
 \begin{quote}{\it
-`` `TorBrowser' can't be opened because it's from an unidentified developer.'
-Grr! I express some frustration at this fact.''} - P4
+``\/`\/``TorBrowser'' can't be opened because it's from an unidentified developer.'
+Grr! I express some frustration at this fact.''} \mbox{---P4}
 \end{quote}
@@
 \begin{quote}{\it
-``...it looks like I should click there, because it is purple. No, not because it's purple, but... 
-[laughter] because it has that little cloud with the arrow... and you can't click anywhere else to download.''} -P1 
+``\ldots it looks like I should click there, because it is purple. No, not because it's purple, but\ldots\ 
+[laughter] because it has that little cloud with the arrow\ldots\ and you can't click anywhere else to download.''} \mbox{---P1} 
 \end{quote}
@@
 so I'm going to click on that because it seems like the most obvious thing.
-There are a couple of other small words on the screen that I'm not going to look at, because this seems like the most obvious thing to do.''} -P3
+There are a couple of other small words on the screen that I'm not going to look at, because this seems like the most obvious thing to do.''} \mbox{---P3}
 \end{quote}
@@
 \begin{quote}{\it
-"Don't open documents downloaded through Tor... That doesn't make sense to me.
-But I'll just pay attention because it's in capitals and it's like they're yelling at me.''} -P1
+``Don't open documents downloaded through Tor\ldots\ That doesn't make sense to me.
+But I'll just pay attention because it's in capitals and it's like they're yelling at me.''} \mbox{---P1}
 \end{quote}
@@
 \begin{quote}{\it
-``Yeah, and like the settings of your Tor Browser, I guess.''} -P1
+``Yeah, and like the settings of your Tor Browser, I guess.''} \mbox{---P1}
 \end{quote}
@@
 ``But then I have toyed around before with like preferences and looking around and 
-usually it's out of my understanding.''} -P5
+usually it's out of my understanding.''} \mbox{---P5}
 \end{quote}
@@
 want the history to show up or something. And then you can, it's like you're disconnected 
-from your Gmail account and everything, you can type that as a different user.''} -P3 
+from your Gmail account and everything, you can type that as a different user.''} \mbox{---P3} 
 \end{quote}

### 2015-05-12 cs261n-paper/paper.tex
First quote is P1.
rough ux results section

--- 2015-05-12 cs261n-paper/paper.tex
@@
 countries) and aiming to identify how well they could understand Tor's non-typical behaviors and 
-navigate advanced settings. For the full details of this pilot experiment, we refer you to Appendix~\ref{sec:pilot}.
+navigate advanced settings. For the full details of this pilot experiment, we refer you to Appendix ~\ref{sec:pilot}.
 
@@
 the aforementioned set of tasks. To complete all the tasks, the participants will ultimately need to get the correct
-configuration settings for the country they are simulated to be in.  Figure~\ref{dialog} shows one of the 
+configuration settings for the country they are simulated to be in.  Figure ~\ref{dialog} shows one of the 
 Tor configuration dialog screens that a user will need to navigate.
@@
 The survey consists of 17 questions total, with a basic breakdown as follows. 
-The complete list of survey questions can be found in Appendix~\ref{sec:survey}.
+The complete list of survey questions can be found in Appendix ~\ref{sec:survey}.
 
@@
 language, preventing errors, having consistent visuals, flexibility and efficiency of use, 
-error recovery, and leveraging recognition over memorization~\cite{nielsen199510}. Note
+error recovery, and leveraging recognition over memorization ~\cite{nielsen199510}. Note
 that these are not specific usability guidelines, but heuristics.
@@
 are able to figure out how to successfully perform those tasks, do not make dangerous errors, and
-are sufficiently comfortable with the software interface~\cite{whitten1999johnny}. Since usable security 
+are sufficiently comfortable with the software interface ~\cite{whitten1999johnny}. Since usable security 
 has user interface design goals than general consumer software, it likewise requires usability evaluation
@@
 \indent \indent  Work by Clark \etal to explore ways to simplify the Tor user interface
-has led to great usability improvements~\cite{clark2007usability}.  Clark analyzed the challenges 
+has led to great usability improvements ~\cite{clark2007usability}.  Clark analyzed the challenges 
 of using multiple Tor-related tools including TorPark, Vidalia, FoxyProxy, and TorButton to find that
@@
 anonymized browser windows while using tor, unclear download and install processes, and 
-confusion as to why the Tor behaves in peculiar ways~\cite{norcie2012eliminating}. A follow up
+confusion as to why the Tor behaves in peculiar ways ~\cite{norcie2012eliminating}. A follow up
 study by Norcie \etal verifies that the changes recommended to the Tor Project were indeed 
@@
 design heuristics for designing usable anonymous systems, such as easy installation, communicating
-tradeoffs made to users, and informing why, not how, precautions are taken for security guarantees~\cite{norcie2014johnny}.
+tradeoffs made to users, and informing why, not how, precautions are taken for security guarantees ~\cite{norcie2014johnny}.
 
@@
 while performing a cognitive walkthrough along the process of completing the task. We give our 
-participants feedback on how to properly conduct a cognitive walkthrough~\cite{wharton1994cognitive}.
+participants feedback on how to properly conduct a cognitive walkthrough ~\cite{wharton1994cognitive}.
 This process was also used to get users comfortable with talking our loud with the researcher and gauge 
@@
 \subsection{Results}
-\indent \indent Because of the limited size of the study, it's not possible to state with confidence what 
+\indent \indent This experiment uncovered a powerful vector for attack, an unlikely source
+of usability issues, and insight into how to better communicate to users so that they can be 
+empowered to use Tor Browser and its advanced settings. 
+Because of the limited size of the study, it's not possible to state with confidence what 
 fraction of users will encounter major usability obstacles. However, it was effective at discovering 
@@
 and were confused by most Tor-specific behaviors. For specific problems 
-encountered by an individual user, we refer you to our resources below.
+encountered by an individual user, we refer you to our resources online.
 
-{\color {red}
-
-We saw an SEO poisoning opportunity.
+\subsubsection{How to Attack Users}
+During the task completion process, we observed that all our participants are likely 
+susceptible to a search engine optimization (SEO) poisoning attack. Most of our 
+participants  were on autopilot to complete this standard download task and 
+were also not aware of the possibility that their download may come from an 
+illegitimate source. Usually, our participants picked whichever was the first search
+result and believed it to be a good enough source for the download:
 
@@
 that's what I'm supposed to do. And I'm going to click on the first one, because,
-at the top, which is `Download Tor'.''} -P
+at the top, which is `Download Tor'.''} -P1
 \end{quote}
@@
 \begin{quote}{\it
-``Okay. So I just would type in `tor' in the uh search engine and `Tor Project'...
-`Anonymity Online'... I guess this is it. And I click. And the there is a "Download Tor", 
-so I am going to click this.''} -P2
+``so I am going to type in `tor mac download.'
+And that gives me some suggestions. I pick the first one.'''} -P4
 \end{quote}
@@
 
-\begin{quote}{\it
-``so I am going to type in `tor mac download.'
-And that gives me some suggestions. I pick the first one.'''} -P4
-\end{quote}
+There was one participant who did not pick the first search result, but to save themselves
+time while completing the task:
 
@@
 
-Something unexpected which interfered with Tor's usability is that Mac's usable 
-security feature which prevents opening unsigned code made Tor much less usable.
+Luckily, all of our users managed to download Tor browser from the legitimate source. However, 
+upon searching through various search engines with a clear history, we found that cnet.com or techsource.com 
+ appears as the first search result. Defenses against SEO optimization would be prudent to employ.
+
+\subsubsection{Fighting Mac's Security Features}
+The biggest usability struggle was the result of tensions between Mac's security feature 
+and Tor's usability, rather than a specific feature of the Tor Browser itself.
 
@@
 
-Lessons learned: 
-Leverage visuals and interface design to prioritize communication to users. Most of the 
-important information was communicated with paragraphs of text that users actively 
-communicated that they did not read or did not want to read and only read because of 
-issues they were experiencing.
+\subsubsection{On Visual Communication}
+Through observing our participants, 
+we believe visual elements into their user interface design may be the key to 
+communicating with users.
 
@@
 
-Most participants did not have any interest or comprehension for advanced features.
-In usability literature, it is good to just configure these for users, but Tor does not track
-information on users. Maybe it's good to have failsafe defaults and less options.
+\subsubsection{User Comprehension} 
+Most of our participants did not have the expertise to understand 
+the advanced setting for Tor Browser, and were wary to user it, but explaining why an option 
+tis available to the user may increase comprehension and tailored use.
 
@@
 \end{quote}
-}
 

### 2015-05-12 cs261n-paper/paper.tex

--- 2015-05-12 cs261n-paper/paper.tex
@@
 that's what I'm supposed to do. And I'm going to click on the first one, because,
-at the top, which is `Download Tor'.''} \mbox{---P}
+at the top, which is `Download Tor'.''}\mbox{---P1}
 \end{quote}
@@
 
-\begin{quote}{\it
-``There's, like, the first thing on the page is called the Tor Project, and I wouldn't figure out what that is,
-but then it says `Tor Browser' just a little bit underneath, so I get, I put two and two together and I figure 
-this is probably what I have to download.'}' \mbox{---P3}
-\end{quote}
-
+There was one participant who did not pick the first search result, but to save themselves
+time while completing the task: 
 \begin{quote}{\it

### 2015-05-12 cs261n-paper/paper.tex
Editing of introduction.

@@
 for the purpose of circumvention.
-We focus our analysis on the browser's connection configuration dialog,
-which enables circumvention even under stringent censors,
-when used correctly.
-The experiment is aimed at evaluating whether, and how easily users can circumvent censorship using Tor Browser,
+We focus our analysis on the browser's connection configuration dialog, which,
+when used correctly,
+enables circumvention under many of the world's most stringent censors.
+The experiment is aimed at evaluating whether, and how easily users can circumvent censorship using Tor Browser
 under several censorship environments.
@@
 the lessons we learned from it,
-and how it guided our future experimental ambitions.
+and how it guided the current design.
 The experiment we describe is scheduled to run in August 2015.
@@
 and improving the usability of security software.
-Both ``usability'' and ``security'' encompass many topics;
+The topics of usability and security encompass many ideas;
 therefore we limit our scope and focus on
-an important and timely use case:
-user configuration of software to evade Internet censorship.
+a timely use case:
+end-user configuration of software to evade Internet censorship.
 In this report, we detail the design of a usability-focused user experiment,
@@
 
-We hold that usability must be regarded as a security property.
-It should be part of the design of security software.
+We hold that usability is a security property.
+Usability considerations should be part of the design of security software.
 Usable software not only decreases the risk of making mistakes
-with dangerous security consequences,
-but also provides a bridge over which users can
-transition from substitutes that are less safe.
+with potentially serious security consequences,
+but also provides users with a realistic alternative to
+substitute programs that are nice to use but less safe.
 
@@
 basic web browsing tasks in the presence of a censor.
+The topic of this paper is the design of the study.
 We will place users in a controlled network environment
@@
 Tor Browser, which bundles a variety of circumvention
-tools designed for different use cases.
+tools that are designed to evade different kinds of censors.
 
@@
 
-\indent \indent The Tor Project, known for its anonymity network~\cite{tor-design},
+\indent \indent The Tor Project, best known for its anonymity network~\cite{tor-design},
 has in recent years become an important player in the world of
@@
 In response, work began on various anti-censorship technologies
-now known as ``pluggable transports''~\cite{pluggable-transports}.
-Currently there are over 15,000 users accessing the Tor network
+now known as ``bridges'' and ``pluggable transports''~\cite{pluggable-transports}.
+As of May 2015, there are over 15,000 users accessing the Tor network
 at any given time using one of these
@@
 accessible even to nontechnical users.
-Its user interface was greatly overhauled in its version~3.5 release,
-and since then it has not had a comprehensive usability evaluation.
+It has not undergone a formal usability assessment since
+its user interface was overhauled in its version~3.5 release in December 2013.
+A central component of its user configuration interface
+is a panel to select bridges and pluggable transports
+for censorship circumvention.
+This selection interface is the focus of our study.
 
 \subsection{What is Required of Users}
-\indent \indent For users to circumvent censorship in their resident countries, they will need to 
-configure Tor to set up a proxy, bridge, or both. The requirement of the user will vary on their censorship
-environment, specifically, if they need to conceal the fact that they are using Tor or if Tor entry nodes 
+\indent \indent In order to circumvent censorship in their resident countries, users need to 
+configure Tor Browser to use a bridge or pluggable transport. This requirement of the user will vary depending on their censorship
+environment; specifically, on whether they need to conceal the fact that they are using Tor or if Tor entry nodes 
 have been blocked by the government.
-There is a configuration wizard to help guide users through setting up their connection, but they require the user to provide IP addresses of proxies or bridges to use.
+There is a configuration wizard to help guide users through setting up their connection, but they require the user to provide the IP addresses of proxies or bridges to use.
 
@@
 of ways, including reading online manuals on how to configure Tor, finding out information through word of mouth, 
-or figuring out correct configurations themselves by trial and error.  We cannot accurately simulate the effects
+or figuring out correct configurations themselves by trial and error.  We cannot meaningfully simulate the effects
 of these localized effects during our experiment.
@@
 However, we are testing the usability, and therefore comprehension and user-friendliness, of the Tor configuration 
-dialog, which will require users in the most strict censorship environments to navigate through three configuration windows and provide correct answers all along the process in order to configure the connection correctly.
-Knowledge
-required includes if their connection would require a proxy to access the Internet, the IP address of a bridge if required, 
+dialog, which requires users in the most strict censorship environments to navigate through three configuration windows and provide correct answers all along the process in order to configure the connection correctly.
+Users must know
+whether their connection requires a proxy to access the Internet, the IP address of a bridge if required, 
 and which pluggable transports are functional in their country.

### 2015-05-12 cs261n-paper/paper.tex
finished ux writeup

--- 2015-05-12 cs261n-paper/paper.tex
@@
 empowered to use Tor Browser and its advanced settings.
-Because of the limited size of the study, it's not possible to state with confidence what 
-fraction of users will encounter major usability obstacles. However, it was effective at discovering 
-and demonstrating issues that are likely to cause problems for many users. 
-People did have difficulty with installing Tor Browser (principally because of the Gatekeeper 
-code-signing feature on OS X), did not understand what many of the toolbar options meant, 
-and were confused by most Tor-specific behaviors. For specific problems 
-encountered by an individual user, we refer you to our resources online.
 
@@
 time while completing the task:
-\begin{quote}{\it
-``\ldots so I am going to type in `tor mac download'.
-And that gives me some suggestions. I pick the first one.''} \mbox{---P4}
-\end{quote}
 
@@
 \subsubsection{Fighting Mac's Security Features}
-The biggest usability struggle was the result of tensions between Mac's security feature 
-and Tor's usability, rather than a specific feature of the Tor Browser itself.
+The biggest usability obstacle was the result of tensions between Mac's Gatekeeper 
+code-signing feature on OS X, which prevents users from opening unsigned code 
+downloaded from the Internet to execute on their machine unless overridden through
+managing system preferences. Surprisingly, the feature which impacted Tor's usability
+the most was the tension between a security precaution, and Tor's decision to self-sign
+their downloads, rather than a specific feature of the Tor Browser itself. We found that 
+encountering the Gatekeeper will cause frustration to most users, and may be enough 
+to stop our participants in the download process:
 
@@
 
+As a result, Tor has developed a step-by-step visual guide on the download page to 
+help Mac OS X users to bypassing the Gatekeeper during their download.
+
 \subsubsection{On Visual Communication}
-Through observing our participants, 
-we believe visual elements into their user interface design may be the key to 
-communicating with users.
+Our participants did not read much of the text provided on the download page or elsewhere during 
+the experiment. Critical actions were predominantly guided by visual cues:
 
@@
 
-\begin{quote}{\it
-``Don't open documents downloaded through Tor\ldots\ That doesn't make sense to me.
-But I'll just pay attention because it's in capitals and it's like they're yelling at me.''} \mbox{---P1}
-\end{quote}
+Prudently and selectively incorporating visual elements into user interface design may be the key to 
+communicating with users and guiding correct user behaviors.
 
 \subsubsection{User Comprehension}
+
 Most of our participants did not have the expertise to understand 
-the advanced setting for Tor Browser, and were wary to user it, but explaining why an option 
-tis available to the user may increase comprehension and tailored use.
+the advanced settings for the Tor Browser:
 
@@
 
+There was one participant who communicated a correct and thorough understanding of the 
+new identity feature:
+
 \begin{quote}{\it
@@
 
+Notice that this user explained what the feature can do for him, rather than how the 
+feature works. For the end user, the reason why a security feature is employed is what 
+makes a feature valuable and thus motivates them to use the feature. Communicating why a 
+feature is present may be more effective for increasing use of advanced features 
+than communicating the technical details of how a feature works.
+
 \subsection{Resources}
+
+\indent \indent Because of the limited size of the study, it's not possible to state with confidence what 
+fraction of users will encounter major usability obstacles. However, it was effective at discovering 
+and demonstrating issues that are likely to cause problems for many users. 
+People did have difficulty with installing Tor Browser (principally because of the Gatekeeper 
+code-signing feature on OS X), did not understand what many of the toolbar options meant, 
+and were confused by most Tor-specific behaviors. For specific problems 
+encountered by an individual user, we refer you to our resources online.
 
@@
 
-\noindent If you would like to observe individual participants' cognitive walkthroughs, 
+\indent \indent If you would like to observe individual participants' cognitive walkthroughs, 
 we transcribed the audio files from our experiment

### 2015-05-12 cs261n-paper/paper.tex
removed laptop details
Documentation on the download page.

@@
 refers to the learnability, efficiency, memorability, error rate/recoverability, and satisfaction
-during use. To achieve these goals, the HCI community has established heuristics for user
-interface design: visibility of the system status, using familiar
+during use. To achieve these goals, the computer human interaction community has established 
+heuristics for user interface design: visibility of the system status, using familiar
 language, preventing errors, having consistent visuals, flexibility and efficiency of use, 
@@
 
-Usability has sligtly different meanings depending on the context. Some emphasize
+Usability has slightly different meanings depending on the context. Some emphasize
 learnability, flexibility, and ease of user. In a security context, the priorities are whatever is 
@@
 has user interface design goals than general consumer software, it likewise requires usability evaluation
-methods which are suitable to test these properties. Our goals are to test that the Tor Browser, 
-communicates an accurate conceptual model of the task to the users as quickly as possible, provide guidance to 
-users at the right time, and use warnings and other interactive tools to prevent any mistakes.
+methods which are suitable to test these properties. Our goals are to test that the Tor Browser 
+communicates an accurate conceptual model of the task to the users as quickly as possible, provides guidance to 
+users at the right time, and uses warnings and other interactive tools to prevent any mistakes.
 
@@
 of using multiple Tor-related tools including TorPark, Vidalia, FoxyProxy, and TorButton to find that
-none are fully satisfactory from a usability perspective. Researchers provide guidelines on 
+none are fully satisfactory from a usability perspective.  Clark \etal also provided guidelines on 
 how to incorporate the best aspects of each tool, while providing a set of guidelines drawn from
-usable security and computer human interaction. Key takeaways from this work includes 
-finding out that exposure to how Tor works may be difficult for users to understand, and that 
-familiar, non-technical language is critical for communication. We plan to draw from Clark's
+usable security and computer human interaction: Tor works may be difficult for users to understand, 
+so familiar, non-technical language is critical for communication. We plan to draw from Clark's
 guidelines as well as other works in usable security and computer human interaction to suggest
@@
 
-This will be the first experiment to evaluate Tor's usability as a censorship circumvention tool.
 Previous work on evaluating the usability of Tor as an anonymity system have been fruitful. 
@@
 We conducted the experiment on January 30-31st in Soda 
-Hall at the University of Berkeley, California. We used a 2013 Macbook Air and a 
-2012 Acer Aspire AS5750Z-4835 Windows laptop to give users a choice in using whatever they were comfortable with. 
+Hall at the University of Berkeley, California. We used a Mac laptop and a 
+Windows laptop to give users a choice in using whatever they were comfortable with. 
 All of our participants were Mac users. During the experiment, 
@@
 
+When users encountered this obstacle,
+they often returned to the download page, looking for hints or documentation.
+The download page did not provide help for problems such as this
+that are most salient immediately after downloading.
 As a result, Tor has developed a step-by-step visual guide on the download page to 

### 2015-05-12 cs261n-paper/paper.tex
reword related work
Edits on pilot study.

@@
 It has not undergone a formal usability assessment since
-its user interface was overhauled in its version~3.5 release in December 2013.
+its user interface was overhauled in December 2013.
 A central component of its user configuration interface
@@
 \section{A Pilot Tor Usability Study} 
-\indent \indent We ran a pilot Tor usability study to test the usability of Tor as an anonymity tool,
-targeting a specific demographic of users known to use Tor (journalists who have reported in other
-countries) and aiming to identify how well they could understand Tor's non-typical behaviors and 
-navigate advanced settings. For the full details of this pilot experiment, we refer you to Appendix~\ref{sec:pilot}.
+\indent \indent We ran a pilot study to test the usability of Tor as an anonymity tool,
+targeting a demographic of users who may have reason to use Tor, namely, journalists who have reported in other
+countries. We sought to identify how well they could understand Tor's non-typical behaviors and 
+navigate advanced settings. For the full details of this pilot experiment, see Appendix~\ref{sec:pilot}.
 
-During this pilot, the users were struggling with confusing bugs, such as flash errors which
-say ``Firefox'' rather than ``Tor,'' disappearing buttons on the configuration window, and errors when
-launching Tor from the download dialog rather than from their applications folder. This resulted in our 
-participants spending most of their time on the download and install tasks, rather than 
-our original task for navigating a robust menu or questioning the clarity of provided security 
-guarantees. We took the opportunity to collaborate with Tor developers to make changes for the Tor 
-Browser and use the lessons learned to design our large-scale user study on testing Tor as a 
+During the pilot, users struggled with confusing bugs, such as a few error messages that
+said ``Firefox'' rather than ``Tor Browser,'' disappearing buttons on the configuration window, and errors when
+running the program from the download archive without installing it.
+This resulted in our
+participants spending most of their time on the download and install tasks, and not
+what we considered the main tasks of browsing and
+questioning the clarity of provided security 
+guarantees. We took the opportunity to collaborate with Tor developers to make changes in the
+browser and use the lessons learned to design our large-scale user study on testing Tor as a 
 censorship circumvention tool.
@@
 \subsection{Impact}
-\indent \indent Along with the Tor developers who came to observe the UX pilot, we filed 
+\indent \indent Along with the Tor developers who came to observe the usability pilot, we filed 
 a total of sixteen bug tickets to Tor. At the time of  this writing, eight of the sixteen tickets 
@@
 
-As of April, the changes resulting from our pilot study has been incorporated into the latest 
-version of Tor Browser, making Tor more usable for people to use. 
-The summary of the usability changes can be found at \url{https://blog.torproject.org/blog/tor-browser-45a4-released}.
+As of April 2015, the usability improvements resulting from our pilot study has been incorporated into the shipping
+release of Tor Browser.
+A summary of changes can be found at \url{https://blog.torproject.org/blog/tor-browser-45a4-released}.
 
-Through the publicity of this usability pilot study on the Tor weekly blogs, we were connected
-with a source from the Library Freedom Project, which provides training on various technologies 
-to libraries across the country. We now collaborate with her work on creating a user manual
-for the Tor Browser.
+Through the publicity of the usability study on the Tor blog, we were connected
+with a source from the Library Freedom Project~\cite{libraryfreedomproject}, which provides training on various technologies 
+to libraries across the country. We now collaborate with her in working on creating a user manual
+for Tor Browser.
 
@@
 Although the data from the pilot study provided a lot of insight into what users thought processes
-are when completing various asks, transcribing audio recordings and syncing them to videos was
-required a lot of manual labor. Not only did this form of data collection and processing not scale 
+are when completing various asks, transcribing audio recordings and syncing them to videos
+required much manual work. Not only did this form of data collection and processing not scale 
 to larger numbers, we found that most users encountered similar thought processes and struggled
 with the same issues. Because of this, we aim to collect our future qualitative data in the form of 
-an open-ended survey question rather than using audio recordings.
+an open-ended survey rather than through audio recordings.
 
@@
 
-\section{UX sprint}
+\section{Pilot study}
 \label{sec:pilot}
-\indent \indent This pilot was to test-drive an experiment which examines the usability of Tor as an anonymity tool
-with respect to a target demographic of users known to use Tor (journalists who have reported in other
-countries). We emphasized the targeting of a high-risk user group of Tor and to 
+\indent \indent This pilot examined the usability of Tor as an anonymity tool
+with respect to journalists, a target demographic of users known to use Tor. 
+We emphasized the targeting of a high-risk user group of Tor and to 
 target usability changes aimed at helping those who could not afford to make mistakes. To see 
@@
 \subsection{Experiment Overview}
-\indent \indent Our experiment consisted of three parts. We first prepare our participants to perform a 
-cognitive walkthrough, ask our participants to perform a list of Internet browsing 
-tasks while performing a cognitive walkthrough, and finish with an exit survey to collect 
-additional information.
+\indent \indent Our experiment consisted of three parts. We first prepared our participants to perform a 
+cognitive walkthrough, asked our participants to perform a list of Internet browsing 
+tasks while performing a cognitive walkthrough, and finished with an exit survey to collect 
+demographic information.
 
-To first ensure that our users knew what a cognitive walkthrough is, we explain what a cognitive
-walkthrough and give a demonstration of a cognitive walkthrough on a non-related dummy task 
-(drawing a red hexagon in the computer graphics program Paint). We then ask our users to perform
+To first ensure that our participants are able to perform a cognitive walkthrough is, we explain what a cognitive
+walkthrough is and gave a demonstration of a cognitive walkthrough on a non-related dummy task 
+(drawing a red hexagon in the computer graphics program Paint). We then asked our users to perform
 an unrelated Internet-based task (finding the population of Zimbabwe) using any browser of their choice
-while performing a cognitive walkthrough along the process of completing the task. We give our 
+while performing a cognitive walkthrough. We took this opportunity to give our 
 participants feedback on how to properly conduct a cognitive walkthrough~\cite{wharton1994cognitive}.
@@
 
-We originally had another step after Step~1, ``Configure Tor.''
+We originally had an extra step after Step~1: ``Configure Tor.''
 We removed it after the first two participants
@@
 
-Tasks 1--3 test how easy it was for a user to search for, download, and install Tor Browser 
+Tasks 1--3 tested how easy it was for a user to search for, download, and install Tor Browser 
 correctly for use and if they understood that they had done the tasks correctly. 
 Since no software is useful if the user is not able to access it, we found it valuable
-to test the usability of this process.  Additionally, tasks 4--6 highlight Tor's ``irregular'' behavior 
-comparatively to other web browsers. Specifically, gauge user reactions to Tor's default
-privacy-preserving search engine Startpage,  longer loading times and performance for videos, 
-and disappearing tabs upon starting a new identity. Lastly, we asked our users to 
+to test the usability of this process.  Additionally, tasks 4--6 highlighted Tor's ``irregular'' behavior 
+comparatively to other web browsers. Specifically, we wanted to gauge user reactions to Tor's
+privacy-preserving search engine Startpage, decreased performance, 
+and side effects of advanced settings (such as disappearing tabs upon starting a new identity).
+ Lastly, we asked our users to 
 interact with and describe buttons on the toolbar to gauge user comprehension of how Tor functioned.
@@
 \subsection{Methodology} 
-\indent \indent We recruited five journalists from Berkeley by reaching out to journalist contacts.
- We recruited five users with an average age of 28 ($\sigma = 13 $~years). Out of 
-our five participants, 3 were female.
+\indent \indent We recruited five journalists from the Berkeley area by reaching out to journalist contacts.
+ We recruited five users with an average age of 28 ($\sigma = 13 $~years).  Out of  %?
+five participants, three were female.
 
@@
 
-This pilot was held in conjunction with the first Tor UX sprint. With IRB approval, Tor developers
+This pilot was held in conjunction with the first Tor UX Sprint. With IRB approval, Tor developers
 observed the screens of our participants, which was set to broadcast to a separate  
@@
 \indent \indent This experiment uncovered a powerful vector for attack, an unlikely source
-of usability issues, and insight into how to better communicate to users so that they can be 
-empowered to use Tor Browser and its advanced settings.
+of usability issues, and how users communicated with the current interface design.
 
@@
 During the task completion process, we observed that all our participants are likely 
-susceptible to a search engine optimization (SEO) poisoning attack. Most of our 
-participants  were on autopilot to complete this standard download task and 
+susceptible to a search engine optimization (SEO) poisoning attack during the 
+Tor download process. Most of our  participants were on autopilot and 
 were also not aware of the possibility that their download may come from an 
@@
 Luckily, all of our users managed to download Tor browser from the legitimate source. However, 
-upon searching through various search engines with a clear history, we found that cnet.com or techsource.com 
- appears as the first search result. Defenses against SEO optimization would be prudent to employ.
+defenses against SEO optimization would be prudent to employ.
 
@@
 downloaded from the Internet to execute on their machine unless overridden through
-managing system preferences. Surprisingly, the feature which impacted Tor's usability
-the most was the tension between a security precaution, and Tor's decision to self-sign
-their downloads, rather than a specific feature of the Tor Browser itself. We found that 
+managing system preferences. Participants could not download Tor without correctly
+configuring these system preferences. We found that 
 encountering the Gatekeeper will cause frustration to most users, and may be enough 
@@
 
-Notice that this user explained what the feature can do for him, rather than how the 
+This user explained what the feature can do for him, rather than how the 
 feature works. For the end user, the reason why a security feature is employed is what 
-makes a feature valuable and thus motivates them to use the feature. Communicating why a 
+makes a feature valuable and thus motivates them to use the feature. We believe that communicating why a 
 feature is present may be more effective for increasing use of advanced features 
@@
 fraction of users will encounter major usability obstacles. However, it was effective at discovering 
-and demonstrating issues that are likely to cause problems for many users. 
-People did have difficulty with installing Tor Browser (principally because of the Gatekeeper 
-code-signing feature on OS X), did not understand what many of the toolbar options meant, 
-and were confused by most Tor-specific behaviors. For specific problems 
+and demonstrating issues that are likely to cause problems for many users. For specific problems 
 encountered by an individual user, we refer you to our resources online.

### 2015-05-12 cs261n-paper/paper.tex
some edits to ux section

--- 2015-05-12 cs261n-paper/paper.tex
@@
 \label{sec:pilot}
-\indent \indent This pilot was to test-drive an experiment which examines the usability of Tor as an anonymity tool
-with respect to a target demographic of users known to use Tor (journalists who have reported in other
-countries). We emphasized the targeting of a high-risk user group of Tor and to 
+\indent \indent This pilot examined the usability of Tor as an anonymity tool
+with respect to journalists, a target demographic of users known to use Tor. 
+We emphasized the targeting of a high-risk user group of Tor and to 
 target usability changes aimed at helping those who could not afford to make mistakes. To see 
@@
 \indent \indent We recruited five journalists from Berkeley by reaching out to journalist contacts.
- We recruited five users with an average age of 28 ($\sigma = 13 $~years). Out of 
+ We recruited five users with an average age of 28 ($\sigma = 13 $~years).  Out of  %?
 our five participants, 3 were female.
@@
 
-When users encountered this obstacle,
-they often returned to the download page, looking for hints or documentation.
-The download page did not provide help for problems such as this
-that are most salient immediately after downloading.
 As a result, Tor has developed a step-by-step visual guide on the download page to 

### 2015-05-12 cs261n-paper/paper.tex
corrections to experiment design section

@@
 
-\subsection{Censorship} %%%
-% \indent \indent Motivational paragraph time about how this is so everywhere.
+\subsection{Censorship}
 
@@
 demographics of our participants, open-ended responses of their experience with censorship circumvention,
-and general security questions to gauge their awareness in this area. Along with the empirical measurements 
-we have taken during the experiment, we will use this survey information to determine which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.
+and general security questions.
+Along with the empirical measurements, we will use this survey information to determine which configuration tasks are hard (bridges versus proxies), how many were successful, how long it took users to configure, if they understood the process, and if they were confident that it was working as expected.
 
@@
 
-\indent \indent For our experiment, we plan to simulate and test three distinct censorship environments
+\indent \indent We plan to simulate and test three distinct censorship environments
 which vary in their methods of censorship and thus require distinct responses from our 
@@
 Blocked requests are redirected to a block page.
-%what do users need to do to circumvent this? 
 \item{\bfseries DNS-only censor.}
@@
 outside a small whitelisted set.
-%what do users need to do to circumvent this? 
 \item{\bfseries Comprehensive censor.}
@@
 Blocked requests fail silently (no block page).
-%what do users need to do to circumvent this? 
 \end{itemize}
@@
 they are not comfortable with performing or sending them to websites which they are 
-unfamiliar with will introduce more variables into the experiment to account for. 
+unfamiliar with will introduce more variables into the experiment. 
 Specifically, we would need to separate any confusion caused by the task itself versus
@@
 We plant to solicit feedback on the design of this experiment at HotPETs 2015. 
-Circumvention is broader than the stereotypical ``dissident blogger'' 
-use case. We will solicit feedback on which additional tasks will provide additional insight,
+We will solicit feedback on which additional tasks will provide additional insight,
 or if there are different tasks which are representative of other censorship evasion use cases.
@@
 \subsection{Recruitment}  
-\indent \indent We plan to recruit up to 200 users for the purpose of this study, making this the largest user 
+\indent \indent We plan to recruit around 200 users for the purpose of this study, making this the largest user 
 study to date examining Tor. We do this in order to increase our chances at recruiting a diverse
@@
 We opted for both concrete quantitative measurements of their experience along with free-text
-qualitative data to gather a broad range of information from our 200 participants in a scalable manner.
+qualitative data to gather a broad range of information in a scalable manner.
 
@@
 Although quantitative and qualitative data provides valuable feedback into what users perceive of 
-their censorship circumvention experience, it will be imperative that we check for the validity of their 
+their censorship circumvention experience, we will check for the validity of their 
 statements by analyzing empirical data collected by our browser extension during the process of the

### 2015-05-12 cs261n-paper/paper.tex

@@
 
-\section{UX sprint}
+\section{Pilot study}
 \label{sec:pilot}
@@
 \subsection{Methodology} 
-\indent \indent We recruited five journalists from Berkeley by reaching out to journalist contacts.
+\indent \indent We recruited five journalists from the Berkeley area by reaching out to journalist contacts.
  We recruited five users with an average age of 28 ($\sigma = 13 $~years).  Out of  %?
-our five participants, 3 were female.
+five participants, three were female.
 

### 2015-05-12 cs261n-paper/paper.tex
kill orphans

@@
 
-These environments are not meant perfectly to replicate the network environment
-in any particular country.  Censorship environments in are complex and volatile, making
-the task of replicating a network environment infeasible. More importantly, replicating these
-environments is not critical to this experiment. What is required for this experiment are 
+These environments are not meant to replicate the network environment
+in a particular country.  Censorship environments in are complex and volatile, making
+it infeasible to replicating a network precisely. Moreover, precise
+environments is not critical to this experiment but rather
 environments which would require users to complete similar Tor configuration 
 tasks before they are able to circumvent the censorship environment. We set up the following 
-abstract simulations which are inspired by reality and require users to complete various tasks
-to circumvent censorship.
+abstract environments, which are inspired by reality.
 
@@
 
-All participants will be given the same set of tasks, regardless of their simulated
-censorship environment.  Although every participant will attempt to complete the same 
+All participants will be given the same set of tasks, regardless of their environment.  
+Although every participant will attempt to complete the same 
 set of tasks, the difficulty of completing these tasks will vary based on their chosen environment. 
@@
 
-The goal of this experiment is to measure how usable Tor Browser is as a censorship circumvention
-tool. We hope that this experiment will provide insight into what usability improvements can be made 
+We hope that this experiment will provide insight into what usability improvements can be made 
 in order to better to make Tor Browser's advanced features more accessible to the average user. The results
@@
 \indent \indent  Work by Clark \etal to explore ways to simplify the Tor user interface
-has led to great usability improvements~\cite{clark2007usability}.  Clark analyzed the challenges 
+has led to usability improvements~\cite{clark2007usability}.  Clark analyzed the challenges 
 of using multiple Tor-related tools including TorPark, Vidalia, FoxyProxy, and TorButton to find that
@@
 how to incorporate the best aspects of each tool, while providing a set of guidelines drawn from
-usable security and computer human interaction: Tor works may be difficult for users to understand, 
-so familiar, non-technical language is critical for communication. We plan to draw from Clark's
+usable security and computer human interaction. We plan to draw from Clark's
 guidelines as well as other works in usable security and computer human interaction to suggest
@@
 After the calibration task, we asked participants to complete
-the following Tor Browser--related tasks:
+the following Tor Browser--related tasks: \\
 

### 2015-05-12 cs261n-paper/paper.tex
Edits on experiment design.

@@
 common censorship techniques employed 
-today along with knowledge of how pluggable transports will need to be used.
-For instance, some of Tor's pluggable transports work in censorship environments
-where others do not. Additionally, some of them require additional information (like bridge 
-addresses) before they enable the user to successfully circumvent censorship. 
+today, along with knowledge of how pluggable transports will need to be used.
+For instance, some of Tor's pluggable transports work in places
+that others do not. Additionally, some of them require additional information (like bridge 
+addresses) before they work.
 Details of the three censorship environments are below, increasing in 
-order of censorship comprehensiveness and, therefore, difficulty to circumvent.
+rough order of sophistication and difficulty to circumvent.
 
@@
 
-We plan to solicit feedback on the design of this experiment at HotPETs 2015.
-Specifically, we would want a reliable way to target the testing of 
-specific transports. But given that the average user would not have domain knowledge of 
-what transports are for Tor, is there anything to infer from participants' selection of transports, 
-or do we assume they are trying transports at random?
+We plan to solicit feedback on the design of this experiment at the HotPETs 2015 workshop.
+Specifically, we would like a reliable way to target the testing of 
+specific transports. Given that the average user does not have domain knowledge of 
+what transports are for Tor, we wonder whether there is anything to infer from users' selection,
+or whether they are try transports at random?
 
@@
 down the possibilities by removing tasks which caused ethical concerns (such as 
-requiring a user to log in to a websites, which would reveal login information).  
-We believe that these tasks we will use for our study will be simple tasks for an average 
-user to complete, on familiar websites.
+requiring a user to log in with a personal account).  
+We believe that the tasks we will use for our study will be easy for an average 
+user to complete.
 
@@
 Although every participant will attempt to complete the same 
-set of tasks, the difficulty of completing these tasks will vary based on their chosen environment. 
-Depending on the censorship environment, some tasks may not even require the use or Tor Browser.
+set of tasks, the difficulty of completing these tasks will vary based on the simulated censor.
+Depending on the environment, some tasks may not even require the use or Tor Browser.
 

### 2015-05-12 cs261n-paper/paper.tex
Typo.

@@
 what transports are for Tor, we wonder whether there is anything to infer from users' selection,
-or whether they are try transports at random?
+or whether they try transports at random?
 

### 2015-05-12 cs261n-paper/paper.tex
better

@@
 what transports are for Tor, we wonder whether there is anything to infer from users' selection,
-or whether they try transports at random?
+or whether they try transports at random.
 
